### 2020-04-06 paper.tex
Initial Overleaf Import

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{hyperref}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{SPANG library: a controlled query set for FAIR SPARQL}
%
\titlerunning{SPANG library}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
%\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
%Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
%Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
\author{Hirokazu Chiba}
%
\authorrunning{H. Chiba}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
%\institute{Princeton University, Princeton NJ 08544, USA \and
%Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
%\email{lncs@springer.com}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
%ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
%\email{\{abc,lncs\}@uni-heidelberg.de}}
\institute{Database Center for Life Science, Chiba 277-0871, Japan\\
\email{chiba@dbcls.rois.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 15--250 words.
How can we maximize the value of accumulated SPARQL queries? An increasing number of datasets have been published in the Resource Description Framework (RDF) and the SPARQL standard allows interoperable framework for querying the RDF datasets; however, reuse of SPARQL queries remains in a limited level. The problem is the lack of findability, accessibility and reusability of SPARQL queries that were once written. Given that SPARQL is an important framework of the Semantic Web, it is important to consolidate the eco-system to reuse SPARQL queries written in various project.
Here, we present a extended specification for storing and distributing SPARQL queries named SPANG, and provide a pilot study of SPANG library.
These features facilitate easy access to RDF datasets by users. 
We present a metadata set for annotating a SPARQL query.
It enables to identify SPARQL query, and provides useful information fo the query.
We also present a mechanism to parameterize the SPARQL query.
It make each query reusable in different settings.
Further, the mechanism enables federated queries by combining multiple queries through Unix pipe. 
Here, we developed spang command, as a client that helps users to generate queries. SPANG can create typical short queries according to the arguments specified by users like a \textit{one-liner} style in the Unix command line. It can also call SPARQL template libraries constructed in a local file system or published on the Web. 
This study make SPARQL queries more findable, accessible, interoperable, and reusable, i.e., pushing forward FAIR SPARQL.
SPANG is freely available at \url{https://spang.dbcls.jp}.
\keywords{SPARQL query \and RDF store \and template library.}
\end{abstract}
%
%
%
\section{Introduction}
An increasing number of datasets have been published in the Resource Description Framework (RDF). 
Although the SPARQL language provides a basis for exploiting RDF databases, writing a raw SPARQL code often becomes a burden for users. 
% Several approaches for support of SPARQL writing exist. One is to develop SPARQL editors that have useful functionalities 
% such as URI autocompletion~\cite{Rietveld}.
% Another aims at automatic generation of SPARQL queries~\cite{Yamaguchi}.
% Despite the efforts of previous studies, Semantic Web users remain bound to the task of SPARQL coding.
Here, we developed SPANG, a novel SPARQL client
that addresses this issue of SPARQL coding by simple query generation and reusing existing query templates.
SPANG
%, with its unique features, 
minimizes the burden of coding SPARQL,
thereby enhancing integrative analysis of distributed RDF databases.

SPARQL is a fundamental technology for querying RDF data. However, is is not designed for reusability. In data management guideline, FAIR principle is well known~\cite{fair}. Findability, Accesibility, Reusablility should be addressed, to make the most of SPARQL queries as resources.

The Semantic Web is comprised of various specifications, including RDF~\cite{rdf}, OWL~\cite{owl}, and SPARQL~\cite{sparql}. The ontologies written in OWL are accumulated and shared on repositories~\cite{bioportal}.
RDF datasets are also accumulated and hosted in portal web sites~\cite{rdf-portal}.
Not only the ontologies and datasets, but also the queries are important for the Semantic Web.
Accumulating and reusing the queries are important.

Reusing SPARQL queries are important for efficient development of the Semantic Web.

Are SPARQL queries accessible? In most cases, those queries are not accessible. According to the FAIR principle, resources should be accessible by through URI. In some cases, SPARQL queries are stored in repositories. But they do not have stable URIs.

How about findability? In many Semantic Web projects, SPARQL queries are written and accumulated. However, those SPARQL queries are not findable, due to the lack of export and import SPARQL queries.

Here, we decided to follow the FAIR principle and extend the SPARQL specifications for more efficient development of the Semantic Web.

The SPANG package includes the main {\tt spang} command, which can be used in the Unix command-line environment.
In general, the {\tt spang} command help users query RDF databases by dynamically generating SPARQL queries according to the command-line options or arguments. 
More specifically, {\tt spang} has two execution modes: 
1) simple mode; for a simple query, users must only specify some command-line options to generate the query without writing any SPARQL code, and
2) template mode; for a more complex query, users can generate the query using a predefined SPARQL template and parameters.
Basically, each {\tt spang} process submits a query to a specific database,
and the {\tt spang} process can be combined with other Unix processes through a Unix pipe. 
Notably, multiple {\tt spang} commands each with distinct target database can be combined through a Unix pipe, thereby realizing federated queries to multiple databases (see Section 2.4).

To reduce the burden of coding SPARQL, the SPANG package provides predefined configurations about nicknames for SPARQL endpoints, prefix declarations for URIs, and SPARQL libraries (see Section 3).

Contributions of this work:
we provide a SPARQL meta data required for constucting SPARQL queries.
we constructed template engines for SPARQL queries.
we constructed controlled SPARQL queries for available SPARQL endpoints.

The following section includes: overview of the SPANG project, specification of SPANG templates, implementation of the SPANG library, and use case of SPANSG library.

%%%%%%%%%%%%%%%%%%%%%%%%

\section{SPANG}
SPANG is originally developed for "SARQLing" the RDF dataset from command line. Here, we re-implemented the SPANG using Node.js and now the functionality is available through Web browser.

Figure~\ref{fig:spang_top} is the top page of SPANG, which includes links to GitHub, Documentation, and SPANG library.

\begin{figure}
\center
\includegraphics[width=1.0\textwidth]{spang_top.png}
\caption{SPANG web site}
\label{fig:spang_top}
\end{figure}

Figure~\ref{fig:spang_lib} is the list of the target SPARQL endpoints. It also lists the SPARQL templates available in general for various endpoints.

\begin{figure}
\center
\includegraphics[width=1.0\textwidth]{spang_lib.png}
\caption{SPANG library}
\label{fig:spang_lib}
\end{figure}

Figure~\ref{fig:spang_lib} is the list of SPARQL templates for DisGeNet SPARQL endpoint.
A short name for the SPARQL template, descriptin of the query, and example parameters are shown.

\begin{figure}
\center
\includegraphics[width=1.0\textwidth]{spang_disgenet.png}
\caption{SPANG templates for DisGeNet SPARQL endpoint}
\label{fig:spang_disgenet}
\end{figure}

Figure~\ref{fig:spang_disease_gene_query} shows a query for DiesGeNet SPARQL endpoint to get disase gene relationship. 
Figure~\ref{fig:spang_disease_gene_result} shows the result of the query. Thus, users can get the results only by clicking on the web pages, browsing the SPARQL template on the SPANG web site.

\begin{figure}
\center
\includegraphics[width=1.0\textwidth]{spang_disease_gene_query.png}
\caption{SPANG templates for DisGeNet SPARQL endpoint}
\label{fig:spang_disease_gene_query}
\end{figure}

\begin{figure}
\center
\includegraphics[width=1.0\textwidth]{spang_disease_gene_result.png}
\caption{SPANG templates for DisGeNet SPARQL endpoint}
\label{fig:spang_disease_gene_result}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%
\section{SPANG library}

Here, we constructed SPANG library: a SPARQL library which is findable, accessible, interoperable and reusable.

\subsection{Findability of SPARQL queries}
Most of the SPARQL queries are not findable from general users of the Semantic Web. The first and most important step toward increased value of the written SPARQL queries is to consider how to make SPARQL queries findable.
In the FAIR principle, making resources findable includes indexing resources by adding metadata to each resources. 
To make SPARQL queries findable, we propose to add metadata to SPARQL.
The SPARQL metadata includes:
\begin{itemize}
    \item Title
    \item Description
    \item Topic
    \item Parameters: name, default value, class
    \item Target endpoint
\end{itemize}

Indexing of SPARQL queries are conducted and thus users can obtain specific queries of interest through a search API.

\subsection{Accessibility to SPARQL queries}
Some of the SPARQL libraries are accessible from internet. Howver, we could consider more general scheme for accesibility. In the FAIR principle, accessibility includes minting URI for each resource. Here we propose to use stable URI for each SPARQL query.
In the case of SPANG library, we assign two URI for each query. One is for retrieving SPARQL query string, thereby users can retrieve the concrete content of the query. Another is URI to get results. This URI can include the parameter settings for the specified query.

\subsection{Interoperability of SPARQL}
SPARQL specification is proposed for interoperable use of queries to the Semantic Web. It is valuable to use several triplestore implementation through the same programming interface. However, no rule is proposed for coding rules; capitalization, indentation and newline, etc. Lack of those rules result in variation of SPARQL queries, which hampers the reuse of SPARQL queries. In other languages, some coding ruels exist. In the case of SPARQL, specification document or text books do not follow a specific coding rules. Here, we specify the coding rule used in SPANG template library, and implemented spfmt command to reformat of the code.

\subsubsection{SPANG coding rules}
We defined a coding rule for SPARQL and its extention in SPANG framework. Coding rule is important for productivity of shared coding tasks and effective maintenance. It also helps to make debug process easier; weird look suggests possible bugs. 
\begin{itemize}
    \item Header lines: query can start with header lines as comment lines. Metadata can be added at the top of the query as comment lines. Multiple lines are allowed. If multiple lines are described, they are written in sequential without blank lines. After the metadata lines, a blank line comes.
    \item Prefix: prefix declaration comes in sequential lines. Each of before and after the prefix declaration lines, a blank line exists.
    \item Cases: the SPARQL keywords should be in upper case characters. variabl names comes with ? followed by lower case characters.
    \item Literal: the literals are surrounded by "".
    \item Indent: indentation depth is two spaces.
    \item Spaces: a space exists between keywords and variables. A space exists before , or ; or . .
    \item Newline: a newline exists before the keyword \texttt{WHERE} and after \texttt{\{}. A new line exist after ; or . but not after ,. After the newline following ;, an indent follows. A newline exist before query modifiers such as \texttt{ORDER BY} or \texttt{LIMIT}.
\end{itemize}
We developed a reformatter of the SPARQL code as described below.

\subsection{Reusability of SPARQL queries}
Reusability of SPARQL is not a new topic. Various activity is conducted to construct libraries of SPARQL. It is considered as acitivities to increase the reusability of SPARQL queries. However, no standard to increase the reusability is proposed. In the specifiation of SPARQL, reusability is not a centroal topic. However, it is an central resource in a Semantic Web. If it is a component of Semantic Web comprised of RDF/OWL/SPARQL, it is reasonable to represent it in RDF framework. We propose a way to represent SPARQL in the RDF framework.

Templating is also a key issue for reusability. SPARQL specifications do not includes templating mechanism, but without templating, each SPARQL queries are not applicable to other use cases. We implemented templating mechanism using a general freamework, mustash.

\subsection{Example query}
An example query in the SPANG library is shown below.
The DisGeNet endpoint is specified.

\begin{figure}[!t]
\begin{scriptsize}
\begin{verbatim}
# @title Get UniProt IDs for a specific disease, e.g. C0751955 ("Brain Infarction")
# @endpoint http://rdf.disgenet.org/sparql/
# @prefix https://raw.githubusercontent.com/hchiba1/spang-library/master/prefix/bio
# @param arg1=C0751955

PREFIX disgenet_source: <http://rdf.disgenet.org/v4.0.0/void/>
PREFIX umls: <http://linkedlifedata.com/resource/umls/id/>

SELECT DISTINCT ?gene ?score ?gene_label ?source ?gda ?pmid ?description
WHERE {
    ?gda sio:SIO_000628 umls:{{arg1}} ,
                        ?gene ;
          a ?type ;
          sio:SIO_000253 ?source ;
          sio:SIO_000216/sio:SIO_000300 ?score .
    ?gene a ncit:C16612 ;
          rdfs:label ?gene_label .
    OPTIONAL {
        ?gda sio:SIO_000772 ?pmid ;
             dct:description ?description .
    }
}
ORDER BY DESC(?score) ?source ?pmid

\end{verbatim}
\end{scriptsize}
\caption{Example query in SPANG library}
\label{fig:example-rdf}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SPANG API}

SPANG library is accesible through SPANG Web API.

\subsection{Library API}

\subsection{Query API}

The following command returns the list of query libraries.

\texttt{curl https://spang-portal.dbcls.jp/api/library}

\begin{figure}[!t]
\begin{scriptsize}
\begin{verbatim}
[
  {
    "name": "disgenet",
    "title": "DisGeNET",
    "description": "DisGeNET",
    "endpoint": "http://rdf.disgenet.org/sparql/",
    "schema": "http://www.disgenet.org/web/DisGeNET/menu/rdf#schema",
    "uri": "http://localhost:7070/api/library/disgenet",
    "count": 14
  },
  {
    "name": "wikipathways",
    "title": "WikiPathways",
    "description": "WikiPathways",
    "endpoint": "http://sparql.wikipathways.org/",
    "schema": null,
    "uri": "http://localhost:7070/api/library/wikipathways",
    "count": 6
  },
  ...
]
\end{verbatim}
\end{scriptsize}
\caption{List of in query libraries obtained by API}
\label{fig:example-rdf}
\end{figure}

The following command returns the result of the query, with the given paramter.

\texttt{curl https://spang-portal.dbcls.jp/api/library/disgenet/gene\_disease.rq?arg1=678}

\begin{figure}[!t]
\begin{scriptsize}
\begin{verbatim}

"Precursor T-Cell Lymphoblastic Leukemia-Lymphoma"@en	"0.31"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/28671688>	"2017"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Precursor T-Cell Lymphoblastic Leukemia-Lymphoma"@en	"0.31"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/20622884>	"2010"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Colorectal Cancer"@en	"0.3"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/25944804>	"2016"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Colorectal Carcinoma"@en	"0.3"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/25944804>	"2016"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Colorectal Neoplasms"@en	"0.3"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/25944804>	"2016"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Malignant neoplasm of prostate"@en	"0.3"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/17199135>	"2007"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Prostatic Neoplasms"@en	"0.3"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/17199135>	"2007"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Lymphocyte Count measurement"@en	"0.1"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/27863252>	"2017"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Platelet Count measurement"@en	"0.1"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/27863252>	"2017"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Acute leukemia"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/21109922>	"2011"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Burkitt Lymphoma"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/21109922>	"2011"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Hematologic Neoplasms"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/21109922>	"2011"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Leukemia, Myelocytic, Acute"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/21109922>	"2011"^^<http://www.w3.org/2001/XMLSchema#gYear>
"leukemia"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/21109922>	"2011"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Acute lymphocytic leukemia"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/20622884>	"2010"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Lymphoid leukemia"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/20622884>	"2010"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Precursor Cell Lymphoblastic Leukemia Lymphoma"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/20622884>	"2010"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Breast Carcinoma"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/19146866>	"2009"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Malignant neoplasm of breast"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/19146866>	"2009"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Choriocarcinoma"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/12566248>	"2003"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Complete hydatidiform mole"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/12566248>	"2003"^^<http://www.w3.org/2001/XMLSchema#gYear>
"Gestational Trophoblastic Neoplasms"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/12566248>	"2003"^^<http://www.w3.org/2001/XMLSchema#gYear>
\end{verbatim}
\end{scriptsize}
\caption{Query results obtained by API}
\label{fig:example-rdf}
\end{figure}

The following command searches for queries with keywords.

\texttt{curl https://spang-portal.dbcls.jp/api/search?keyword=gene}

\begin{figure}[!t]
\begin{scriptsize}
\begin{verbatim}

{
  "disgenet": [
    {
      "name": "disease_gene",
      "title": "Get UniProt IDs for a specific disease, e.g. C0751955 (\"Brain Infarction\")",
      "uri": "http://localhost:7070/api/disgenet/disease_gene",
      "endpoint": "http://rdf.disgenet.org/sparql/",
      "param": [
        {
          "name": "arg1",
          "default": "C0751955"
        }
      ]
    },
    {
      "name": "disease_uniprot",
      "title": "Get UniProt IDs for a specific disease, e.g. C0751955 (\"Brain Infarction\")",
      "uri": "http://localhost:7070/api/disgenet/disease_uniprot",
      "endpoint": "http://rdf.disgenet.org/sparql/",
      "param": [
        {
          "name": "arg1",
          "default": "C0751955"
        }
      ]
    },
    {
      "name": "gda_alzheimer",
      "title": "Alzheimer's disease-related genes with curated evidences",
      "uri": "http://localhost:7070/api/disgenet/gda_alzheimer",
      "endpoint": "http://rdf.disgenet.org/sparql/",
      "param": [

      ]
    },
    {
      "name": "gda_evidence",
      "title": "Get specific gda, e.g. NCBI gene ID 4204 and C0035372(\"Rett Syndrome\")",
      "uri": "http://localhost:7070/api/disgenet/gda_evidence",
      "endpoint": "http://rdf.disgenet.org/sparql/",
      "param": [

      ]
    },
    {
      "name": "gene_disease",
      "title": "Get disease associated with NCBI gene ID",
      "uri": "http://localhost:7070/api/disgenet/gene_disease",
      "endpoint": "http://rdf.disgenet.org/sparql/",
      "param": [
        {
          "name": "arg1",
          "default": "675"
        }
      ]
    },
    {
      "name": "get_gda",
      "title": "Get specific type of gene-disease association",
      "uri": "http://localhost:7070/api/disgenet/get_gda",
      "endpoint": "http://rdf.disgenet.org/sparql/",
      "param": [
        {
          "name": "arg1",
          "default": "SIO_001120"
        },
        {
          "name": "arg2",
          "default": "10"
        }
      ]
    },
    {
      "name": "list_gda_sources",
      "title": "List sources of gene-disease association",
      "uri": "http://localhost:7070/api/disgenet/list_gda_sources",
      "endpoint": "http://rdf.disgenet.org/sparql/",
      "param": [

      ]
    },
    {
      "name": "list_gene_disease",
      "title": "List gene disease associations",
      "uri": "http://localhost:7070/api/disgenet/list_gene_disease",
      "endpoint": "http://rdf.disgenet.org/sparql/",
      "param": [
        {
          "name": "arg1",
          "default": "10"
        }
      ]
    },
    {
      "name": "regex_disease",
      "title": "Search the NCI Thesaurus for specific diseases",
      "uri": "http://localhost:7070/api/disgenet/regex_disease",
      "endpoint": "http://rdf.disgenet.org/sparql/",
      "param": [
        {
          "name": "arg1",
          "default": "breast"
        }
      ]
    },
    {
      "name": "regex_gda_disease",
      "title": "Regex seach for specific diseases that have gene-disease association information",
      "uri": "http://localhost:7070/api/disgenet/regex_gda_disease",
      "endpoint": "http://rdf.disgenet.org/sparql/",
      "param": [
        {
          "name": "arg1",
          "default": "alzheimer"
        }
      ]
    },
    {
      "name": "uniprot2disease",
      "title": "Get diseases associated with given UniProt IDs",
      "uri": "http://localhost:7070/api/disgenet/uniprot2disease",
      "endpoint": "http://rdf.disgenet.org/sparql/",
      "param": [

      ]
    },
    {
      "name": "uniprot2disease_curated",
      "title": "Get diseases associated with given UniProt IDs",
      "uri": "http://localhost:7070/api/disgenet/uniprot2disease_curated",
      "endpoint": "http://rdf.disgenet.org/sparql/",
      "param": [

      ]
    },
    {
      "name": "uniprot2disease_curated_none",
      "title": "Get diseases associated with given UniProt IDs",
      "uri": "http://localhost:7070/api/disgenet/uniprot2disease_curated_none",
      "endpoint": "http://rdf.disgenet.org/sparql/",
      "param": [

      ]
    },
    {
      "name": "uniprot2disease_none",
      "title": "Get diseases associated with given UniProt IDs",
      "uri": "http://localhost:7070/api/disgenet/uniprot2disease_none",
      "endpoint": "http://rdf.disgenet.org/sparql/",
      "param": [

      ]
    }
  ],
  "general": [
    {
      "name": "find_term_uri",
      "title": "Find classes or properties (regex search for URIs or labels)",
      "uri": "http://localhost:7070/api/general/find_term_uri",
      "endpoint": "http://dbpedia.org/sparql",
      "param": [
        {
          "name": "arg1",
          "default": "homolo"
        }
      ]
    },
    {
      "name": "graphs_bug",
      "title": "SELECT DISTINCT ?graph, instead of GROUP BY ?graph, returns less results (Virtuoso 7.1.0)",
      "uri": "http://localhost:7070/api/general/graphs_bug",
      "endpoint": "http://dbpedia.org/sparql",
      "param": [

      ]
    },
    {
      "name": "label",
      "title": "",
      "uri": "http://localhost:7070/api/general/label",
      "endpoint": "http://dbpedia.org/sparql",
      "param": [

      ]
    },
    {
      "name": "link_select",
      "title": "Links from a specific instance",
      "uri": "http://localhost:7070/api/general/link_select",
      "endpoint": "http://dbpedia.org/sparql",
      "param": [

      ]
    },
    {
      "name": "regex_uri",
      "title": "Regex search for URIs (subjects of triples)",
      "uri": "http://localhost:7070/api/general/regex_uri",
      "endpoint": "http://dbpedia.org/sparql",
      "param": [

      ]
    },
    {
      "name": "search_for_class",
      "title": "Free text search in Virtuoso",
      "uri": "http://localhost:7070/api/general/search_for_class",
      "endpoint": "http://dbpedia.org/sparql",
      "param": [

      ]
    },
    {
      "name": "search_label_for_class",
      "title": "Free text search in Virtuoso",
      "uri": "http://localhost:7070/api/general/search_label_for_class",
      "endpoint": "http://dbpedia.org/sparql",
      "param": [

      ]
    },
    {
      "name": "search_label_not_class",
      "title": "Free text search in Virtuoso (count instances of each class)",
      "uri": "http://localhost:7070/api/general/search_label_not_class",
      "endpoint": "http://dbpedia.org/sparql",
      "param": [

      ]
    }
  ]
}

\end{verbatim}
\end{scriptsize}
\caption{Search results obtained by API}
\label{fig:example-rdf}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementation}
SPANG is implemented in JavaScript.

\subsubsection{SPANG template specification}
SPANG template syntax is an extension of sparql-doc. Although the sparql-doc aims at documentation of SPARQL originally, this notation is suitable for annotating each SPARQL query with metadata in the frame of SPARQL query. Each query can be still used as standard SPARQL query, and furthermore, if a parser for comment liens is implemented, users can obtain the metadata for the queries.
Here, we consider the parameterization in this frame. We consider the parameters of the query as metadata of SPARQL.
As a synatax parameterization, we consider mustash notation.

\subsubsection{SPARQL template engine on the basis of AST}
SPANG template engine is implemented, where each template can be transformed into abstract syntax tree, and then reconstructed into SPARQL. 
We used PEG expression of SPARQL grammer originally expressed in EBNF in the SPARQL specification. The original implementation of PEG.js of SPARQL grammer is provided by rdfstore-js project (https://github.com/antoniogarrote/rdfstore-js).
The PEG.js code was modified to fit the use in the case of SPANG library.
The PEG.js is a parser generator, thus, we could generate our own parser based on the PEG.js description. Thus, we obtained abstract syntax tree in the form of JSON objecct.

We also developed a formatter to stringify the JSON object into string text. Thus, we can reformat the input SPARQL.

\subsubsection{SPARQL template library}
We implemented SPARQL queries for 10 endpoints.
We implemeted the API using Ruby.

\subsubsection{SPANG command line client}
Originally, SPANG was developed as a command line client using Perl language.
It is re-implemented in JavaScript using Node.js.
SPARQL templates can be executed in command line.

\subsubsection{SPANG Web site}
SPARQL queries can be executed in Web site.

%%%%%%%%%%%%%%%%%%%%
\section{Use cases}

% \subsection{Simple querying with SPARQL shortcuts}

% Specific command-line options, including \texttt{-S~\textit{SUBJECT}}, \texttt{-P~\textit{PREDICATE}},\\ \texttt{-O~\textit{OBJECT}}, \texttt{-L~\textit{LIMIT}}, and other modifiers, 
% are interpreted as shortcuts for generating typical SPARQL queries. 
% A simple example is:

% \texttt{spang uniprot -S tax:511145 -a}

% \noindent where the first argument is the target SPARQL endpoint and the following arguments are SPARQL shortcuts (the SPARQL endpoint can be specified in a URL or nickname for simplicity). 
% \texttt{uniprot} is a nickname for the UniProt SPARQL endpoint \cite{UniProt} and \texttt{tax:} is a prefix for URIs of NCBI taxonomy IDs. 
% This example command line searches the target database for statements that have taxonomy ID 511145 ({\it Escherichia coli} strain K-12 MG1655) as a subject. Using the \texttt{-a} option transforms the URIs in the search result into abbreviated forms using predefined prefix declarations. For example,\\
% \texttt{\textless http://www.w3.org/2000/01/rdf-schema\#subClassOf\textgreater}\\
% is transformed into \texttt{rdfs:subClassOf}.
% The result is output to the standard output in the form of tab-separated values by default, as it is suitable for processing by line-oriented Unix programs.
% In addition, combination of subject, predicate, and object is possible according to the following.

% \texttt{spang uniprot -S tax:511145 -P up:otherName}

% \noindent where predicate {\tt up:otherName} is specified to further confine the results to other names. 
% For the full list of available command-line options, simply type the command {\tt spang}.

\subsection{Using SPARQL templates with parameters}

Although SPARQL shortcuts are useful for simple querying with typical query patterns, they do not cover various
queries with complicated patterns. 
Thus, SPANG provides a mechanism to accept SPARQL templates to generate arbitrary query patterns. 
An example query is:

\texttt{spang uniprot taxtree\_ancestor 511145 -ac}

\noindent where the first argument is the target SPARQL endpoint and the following arguments are SPARQL templates and parameters. {\tt taxtree\_ancestor} is the name of a SPARQL template included in the predefined SPARQL library (see supplementary data for the code), {\tt 511145} is the parameter, {\tt -a} is the option for abbreviating results, and {\tt -c} is for aligning output columns for easier reading.
The specified parameter replaces the placeholder included in the template before execution. 
This example query traverses the NCBI taxonomy tree from the given ID (511145) to the root node and outputs scientific names in each taxonomic rank.

Available SPARQL templates are not limited to the local library.
If SPARQL libraries are published on the Web, the users can call the templates by means of URIs across the Web.
An example usage of the Microbial Genome Database (MBGD) SPARQL library published at http://mbgd.genome.ad.jp/sparql/library/ is as follows.
\begin{quoting}
\texttt{spang mbgd mbgdl:get\_ortholog K9Z723}
\vspace{1pt}
\end{quoting}
where {\tt mbgd} is the MBGD SPARQL endpoint \citep{Chiba} and \texttt{mbgdl:} is a prefix for abbreviating the URI of the template {\tt get\_ortholog} in the MBGD SPARQL library (see supplementary data for the code). 
The template can be specified in the full URI or in abbreviated form using the predefined prefix declarations.
This example query searches the MBGD database \citep{Uchiyama} for the orthologs of a protein \texttt{K9Z723} (Photosystem II lipoprotein Psb27).

The following example command line gives a parameter to the query template, and execute to the DisGeNet endpoint.
\texttt{spang gene\_disease.rq --param disease=C0751955}

% \subsection{Combinatorial execution of multiple queries}

% SPANG combines multiple queries through a Unix pipe. 
% Combining a {\tt spang} command in shortcut mode and another one in template mode is also possible.
% An example of such a combinatorial query is shown in Fig.~\ref{fig:01}.
% The first {\tt spang} command is in template mode, which is the same as that presented in the Section 2.3. 
% This command searches the MBGD database for orthologs of a protein {\tt K9Z723}. 
% The obtained list of proteins are used in the second query, which searches the UniProt database for annotations of the given list of proteins. 
% The option \texttt{-S 1} specifies the values from the first column of the standard input as subject.
% This combinatorial query enables integrative use of two databases distributed across the Web. 
% Here, the output of the first command can be further modified by altering the second command.
% For example:
% \begin{quoting}
% \texttt{spang mbgd mbgdl:get\_ortholog K9Z723 | spang uniprot uniprot\_xref PDB}
% \vspace{1pt}
% \end{quoting}
% where {\tt uniprot\_xref} is a SPARQL template (see supplementary data for the code), which retrieves cross-references from the UniProt IDs given in the standard input to the database specified as the parameter (in this example, {\tt PDB}). This example command line searches for entries in the Protein Data Bank (PDB) \citep{Berman} among orthologs of {\tt K9Z723}.

%%%%%%%%%%%%%%%%%%%%%%
\section{Availability}
\subsection{Command-line client}
We developed a command-line client in JavaScript.
The usages is as follows.

\begin{figure}[!t]
\begin{scriptsize}
\begin{verbatim}
Usage: spang2 [options] <SPARQL_TEMPLATE>

Options:
  -e, --endpoint <ENDPOINT>    target SPARQL endpoint (URL or its predifined name in SPANG_DIR/etc/endpoints,~/.spang/endpoints)
  -p, --param <PARAMS>         parameters to be embedded (in the form of "--param par1=val1,par2=val2,...")
  -o, --outfmt <FORMAT>        tsv, json, n-triples (nt), turtle (ttl), rdf/xml (rdfxml), n3, xml, html (default: "tsv")
  -a, --abbr                   abbreviate results using predefined prefixes
  -v, --vars                   variable names are included in output (in the case of tsv format)
  -S, --subject <SUBJECT>      shortcut to specify subject
  -P, --predicate <PREDICATE>  shortcut to specify predicate
  -O, --object <OBJECT>        shortcut to specify object
  -L, --limit <LIMIT>          LIMIT output (use alone or with -[SPOF])
  -F, --from <FROM>            shortcut to search FROM specific graph (use alone or with -[SPOLN])
  -N, --number                 shortcut to COUNT results (use alone or with -[SPO])
  -G, --graph                  shortcut to search for graph names (use alone or with -[SPO])
  -r, --prefix <PREFIX_FILES>  read prefix declarations (default: SPANG_DIR/etc/prefix,~/.spang/prefix)
  -n, --ignore                 ignore user-specific file (~/.spang/prefix) for test purpose
  -m, --method <METHOD>        GET or POST (default: "GET")
  -q, --show_query             show query and quit
  -f, --fmt                    format the query
  -i, --indent <DEPTH>         indent depth; use with --fmt (default: 2)
  -l, --list_nick_name         list up available nicknames of endpoints and quit
  -d, --debug                  debug (output query embedded in URL, or output AST with --fmt)
  -V, --version                output the version number
  -h, --help                   output usage information

\end{verbatim}
\end{scriptsize}
\caption{Example of input RDF data}
\label{fig:example-rdf}
\end{figure}

\subsection{SPANG portal web site}
SPANG portal web site is developed using Ruby on Rails. And it can be run on Docker. The SPANG query library is published on GitHub. Thus, users can run a portal site by their own.

\section{Related Work}

SPARQL tempalting mechanisms have been implemented in various projects. Based on the templating mechanisms, SPARQL libraries have been implemented, such as Bioqueries. SPARQList is a framework to store SPRARQL templates to be used through API.

As a SPARQL parser, SPARQL.js is available.

\section{Conclusion}
SPANG enables easy generation of typical queries, thereby reducing the burden of writing SPARQL. SPANG also provides a framework for reusing and sharing arbitrary queries across the Web. Moreover, it enables users to execute complex queries by combining existing query templates. SPANG, with these unique features, facilitates integrative exploitation of published RDF datasets and supports knowledge discovery.

\subsubsection{Limitations and Futur Work}
SPANG enables easy and effective access to RDF databases, thereby enhancing integrative exploitation of distributed biological databases.
Although the predefined configurations included in the software package are available to help users query biological RDF databases, 
the range of queries included in the package is limited to rather common ones.
The potential use of SPANG can be further extended by database users or database providers through development of SPARQL template libraries.
Specifically, SPANG can call SPARQL templates by their URIs across the Web.
Thus, if an RDF database provider,
who knows best the manner in which the database should be used,
publishes SPARQL template libraries, database usage can be considerably enhanced.
Sharing not only data but also queries (i.e., means of interpreting data) on the Semantic Web platform will help the biological research community collaborate in knowledge integration and discovery.

\subsubsection{Toward FAIR SPARQL libraries}
FAIRification of SPARQL is the goal of this project.

\section*{Acknowledgements}
We thank Shota Matsumoto for helping implementing the updated version of SPANG.

% \subsection{A Subsection Sample}
% Please note that the first paragraph of a section or subsection is
% not indented. The first paragraph that follows a table, figure,
% equation etc. does not need an indent, either.

% Subsequent paragraphs, however, are indented.

% \subsubsection{Sample Heading (Third Level)} Only two levels of
% headings should be numbered. Lower level headings remain unnumbered;
% they are formatted as run-in headings.

% \paragraph{Sample Heading (Fourth Level)}
% The contribution should contain no more than four levels of
% headings. Table~\ref{tab1} gives a summary of all heading levels.

% \begin{table}
% \caption{Table captions should be placed above the
% tables.}\label{tab1}
% \begin{tabular}{|l|l|l|}
% \hline
% Heading level &  Example & Font size and style\\
% \hline
% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
% \hline
% \end{tabular}
% \end{table}

% \noindent Displayed equations are centered and set on a separate
% line.
% \begin{equation}
% x + y = z
% \end{equation}
% Please try to avoid rasterized images for line-art diagrams and
% schemas. Whenever possible, use vector graphics instead (see
% Fig.~\ref{fig1}).

% \begin{figure}
% \includegraphics[width=\textwidth]{fig1.eps}
% \caption{A figure caption is always placed below the illustration.
% Please note that short captions are centered, while long ones are
% justified by the macro package automatically.} \label{fig1}
% \end{figure}

% \begin{theorem}
% This is a sample theorem. The run-in heading is set in bold, while
% the following text appears in italics. Definitions, lemmas,
% propositions, and corollaries are styled the same way.
% \end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
% \begin{proof}
% Proofs, examples, and remarks have the initial word in italics,
% while the following text appears in normal font.
% \end{proof}
% For citations of references, we prefer the use of square brackets
% and consecutive numbers. Citations using labels or the author/year
% convention are also acceptable. The following bibliography provides
% a sample reference list with entries for journal
% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
% and a homepage~\cite{ref_url1}. Multiple citations are grouped
% \cite{ref_article1,ref_lncs1,ref_book1},
% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

% \bibitem{Rietveld}
% Rietveld,L. and Hoekstra,R.: YASGUI: not just another SPARQL client,
% In: The Semantic Web: ESWC 2013 Satellite Events, 78-86. Springer (2013)

% \bibitem{Yamaguchi}
% Yamaguchi,A. \textit{et~al}.:
% An intelligent SPARQL query builder for exploration of various life-science databases.
% In: The 3rd International Workshop on Intelligent Exploration of Semantic Data (IESD 2014) (2014)

\bibitem{sparql}
SPARQL 1.1 Query Language, W3C Recommendation 21 March 2013. \url{http://www.w3.org/TR/sparql11-query/}

\bibitem{rdf}
RDF 1.1 Concepts and Abstract Syntax, W3C Recommendation 25 February 2014. \url{http://www.w3.org/TR/rdf11-concepts/}

\bibitem{owl}
OWL 2 Web Ontology Language
\url{https://www.w3.org/TR/owl2-overview/}

\bibitem{spang}
Chiba, H., & Uchiyama, I. (2017). SPANG: a SPARQL client supporting generation and reuse of queries for distributed RDF databases. BMC bioinformatics, 18(1), 93.

\bibitem{umaka}
Yamamoto, Y., Yamaguchi, A., & Splendiani, A. (2018). YummyData: providing high-quality open life science data. Database, 2018.

\bibitem{fair}
Wilkinson, M. D., Dumontier, M., Aalbersberg, I. J., Appleton, G., Axton, M., Baak, A., ... & Bouwman, J. (2016). The FAIR Guiding Principles for scientific data management and stewardship. Scientific data, 3.

\bibitem{sparql-doc}
sparql-doc: Generate HTML documentation from SPARQL queries.
\url{https://github.com/ldodds/sparql-doc}

\bibitem{spin}
SPIN: SPARQL Inferencing Notation.
\url{https://spinrdf.org/}

\bibitem{rdf-portal}
Kawashima, S., Katayama, T., Hatanaka, H., Kushida, T., & Takagi, T. (2018). NBDC RDF portal: a comprehensive repository for semantic data in life sciences. Database, 2018.

\bibitem{bioportal}
Salvadores, M., Alexander, P. R., Musen, M. A., & Noy, N. F. (2013). BioPortal as a dataset of linked biomedical ontologies and terminologies in RDF. Semantic web, 4(3), 277-284.

% \bibitem{ref_article1}
% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

% \bibitem{ref_lncs1}
% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
% Springer, Heidelberg (2016). \doi{10.10007/1234567890}

% \bibitem{ref_book1}
% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
% Location (1999)

% \bibitem{ref_proc1}
% Author, A.-B.: Contribution title. In: 9th International Proceedings
% on Proceedings, pp. 1--2. Publisher, Location (2010)

% \bibitem{ref_url1}
% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
% Oct 2017
\end{thebibliography}
\end{document}

### 2020-04-06 paper.tex
modify title and add upto 16 pages

@@
 %
-\title{SPANG library: a controlled query set for FAIR SPARQL}
+\title{SPANG: a controlled query set with the FAIR principle}
 %
@@
 The problem is the lack of findability, accessibility and reusability of SPARQL queries that were once written.
-Given that SPARQL is an important framework of the Semantic Web, it is important to consolidate the eco-system to reuse SPARQL queries written in various project.
-Here, we present a extended specification for storing and distributing SPARQL queries named SPANG, and provide a pilot study of SPANG library.
-These features facilitate easy access to RDF datasets by users. 
-We present a metadata set for annotating a SPARQL query.
+%Given that SPARQL is an important framework of the Semantic Web, it is important to consolidate the eco-system to reuse SPARQL queries written in various project.
+%Here, we present a extended specification for storing and distributing SPARQL queries named SPANG, and provide a pilot study of SPANG library.
+Here we propose a SPARQL extention to construct a reusable query library to enrich the Semantic Web platform.
+As a use case, we constructed a reusable SPARQL query library, named SPANG library.
+Specifically, We challenged the issue of findability and accessibility of SPARQL queries.
+This specification leads to the construction of eco-system to reuse SPARQL queries to enrich the use of the Semantic Web platform.
+% These features facilitate easy access to RDF datasets by users. 
+Our contributions are as follows.
+1) We present a metadata set for annotating a SPARQL query.
 It enables to identify SPARQL query, and provides useful information fo the query.
-We also present a mechanism to parameterize the SPARQL query.
+2) We also present a mechanism to parameterize the SPARQL query.
 It make each query reusable in different settings.
 Further, the mechanism enables federated queries by combining multiple queries through Unix pipe. 
-Here, we developed spang command, as a client that helps users to generate queries.
+% Here, we developed spang command, as a client that helps users to generate queries.
 SPANG can create typical short queries according to the arguments specified by users like a \textit{one-liner} style in the Unix command line.
@@
 The following section includes: overview of the SPANG project, specification of SPANG templates, implementation of the SPANG library, and use case of SPANSG library.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Overview}
+Here we overview the structure of this paper.
+
+\subsection{SPARQL metadata}
+
+We propose a set of SPARQL metadata to annotate each SPARQL query, to make them more reusable.
+Those metadata are added as comment at the head of the SPARQL query, thus that does not violate the SPARQL specification. 
+The set of metadata increase the findability of SPARQL queries.
+
+As a use case, we developed a SPANG API to search for the set of SPARQL queries.
+
+\subsection{SPARQL parameterization}
+
+We propose the parapeterization mechanism of SPARQL query. It is crucial to reuse the SPARQL query for us to improve the productivity of the programming experiance on the Semantic Web platform.
+
+Using SPANG API, users can execute SPARQL query over the Web, with the given parameters.
+
+\subsection{SPANG library}
+
+According to the metadata and parameterization mechanism, we can construct a controlled set of SPARQL library which is reusable in various settings.
+
+\subsection{SPANG command}
+
+As an interface the the SPANG library, we constructed a command-line interface.
 
@@
 An example usage of the Microbial Genome Database (MBGD) SPARQL library published at http://mbgd.genome.ad.jp/sparql/library/ is as follows.
-\begin{quoting}
+
 \texttt{spang mbgd mbgdl:get\_ortholog K9Z723}
-\vspace{1pt}
-\end{quoting}
+
 where {\tt mbgd} is the MBGD SPARQL endpoint \citep{Chiba} and \texttt{mbgdl:} is a prefix for abbreviating the URI of the template {\tt get\_ortholog} in the MBGD SPARQL library (see supplementary data for the code).
@@
 SPANG portal web site is developed using Ruby on Rails. And it can be run on Docker. The SPANG query library is published on GitHub. Thus, users can run a portal site by their own.
+
+\subsection{Simple querying with SPARQL shortcuts}
+
+Specific command-line options, including \texttt{-S~\textit{SUBJECT}}, \texttt{-P~\textit{PREDICATE}}, \texttt{-O~\textit{OBJECT}}, \texttt{-L~\textit{LIMIT}}, and other modifiers, 
+are interpreted as shortcuts for generating typical SPARQL queries. 
+A simple example is:
+
+\texttt{spang uniprot -S tax:511145 -a}
+
+\noindent where the first argument is the target SPARQL endpoint and the following arguments are SPARQL shortcuts (the SPARQL endpoint can be specified in a URL or nickname for simplicity). 
+\texttt{uniprot} is a nickname for the UniProt SPARQL endpoint \citep{UniProt} and \texttt{tax:} is a prefix for URIs of NCBI taxonomy IDs. 
+This example command line searches the target database for statements that have taxonomy ID 511145 ({\it Escherichia coli} strain K-12 MG1655) as a subject.
+Using the \texttt{-a} option transforms the URIs in the
+ search result into abbreviated forms using predefined prefix declarations. For example,
+
+ \texttt{\textless http://www.w3.org/2000/01/rdf-schema\#subClassOf\textgreater}
+
+\noindent is transformed into \texttt{rdfs:subClassOf
+}.
+The result is output to the standard output in the form of tab-separated values by default, as it is suitable for processing by line-oriented Unix programs.
+In addition, combination of subject, predicate, and object is possible according to the following.
+
+\texttt{spang uniprot -S tax:511145 -P up:otherName}
+
+\noindent where predicate {\tt up:otherName} is specified to further confine the results to other names. 
+For the full list of available command-line options, simply type the command {\tt spang}.
+\vspace*{-5pt}
+
+\subsection{Combinatorial execution of multiple queries}
+
+SPANG combines multiple queries through a Unix pipe. 
+Combining a {\tt spang} command in shortcut mode and another one in template mode is also possible.
+An example of such a combinatorial query is shown in Fig.~\ref{fig:01}.
+The first {\tt spang} command is in template mode, which is the same as that presented in the Section 2.3. 
+This command searches the MBGD database for orthologs of a protein {\tt K9Z723}. 
+The obtained list of proteins are used in the second query, which searches the UniProt database for annotations of the given list of proteins. 
+The option \texttt{-S 1} specifies the values from the first column of the standard input as subject.
+This combinatorial query enables integrative use of two databases distributed across the Web. 
+Here, the output of the first command can be further modified by altering the second command.
+For example:
+\begin{quoting}
+\texttt{spang mbgd mbgdl:get\_ortholog K9Z723 | spang uniprot uniprot\_xref PDB}
+\vspace{1pt}
+\end{quoting}
+where {\tt uniprot\_xref} is a SPARQL template (see supplementary data for the code), which retrieves cross-references from the UniProt IDs given in the standard input to the database specified as the parameter (in this example, {\tt PDB}).
+This example command line searches for entries in the Protein Data Bank (PDB) \citep{Berman} among orthologs of {\tt K9Z723}.
 

### 2020-04-06 paper.tex
Updates from Overleaf

@@
 %
-\title{SPANG: a controlled query set with the FAIR principle}
+\title{SPANG: constructing a controlled set of queries with the FAIR principle}
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-\section{Overview}
+\section{The FAIR principle}
+
+Not only the RDF dataset, but also the SPARQL queries are important resource to be shared on the Semantic Web platform.
+Thus, we applied the FAIR principle which have been applied to the RDF datasets, into SPARQL queries.
+
+Here we overview the preliminaries for the FAIR principle.
+It shoulbe noted that the FIAR principle can be applied not only to the dataset resources but also to other type of resources including software tools.
+
+Here, we provide the FAIR principle in the context of SPARQL queries.
+
+\subsection{Findable}
+\begin{itemize}
+    \item Assign global identifier
+    \item Rich metadata
+    \item Include the identifier of the data they describe
+    \item Registered and indexed
+\end{itemize}
+
+\subsection{Accessible}
+\begin{itemize}
+    \item Retrievable by identifier
+    \item Metadata are accessible
+\end{itemize}
+
+\subsection{Interoperable}
+\begin{itemize}
+    \item Use a formal, accessible, shared, and broadly applicable language for knowledge representation.
+    \item Use vocabularies that follow FAIR principles.
+    \item Include qualified references to others
+\end{itemize}
+
+\subsection{Reusable}
+\begin{itemize}
+    \item Richly described with a plurality of accurate and relevant attributes
+    \begin{itemize}
+        \item released with a clear and accessible data usage license
+        \item associated with detailed provenance
+        \item meet domain-relevant community standards
+    \end{itemize}
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\section{SPANG overview}
 Here we overview the structure of this paper.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{SPANG}
+\subsection{SPANG portal}
 SPANG is originally developed for "SARQLing" the RDF dataset from command line. Here, we re-implemented the SPANG using Node.js and now the functionality is available through Web browser.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-\section{SPANG library}
+\section{SPANG specifications}
 
@@
     },
-    {
-      "name": "gene_disease",
-      "title": "Get disease associated with NCBI gene ID",
-      "uri": "http://localhost:7070/api/disgenet/gene_disease",
-      "endpoint": "http://rdf.disgenet.org/sparql/",
-      "param": [
-        {
-          "name": "arg1",
-          "default": "675"
-        }
-      ]
-    },
-    {
-      "name": "get_gda",
-      "title": "Get specific type of gene-disease association",
-      "uri": "http://localhost:7070/api/disgenet/get_gda",
-      "endpoint": "http://rdf.disgenet.org/sparql/",
-      "param": [
-        {
-          "name": "arg1",
-          "default": "SIO_001120"
-        },
-        {
-          "name": "arg2",
-          "default": "10"
-        }
-      ]
-    },
-    {
-      "name": "list_gda_sources",
-      "title": "List sources of gene-disease association",
-      "uri": "http://localhost:7070/api/disgenet/list_gda_sources",
-      "endpoint": "http://rdf.disgenet.org/sparql/",
-      "param": [
-
-      ]
-    },
-    {
-      "name": "list_gene_disease",
-      "title": "List gene disease associations",
-      "uri": "http://localhost:7070/api/disgenet/list_gene_disease",
-      "endpoint": "http://rdf.disgenet.org/sparql/",
-      "param": [
-        {
-          "name": "arg1",
-          "default": "10"
-        }
-      ]
-    },
-    {
-      "name": "regex_disease",
-      "title": "Search the NCI Thesaurus for specific diseases",
-      "uri": "http://localhost:7070/api/disgenet/regex_disease",
-      "endpoint": "http://rdf.disgenet.org/sparql/",
-      "param": [
-        {
-          "name": "arg1",
-          "default": "breast"
-        }
-      ]
-    },
-    {
-      "name": "regex_gda_disease",
-      "title": "Regex seach for specific diseases that have gene-disease association information",
-      "uri": "http://localhost:7070/api/disgenet/regex_gda_disease",
-      "endpoint": "http://rdf.disgenet.org/sparql/",
-      "param": [
-        {
-          "name": "arg1",
-          "default": "alzheimer"
-        }
-      ]
-    },
-    {
-      "name": "uniprot2disease",
-      "title": "Get diseases associated with given UniProt IDs",
-      "uri": "http://localhost:7070/api/disgenet/uniprot2disease",
-      "endpoint": "http://rdf.disgenet.org/sparql/",
-      "param": [
-
-      ]
-    },
-    {
-      "name": "uniprot2disease_curated",
-      "title": "Get diseases associated with given UniProt IDs",
-      "uri": "http://localhost:7070/api/disgenet/uniprot2disease_curated",
-      "endpoint": "http://rdf.disgenet.org/sparql/",
-      "param": [
-
-      ]
-    },
-    {
-      "name": "uniprot2disease_curated_none",
-      "title": "Get diseases associated with given UniProt IDs",
-      "uri": "http://localhost:7070/api/disgenet/uniprot2disease_curated_none",
-      "endpoint": "http://rdf.disgenet.org/sparql/",
-      "param": [
-
-      ]
-    },
-    {
-      "name": "uniprot2disease_none",
-      "title": "Get diseases associated with given UniProt IDs",
-      "uri": "http://localhost:7070/api/disgenet/uniprot2disease_none",
-      "endpoint": "http://rdf.disgenet.org/sparql/",
-      "param": [
-
-      ]
-    }
-  ],
-  "general": [
-    {
-      "name": "find_term_uri",
-      "title": "Find classes or properties (regex search for URIs or labels)",
-      "uri": "http://localhost:7070/api/general/find_term_uri",
-      "endpoint": "http://dbpedia.org/sparql",
-      "param": [
-        {
-          "name": "arg1",
-          "default": "homolo"
-        }
-      ]
-    },
-    {
-      "name": "graphs_bug",
-      "title": "SELECT DISTINCT ?graph, instead of GROUP BY ?graph, returns less results (Virtuoso 7.1.0)",
-      "uri": "http://localhost:7070/api/general/graphs_bug",
-      "endpoint": "http://dbpedia.org/sparql",
-      "param": [
-
-      ]
-    },
-    {
-      "name": "label",
-      "title": "",
-      "uri": "http://localhost:7070/api/general/label",
-      "endpoint": "http://dbpedia.org/sparql",
-      "param": [
-
-      ]
-    },
-    {
-      "name": "link_select",
-      "title": "Links from a specific instance",
-      "uri": "http://localhost:7070/api/general/link_select",
-      "endpoint": "http://dbpedia.org/sparql",
-      "param": [
-
-      ]
-    },
-    {
-      "name": "regex_uri",
-      "title": "Regex search for URIs (subjects of triples)",
-      "uri": "http://localhost:7070/api/general/regex_uri",
-      "endpoint": "http://dbpedia.org/sparql",
-      "param": [
-
-      ]
-    },
-    {
-      "name": "search_for_class",
-      "title": "Free text search in Virtuoso",
-      "uri": "http://localhost:7070/api/general/search_for_class",
-      "endpoint": "http://dbpedia.org/sparql",
-      "param": [
-
-      ]
-    },
-    {
-      "name": "search_label_for_class",
-      "title": "Free text search in Virtuoso",
-      "uri": "http://localhost:7070/api/general/search_label_for_class",
-      "endpoint": "http://dbpedia.org/sparql",
-      "param": [
-
-      ]
-    },
-    {
-      "name": "search_label_not_class",
-      "title": "Free text search in Virtuoso (count instances of each class)",
-      "uri": "http://localhost:7070/api/general/search_label_not_class",
-      "endpoint": "http://dbpedia.org/sparql",
-      "param": [
-
-      ]
-    }
+    ...
   ]
@@
 %%%%%%%%%%%%%%%%%%%%
-\section{Use cases}
 
@@
 % For the full list of available command-line options, simply type the command {\tt spang}.
-
-\subsection{Using SPARQL templates with parameters}
-
-Although SPARQL shortcuts are useful for simple querying with typical query patterns, they do not cover various
-queries with complicated patterns. 
-Thus, SPANG provides a mechanism to accept SPARQL templates to generate arbitrary query patterns. 
-An example query is:
-
-\texttt{spang uniprot taxtree\_ancestor 511145 -ac}
-
-\noindent where the first argument is the target SPARQL endpoint and the following arguments are SPARQL templates and parameters.
-{\tt taxtree\_ancestor} is the name of a SPARQL template included in the predefined SPARQL library (see supplementary data for the code), {\tt 511145} is the parameter, {\tt -a} is the option for abbreviating results, and {\tt -c} is for aligning output columns for easier reading.
-The specified parameter replaces the placeholder included in the template before execution. 
-This example query traverses the NCBI taxonomy tree from the given ID (511145) to the root node and outputs scientific names in each taxonomic rank.
-
-Available SPARQL templates are not limited to the local library.
-If SPARQL libraries are published on the Web, the users can call the templates by means of URIs across the Web.
-An example usage of the Microbial Genome Database (MBGD) SPARQL library published at http://mbgd.genome.ad.jp/sparql/library/ is as follows.
-
-\texttt{spang mbgd mbgdl:get\_ortholog K9Z723}
-
-where {\tt mbgd} is the MBGD SPARQL endpoint \citep{Chiba} and \texttt{mbgdl:} is a prefix for abbreviating the URI of the template {\tt get\_ortholog} in the MBGD SPARQL library (see supplementary data for the code).
-The template can be specified in the full URI or in abbreviated form using the predefined prefix declarations.
-This example query searches the MBGD database \citep{Uchiyama} for the orthologs of a protein \texttt{K9Z723} (Photosystem II lipoprotein Psb27).
-
-The following example command line gives a parameter to the query template, and execute to the DisGeNet endpoint.
-\texttt{spang gene\_disease.rq --param disease=C0751955}
 
@@
 Using the \texttt{-a} option transforms the URIs in the
- search result into abbreviated forms using predefined prefix declarations. For example,
-
+ search result into abbreviated forms using predefined prefix declarations. For example,\\
 \texttt{\textless http://www.w3.org/2000/01/rdf-schema\#subClassOf\textgreater} 
-
-\noindent is transformed into \texttt{rdfs:subClassOf
+is transformed into \texttt{rdfs:subClassOf
 }.
@@
 \vspace*{-5pt}
+
+\subsection{Using SPARQL templates with parameters}
+
+Although SPARQL shortcuts are useful for simple querying with typical query patterns, they do not cover various
+queries with complicated patterns. 
+Thus, SPANG provides a mechanism to accept SPARQL templates to generate arbitrary query patterns. 
+An example query is:
+
+\texttt{spang uniprot taxtree\_ancestor 511145 -ac}
+
+\noindent where the first argument is the target SPARQL endpoint and the following arguments are SPARQL templates and parameters.
+{\tt taxtree\_ancestor} is the name of a SPARQL template included in the predefined SPARQL library (see supplementary data for the code), {\tt 511145} is the parameter, {\tt -a} is the option for abbreviating results, and {\tt -c} is for aligning output columns for easier reading.
+The specified parameter replaces the placeholder included in the template before execution. 
+This example query traverses the NCBI taxonomy tree from the given ID (511145) to the root node and outputs scientific names in each taxonomic rank.
+
+Available SPARQL templates are not limited to the local library.
+If SPARQL libraries are published on the Web, the users can call the templates by means of URIs across the Web.
+An example usage of the Microbial Genome Database (MBGD) SPARQL library published at http://mbgd.genome.ad.jp/sparql/library/ is as follows.
+
+\texttt{spang mbgd mbgdl:get\_ortholog K9Z723}
+
+where {\tt mbgd} is the MBGD SPARQL endpoint \citep{Chiba} and \texttt{mbgdl:} is a prefix for abbreviating the URI of the template {\tt get\_ortholog} in the MBGD SPARQL library (see supplementary data for the code).
+The template can be specified in the full URI or in abbreviated form using the predefined prefix declarations.
+This example query searches the MBGD database \citep{Uchiyama} for the orthologs of a protein \texttt{K9Z723} (Photosystem II lipoprotein Psb27).
+
+The following example command line gives a parameter to the query template, and execute to the DisGeNet endpoint.
+\texttt{spang gene\_disease.rq --param disease=C0751955}
 

### 2020-04-07 paper.tex
add references and update introduction etc.

@@
 %
-\title{SPANG: constructing a controlled set of queries with the FAIR principle}
+\title{SPANG: constructing a controlled set of SPARQL queries with the FAIR principle}
 %
@@
 How can we maximize the value of accumulated SPARQL queries?
-An increasing number of datasets have been published in the Resource Description Framework (RDF) and the SPARQL standard allows interoperable framework for querying the RDF datasets; however, reuse of SPARQL queries remains in a limited level.
-The problem is the lack of findability, accessibility and reusability of SPARQL queries that were once written.
+An increasing number of datasets have been published in the Resource Description Framework (RDF) and the SPARQL standard allows interoperable framework for querying the RDF datasets; however, reuse of SPARQL queries remains limited due to the lack of findability, accessibility and reusability of SPARQL queries that were once written.
 %Given that SPARQL is an important framework of the Semantic Web, it is important to consolidate the eco-system to reuse SPARQL queries written in various project.
@@
 As a use case, we constructed a reusable SPARQL query library, named SPANG library.
-Specifically, We challenged the issue of findability and accessibility of SPARQL queries.
-This specification leads to the construction of eco-system to reuse SPARQL queries to enrich the use of the Semantic Web platform.
+Our contribution is the improvement of findability and accessibility of SPARQL queries.
 % These features facilitate easy access to RDF datasets by users. 
-Our contributions are as follows.
+More specifically,
 1) We present a metadata set for annotating a SPARQL query.
@@
 This study make SPARQL queries more findable, accessible, interoperable, and reusable, i.e., pushing forward FAIR SPARQL.
-SPANG is freely available at \url{https://spang.dbcls.jp}.
+This specification leads to the construction of eco-system to reuse SPARQL queries to enrich the use of the Semantic Web platform.
+SPANG project resources is available at \url{https://spang.dbcls.jp}.
 \keywords{SPARQL query \and RDF store \and template library.}
@@
 \section{Introduction}
+
 An increasing number of datasets have been published in the Resource Description Framework (RDF).
-Although the SPARQL language provides a basis for exploiting RDF databases, writing a raw SPARQL code often becomes a burden for users. 
+SPARQL is the standardized query langage, and many Semantic Web users write queries in SPARQL, with a great amount of efforts.
+Those queries are valuable resource.
+However, due to the limitation of SPARQL specifications, the reuse of those queries are limited. How can we maximize the value of accumulated SPARQL queries?
+%Although the SPARQL language provides a basis for exploiting RDF databases, writing a raw SPARQL code often becomes a burden for users. 
 % Several approaches for support of SPARQL writing exist. One is to develop SPARQL editors that have useful functionalities 
@@
 % Despite the efforts of previous studies, Semantic Web users remain bound to the task of SPARQL coding.
-Here, we developed SPANG, a novel SPARQL client
-that addresses this issue of SPARQL coding by simple query generation and reusing existing query templates.
-SPANG
+%Here, we developed SPANG, a novel SPARQL client
+%that addresses this issue of SPARQL coding by simple query generation and reusing existing query templates.
+%SPANG
 %, with its unique features, 
-minimizes the burden of coding SPARQL,
-thereby enhancing integrative analysis of distributed RDF databases.
+%minimizes the burden of coding SPARQL,
+%thereby enhancing integrative analysis of distributed RDF databases.
 
@@
 Findability, Accesibility, Reusablility should be addressed, to make the most of SPARQL queries as resources.
+
+One of the key principle in the Semantic Web is the FAIR principle: findable, accessible, interoperable and reusable.
+Interestingly, the FAIR principle can be applied not only to the RDF data, but also other resource, like software.
+As the SPARQL queries are important component of the Semantic Web community,
+they should be shared in a solid principle.
+The FAIR principle is suitable for this aim.
 
@@
 Here, we decided to follow the FAIR principle and extend the SPARQL specifications for more efficient development of the Semantic Web.
+
+Semantic Web users often write SPARQL queris.
+However, the SPARQL lacks the parameterization mechanism, thus, users write queries for their specific use cases.
+But good SPARQL queries can be reused.
+Actually, writing good query requires much efforts, thus, they should be reused to improve the productivity.
+Thus, considering the reusability of SPARQL queries are crucial to enrich the Semantic Web community.
+How can we improve the reusability of SPARQL?
+
+One of the key to improve the reusability of queries is parameterization.
+Parameterization make the query more reusable.
+Using the template query with parameters, the same query can be applied to many use cases.
+There can be several types of parameterization.
+The SPARQL variables can be considered as parameter.
+In that case, values to the parameters can replace them.
+On the other hands, part of the URI or literals can be parameterized.
+In that case also, values to the parameters can replace them.
+Another mechanism to use template is to give binding to the variables.
 
@@
 
-As a SPARQL parser, SPARQL.js is available.
+As a SPARQL formatter, some software are available.
+rdfstore-js\cite{rdfstore-js} has SPARQL parser, but does not have formatter.
+SPARQL.js~\cite{sparql-js} implements parser and formatter. However, there are no formatting rule explicitly defined.
+Jena package~\cite{jena} includes parser and formatter. However, it does not define formatting rule.
+
+Bioqueries~\cite{bioqueries} have tried to collect SPARQL queries as community effort. It increase the findability and reusability.
+However, the query can only be executed on the web site.
+Users should copy and paste the queries into their own software.
+In contrast, we tried to build a software network on top of the Semantic Web platform.
+
+Client for calling parameterized queries is still limited.
+ASQC~\cite{asqc} command enables the execution of parameterized queries or queries with given variable bindings. However, it is still not possible to execute the quries publised online across the Web.
 
@@
 
+\bibitem{bioqueries}
+García-Godoy, M.
+J., Navas-Delgado, I., & Aldana-Montes, J.
+(2011, December).
+Bioqueries: a social community sharing experiences while querying biological linked data.
+In Proceedings of the 4th international workshop on semantic web applications and tools for the life sciences (pp.
+24-31).
+
 \bibitem{umaka}
@@
 
+\bibitem{rdfstore-js}
+Hernández, A. G., & GARCıA, M. N. M. (2012). A JavaScript RDF store and application library for linked data client applications. In Devtracks of the, WWW2012, conference. Lyon, France.
+
+\bibitem{sparql-js}
+SPARQL.js – A SPARQL 1.1 parser for JavaScript
+\url{https://github.com/RubenVerborgh/SPARQL.js}
+
+\bibitem{jena}
+Grobe, M. (2009, October). Rdf, jena, sparql and the'semantic web'. In Proceedings of the 37th annual ACM SIGUCCS fall conference: communication and collaboration (pp. 131-138).
+
 \bibitem{spin}
@@
 \url{https://spinrdf.org/}
+
+\bibitem{sparql12}
+SPARQL 1.2 Community Group
+\url{https://github.com/w3c/sparql-12}
 
@@
 Salvadores, M., Alexander, P. R., Musen, M. A., & Noy, N. F. (2013). BioPortal as a dataset of linked biomedical ontologies and terminologies in RDF. Semantic web, 4(3), 277-284.
+
+\bibitem{asqc}
+ASQC provides a simple command-line SPARQL query client.
+\url{https://github.com/gklyne/asqc}
 

### 2020-05-23 paper.tex
v1.0

@@
 %
-\title{SPANG: constructing a controlled set of SPARQL queries with the FAIR principle}
+\title{SPANG library: making SPARQL FAIR in controlled query sets}
 %
-\titlerunning{SPANG library}
+\titlerunning{SPANG library: making SPARQL FAIR}
 % If the paper title is too long for the running head, you can set
@@
 How can we maximize the value of accumulated SPARQL queries? 
+SPARQL contributes to the standardized interface to the RDF, and maximizing the reusability of RDF; however, reusability of SPARQL itself remains to be addressed.
+SPARQL is a key component of the Semantic Web, thus the reusability of SPARQL is important.
+FAIRification of the SPARQL is a plausible way to make SPARQL interoperable and reusable.
 An increasing number of datasets have been published in the Resource Description Framework (RDF) and the SPARQL standard allows interoperable framework for querying the RDF datasets; however, reuse of SPARQL queries remains limited due to the lack of findability, accessibility and reusability of SPARQL queries that were once written.
@@
 %Here, we present a extended specification for storing and distributing SPARQL queries named SPANG, and provide a pilot study of SPANG library.
-Here we propose a SPARQL extention to construct a reusable query library to enrich the Semantic Web platform.
+Here we propose a SPARQL extension to construct a reusable query library to enrich the Semantic Web platform.
 As a use case, we constructed a reusable SPARQL query library, named SPANG library.
@@
 2) We also present a mechanism to parameterize the SPARQL query.
-It make each query reusable in different settings.
+It makes each query reusable in different settings.
 Further, the mechanism enables federated queries by combining multiple queries through Unix pipe. 
@@
 This specification leads to the construction of eco-system to reuse SPARQL queries to enrich the use of the Semantic Web platform.
-SPANG project resources is available at \url{https://spang.dbcls.jp}.
+SPANG project resources are available at \url{https://spang.dbcls.jp}.
+
+In this study, we present the FAIRification process of SPARQL and demonstarate the usefulness of the result.
+
 \keywords{SPARQL query \and RDF store \and template library.}
+
 \end{abstract}
@@
 
+SPARQL contributes to the standardized interface to RDF, and miximizing the RDF reusability. Reusability is the key to miximize the value of accumulated open data and software.
 An increasing number of datasets have been published in the Resource Description Framework (RDF).
@@
 Those queries are valuable resource.
-However, due to the limitation of SPARQL specifications, the reuse of those queries are limited. How can we maximize the value of accumulated SPARQL queries?
+However, due to the limitation of SPARQL specifications, the reuse of those queries are limited. 
+So, how can we maximize the value of accumulated SPARQL queries?
 %Although the SPARQL language provides a basis for exploiting RDF databases, writing a raw SPARQL code often becomes a burden for users. 
@@
 
-SPARQL is a fundamental technology for querying RDF data.
+SPARQL is a fundamental technology for querying RDF data contributing an interoperable interface to the Semantic Web.
 However, is is not designed for reusability.
@@
 
-The SPANG package includes the main {\tt spang} command, which can be used in the Unix command-line environment.
-In general, the {\tt spang} command help users query RDF databases by dynamically generating SPARQL queries according to the command-line options or arguments. 
-More specifically, {\tt spang} has two execution modes: 
-1) simple mode; for a simple query, users must only specify some command-line options to generate the query without writing any SPARQL code, and
-2) template mode; for a more complex query, users can generate the query using a predefined SPARQL template and parameters.
-Basically, each {\tt spang} process submits a query to a specific database,
-and the {\tt spang} process can be combined with other Unix processes through a Unix pipe. 
-Notably, multiple {\tt spang} commands each with distinct target database can be combined through a Unix pipe, thereby realizing federated queries to multiple databases (see Section 2.4).
+% The SPANG package includes the main {\tt spang} command, which can be used in the Unix command-line environment.
+% In general, the {\tt spang} command help users query RDF databases by dynamically generating SPARQL queries according to the command-line options or arguments. 
+% More specifically, {\tt spang} has two execution modes: 
+% 1) simple mode; for a simple query, users must only specify some command-line options to generate the query without writing any SPARQL code, and
+% 2) template mode; for a more complex query, users can generate the query using a predefined SPARQL template and parameters.
+% Basically, each {\tt spang} process submits a query to a specific database,
+% and the {\tt spang} process can be combined with other Unix processes through a Unix pipe. 
+% Notably, multiple {\tt spang} commands each with distinct target database can be combined through a Unix pipe, thereby realizing federated queries to multiple databases (see Section 2.4).
 
-To reduce the burden of coding SPARQL, the SPANG package provides predefined configurations about nicknames for SPARQL endpoints, prefix declarations for URIs, and SPARQL libraries (see Section 3).
+% To reduce the burden of coding SPARQL, the SPANG package provides predefined configurations about nicknames for SPARQL endpoints, prefix declarations for URIs, and SPARQL libraries (see Section 3).
 
@@
 
-The following section includes: overview of the SPANG project, specification of SPANG templates, implementation of the SPANG library, and use case of SPANSG library.
+% The following section includes: overview of the SPANG project, specification of SPANG templates, implementation of the SPANG library, and use case of SPANSG library.
+
+% \begin{figure}
+% \center
+% \includegraphics[width=1.0\textwidth]{spang_top.png}
+% \caption{SPANG web site}
+% \label{fig:spang_top}
+% \end{figure}
 
 %%%%%%%%%%%%%%%%%%%%%%%%
-\section{The FAIR principle}
+\section{FAIR principle}
+
+The FAIR guiding principle aims to enhance the Findability, Accessibility, Interoperability and Reusability of digital resources.
 
@@
 
-\subsection{Findable}
-\begin{itemize}
-    \item Assign global identifier
-    \item Rich metadata
-    \item Include the identifier of the data they describe
-    \item Registered and indexed
-\end{itemize}
+\subsection{Findability}
+The first step is using data to find SPARQL queries.
+Metadata should be easy to find for both humans and computers.
+Machine-readable metadata are essential for automatic discovery of resources, so this is essential component.
+% \begin{itemize}
+%     \item Assign global identifier
+%     \item Rich metadata
+%     \item Include the identifier of the data they describe
+%     \item Registered and indexed
+% \end{itemize}
 
-\subsection{Accessible}
-\begin{itemize}
-    \item Retrievable by identifier
-    \item Metadata are accessible
-\end{itemize}
+\subsection{Accessibility}
+Once the user finds the required data, the user needs to know how can they be accessed, possibly including authentication and authorisation.
+% \begin{itemize}
+%     \item Retrievable by identifier
+%     \item Metadata are accessible
+% \end{itemize}
 
-\subsection{Interoperable}
-\begin{itemize}
-    \item Use a formal, accessible, shared, and broadly applicable language for knowledge representation.
-    \item Use vocabularies that follow FAIR principles.
-    \item Include qualified references to others
-\end{itemize}
+\subsection{Interoperability}
+The data usually need to be integrated with other data. In addition, the data need to interoperate with application or workflows for analysis, storage, and processing.
+% \begin{itemize}
+%     \item Use a formal, accessible, shared, and broadly applicable language for knowledge representation.
+%     \item Use vocabularies that follow FAIR principles.
+%     \item Include qualified references to others
+% \end{itemize}
 
-\subsection{Reusable}
-\begin{itemize}
-    \item Richly described with a plurality of accurate and relevant attributes
-    \begin{itemize}
-        \item released with a clear and accessible data usage license
-        \item associated with detailed provenance
-        \item meet domain-relevant community standards
-    \end{itemize}
-\end{itemize}
+\subsection{Reusability}
+The ultimate goal of FAIR is to optimise the reuse of data. To achieve this, metadata should be well-described so that they can be replicated and/or combined in different settings.
+% \begin{itemize}
+%     \item Richly described with a plurality of accurate and relevant attributes
+%     \begin{itemize}
+%         \item released with a clear and accessible data usage license
+%         \item associated with detailed provenance
+%         \item meet domain-relevant community standards
+%     \end{itemize}
+% \end{itemize}
+
+The process of making SPARQL FAIR ("FAIRification") can be described in multiple steps~\cite{fairification}.
+Most of the requirements for findability and accessibility can be achieved at the metadata level. Interoperability and reuse requires more efforts at the SPARQL code level.
 
 %%%%%%%%%%%%%%%%%%%%%%%%
-\section{SPANG overview}
-Here we overview the structure of this paper.
+\section{FAIRification of SPARQL}
 
-\subsection{SPARQL metadata}
+In the previous section, we showed the core idea of the FAIR principle.
 
-We propose a set of SPARQL metadata to annotate each SPARQL query, to make them more reusable.
-Those metadata are added as comment at the head of the SPARQL query, thus that does not violate the SPARQL specification. 
-The set of metadata increase the findability of SPARQL queries.
+So, what is the relationship between FAIR principle and the Semantic Web?
+The core technology constituting the Semantic Web is RDF, OWL, and SPARQL. RDF and OWL follows the FAIR principle. However, SPARQL is not FAIR.
 
-As a use case, we developed a SPANG API to search for the set of SPARQL queries.
+So, what is the problem of the FAIRification status of SPARQL?
+SPARQL is important component of the Semantic Web. The use of SPARQL query is essential for the Semantic Web community.
 
-\subsection{SPARQL parameterization}
-
-We propose the parapeterization mechanism of SPARQL query. It is crucial to reuse the SPARQL query for us to improve the productivity of the programming experiance on the Semantic Web platform.
-
-Using SPANG API, users can execute SPARQL query over the Web, with the given parameters.
-
-\subsection{SPANG library}
-
-According to the metadata and parameterization mechanism, we can construct a controlled set of SPARQL library which is reusable in various settings.
-
-\subsection{SPANG command}
-
-As an interface the the SPANG library, we constructed a command-line interface.
-
-\subsection{SPANG portal}
-SPANG is originally developed for "SARQLing" the RDF dataset from command line. Here, we re-implemented the SPANG using Node.js and now the functionality is available through Web browser.
-
-Figure~\ref{fig:spang_top} is the top page of SPANG, which includes links to GitHub, Documentation, and SPANG library.
-
-\begin{figure}
-\center
-\includegraphics[width=1.0\textwidth]{spang_top.png}
-\caption{SPANG web site}
-\label{fig:spang_top}
-\end{figure}
-
-Figure~\ref{fig:spang_lib} is the list of the target SPARQL endpoints. It also lists the SPARQL templates available in general for various endpoints.
-
-\begin{figure}
-\center
-\includegraphics[width=1.0\textwidth]{spang_lib.png}
-\caption{SPANG library}
-\label{fig:spang_lib}
-\end{figure}
-
-Figure~\ref{fig:spang_lib} is the list of SPARQL templates for DisGeNet SPARQL endpoint.
-A short name for the SPARQL template, descriptin of the query, and example parameters are shown.
-
-\begin{figure}
-\center
-\includegraphics[width=1.0\textwidth]{spang_disgenet.png}
-\caption{SPANG templates for DisGeNet SPARQL endpoint}
-\label{fig:spang_disgenet}
-\end{figure}
-
-Figure~\ref{fig:spang_disease_gene_query} shows a query for DiesGeNet SPARQL endpoint to get disase gene relationship. 
-Figure~\ref{fig:spang_disease_gene_result} shows the result of the query. Thus, users can get the results only by clicking on the web pages, browsing the SPARQL template on the SPANG web site.
-
-\begin{figure}
-\center
-\includegraphics[width=1.0\textwidth]{spang_disease_gene_query.png}
-\caption{SPANG templates for DisGeNet SPARQL endpoint}
-\label{fig:spang_disease_gene_query}
-\end{figure}
-
-\begin{figure}
-\center
-\includegraphics[width=1.0\textwidth]{spang_disease_gene_result.png}
-\caption{SPANG templates for DisGeNet SPARQL endpoint}
-\label{fig:spang_disease_gene_result}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\section{SPANG specifications}
+The key is the metadata.
 
@@
 To make SPARQL queries findable, we propose to add metadata to SPARQL.
-The SPARQL metadata includes:
-\begin{itemize}
-    \item Title
-    \item Description
-    \item Topic
-    \item Parameters: name, default value, class
-    \item Target endpoint
-\end{itemize}
+The SPARQL metadata includes: title, description, target endpoint, and parameters with its name, default value, and classes.
 
@@
 
-\subsubsection{SPANG coding rules}
-We defined a coding rule for SPARQL and its extention in SPANG framework.
-Coding rule is important for productivity of shared coding tasks and effective maintenance.
-It also helps to make debug process easier; weird look suggests possible bugs.
-\begin{itemize}
-    \item Header lines: query can start with header lines as comment lines.
-Metadata can be added at the top of the query as comment lines.
-Multiple lines are allowed.
-If multiple lines are described, they are written in sequential without blank lines.
-After the metadata lines, a blank line comes.
-    \item Prefix: prefix declaration comes in sequential lines. Each of before and after the prefix declaration lines, a blank line exists.
-    \item Cases: the SPARQL keywords should be in upper case characters. variabl names comes with ? followed by lower case characters.
-    \item Literal: the literals are surrounded by "".
-    \item Indent: indentation depth is two spaces.
-    \item Spaces: a space exists between keywords and variables. A space exists before , or ; or . .
-    \item Newline: a newline exists before the keyword \texttt{WHERE} and after \texttt{\{}.
-A new line exist after ; or .
-but not after ,.
-After the newline following ;, an indent follows.
-A newline exist before query modifiers such as \texttt{ORDER BY} or \texttt{LIMIT}.
-\end{itemize}
-We developed a reformatter of the SPARQL code as described below.
-
 \subsection{Reusability of SPARQL queries}
@@
 We implemented templating mechanism using a general freamework, mustash.
-
-\subsection{Example query}
-An example query in the SPANG library is shown below.
-The DisGeNet endpoint is specified.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\section{SPANG API}
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\section{SPANG specifications}
+
+The core of the SPANG specification is the SPARQL metadata and templating mechanism for increasing the reusability of the SPARQL queries.
+
+An example query in the SPANG library is shown below.
+The DisGeNet endpoint~\cite{disgenet} is specified.
+
+\subsection{SPARQL metadata}
+
+We propose a set of SPARQL metadata to annotate each SPARQL query, to make them more reusable.
+Those metadata are added as comment at the head of the SPARQL query, thus that does not violate the SPARQL specification. 
+The set of metadata increase the findability of SPARQL queries.
+
+As a use case, we developed a SPANG API to search for the set of SPARQL queries.
+
+\subsection{SPARQL parameterization}
+
+We propose the parapeterization mechanism of SPARQL query. It is crucial to reuse the SPARQL query for us to improve the productivity of the programming experiance on the Semantic Web platform.
+
+Using SPANG API, users can execute SPARQL query over the Web, with the given parameters.
+
+\subsection{SPANG library API}
+According to the metadata and parameterization mechanism, we can construct a controlled set of SPARQL library which is reusable in various settings.
 
@@
 
-\subsection{Library API}
-
-\subsection{Query API}
-
-The following command returns the list of query libraries.
+The following command returns the list of libraries.
 
 \texttt{curl https://spang-portal.dbcls.jp/api/library}
+
+The results is shown in Figure~\ref{fig:libs-api-out} as JSON format.
+
+The following command returns the list of query in a library.
+
+\texttt{curl https://spang-portal.dbcls.jp/api/library/disgenet}
+
+The results is shown in Figure~\ref{fig:lib-api-out} as JSON format.
+
+\subsection{SPANG query API}
+
+The following command returns the result of the query, with the given paramter.
+
+\texttt{curl https://spang-portal.dbcls.jp/api/library/disgenet/gene\_disease.rq?arg1=678}
+
+Figure~\ref{fig:spang_disease_gene_query} shows a query for DiesGeNet SPARQL endpoint to get disase gene relationship. 
+Figure~\ref{fig:spang_disease_gene_result} shows the result of the query. Thus, users can get the results only by clicking on the web pages, browsing the SPARQL template on the SPANG web site.
+
+The following command searches for queries with keywords.
+
+\subsection{SPANG portal}
+SPANG is originally developed for "SARQLing" the RDF dataset from command line. Here, we re-implemented the SPANG using Node.js and now the functionality is available through Web browser.
+
+% Figure~\ref{fig:spang_top} is the top page of SPANG, which includes links to GitHub, Documentation, and SPANG library.
+
+Figure~\ref{fig:spang_lib} is the list of the target SPARQL endpoints. It also lists the SPARQL templates available in general for various endpoints.
+
+Figure~\ref{fig:spang_lib} is the list of SPARQL templates for DisGeNet SPARQL endpoint.
+A short name for the SPARQL template, descriptin of the query, and example parameters are shown.
+
+\begin{figure}
+\center
+\includegraphics[width=1.0\textwidth]{spang_lib.png}
+\caption{SPANG library}
+\label{fig:spang_lib}
+\end{figure}
 
@@
 \caption{List of in query libraries obtained by API}
-\label{fig:example-rdf}
+\label{fig:libs-api-out}
 \end{figure}
 
-The following command returns the result of the query, with the given paramter.
-
-\texttt{curl https://spang-portal.dbcls.jp/api/library/disgenet/gene\_disease.rq?arg1=678}
-
-\begin{figure}[!t]
-\begin{scriptsize}
-\begin{verbatim}
-
-"Precursor T-Cell Lymphoblastic Leukemia-Lymphoma"@en	"0.31"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/28671688>	"2017"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Precursor T-Cell Lymphoblastic Leukemia-Lymphoma"@en	"0.31"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/20622884>	"2010"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Colorectal Cancer"@en	"0.3"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/25944804>	"2016"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Colorectal Carcinoma"@en	"0.3"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/25944804>	"2016"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Colorectal Neoplasms"@en	"0.3"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/25944804>	"2016"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Malignant neoplasm of prostate"@en	"0.3"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/17199135>	"2007"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Prostatic Neoplasms"@en	"0.3"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/17199135>	"2007"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Lymphocyte Count measurement"@en	"0.1"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/27863252>	"2017"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Platelet Count measurement"@en	"0.1"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/27863252>	"2017"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Acute leukemia"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/21109922>	"2011"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Burkitt Lymphoma"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/21109922>	"2011"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Hematologic Neoplasms"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/21109922>	"2011"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Leukemia, Myelocytic, Acute"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/21109922>	"2011"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"leukemia"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/21109922>	"2011"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Acute lymphocytic leukemia"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/20622884>	"2010"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Lymphoid leukemia"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/20622884>	"2010"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Precursor Cell Lymphoblastic Leukemia Lymphoma"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/20622884>	"2010"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Breast Carcinoma"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/19146866>	"2009"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Malignant neoplasm of breast"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/19146866>	"2009"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Choriocarcinoma"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/12566248>	"2003"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Complete hydatidiform mole"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/12566248>	"2003"^^<http://www.w3.org/2001/XMLSchema#gYear>
-"Gestational Trophoblastic Neoplasms"@en	"0.01"^^<http://www.w3.org/2001/XMLSchema#double>	<http://identifiers.org/pubmed/12566248>	"2003"^^<http://www.w3.org/2001/XMLSchema#gYear>
-\end{verbatim}
-\end{scriptsize}
-\caption{Query results obtained by API}
-\label{fig:example-rdf}
+\begin{figure}
+\center
+\includegraphics[width=1.0\textwidth]{spang_disgenet.png}
+\caption{SPANG templates for DisGeNet SPARQL endpoint}
+\label{fig:spang_disgenet}
 \end{figure}
-
-The following command searches for queries with keywords.
-
-\texttt{curl https://spang-portal.dbcls.jp/api/search?keyword=gene}
 
@@
 \caption{Search results obtained by API}
-\label{fig:example-rdf}
+\label{fig:lib-api-out}
 \end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Implementation}
-SPANG is implemented in JavaScript.
+\begin{figure}
+\center
+\includegraphics[width=1.0\textwidth]{spang_disease_gene_query.png}
+\caption{SPANG templates for DisGeNet SPARQL endpoint}
+\label{fig:spang_disease_gene_query}
+\end{figure}
 
-\subsubsection{SPANG template specification}
+\begin{figure}
+\center
+\includegraphics[width=1.0\textwidth]{spang_disease_gene_result.png}
+\caption{SPANG templates for DisGeNet SPARQL endpoint}
+\label{fig:spang_disease_gene_result}
+\end{figure}
+
+\texttt{curl https://spang-portal.dbcls.jp/api/search?keyword=gene}
+
+\section{Implementation details}
+SPANG is implemented in JavaScript using the Node.js technology~\cite{nodejs}. Thus, it can be called in JavaScript applications, and also in the command-line environment.
+
+\subsection{SPANG template specification}
 SPANG template syntax is an extension of sparql-doc.
@@
 
-\subsubsection{SPARQL template engine on the basis of AST}
+\subsection{SPARQL template engine on the basis of AST}
 SPANG template engine is implemented, where each template can be transformed into abstract syntax tree, and then reconstructed into SPARQL. 
-We used PEG expression of SPARQL grammer originally expressed in EBNF in the SPARQL specification.
-The original implementation of PEG.js of SPARQL grammer is provided by rdfstore-js project (https://github.com/antoniogarrote/rdfstore-js).
+We used PEG~\cite{peg} expression of SPARQL grammer originally expressed in EBNF in the SPARQL specification.
+The original implementation of PEG.js~\cite{pegjs} of SPARQL grammer is provided by rdfstore-js project (https://github.com/antoniogarrote/rdfstore-js).
 The PEG.js code was modified to fit the use in the case of SPANG library.
@@
 
-\subsubsection{SPARQL template library}
+\subsection{SPARQL template library}
 We implemented SPARQL queries for 10 endpoints.
-We implemeted the API using Ruby.
 
-\subsubsection{SPANG command line client}
-Originally, SPANG was developed as a command line client using Perl language.
+\subsubsection{SPANG coding rules}
+We defined a coding rule for SPARQL and its extention in SPANG framework.
+Coding rule is important for productivity of shared coding tasks and effective maintenance.
+It also helps to make debug process easier; weird look suggests possible bugs.
+\begin{itemize}
+    \item Header lines: query can start with header lines as comment lines.
+Metadata can be added at the top of the query as comment lines.
+Multiple lines are allowed.
+If multiple lines are described, they are written in sequential without blank lines.
+After the metadata lines, a blank line comes.
+    \item Prefix: prefix declaration comes in sequential lines. Each of before and after the prefix declaration lines, a blank line exists.
+    \item Cases: the SPARQL keywords should be in upper case characters. variabl names comes with ? followed by lower case characters.
+    \item Literal: the literals are surrounded by "".
+    \item Indent: indentation depth is two spaces.
+    \item Spaces: a space exists between keywords and variables. A space exists before , or ; or . .
+    \item Newline: a newline exists before the keyword \texttt{WHERE} and after \texttt{\{}.
+A new line exist after ; or .
+but not after ,.
+After the newline following ;, an indent follows.
+A newline exist before query modifiers such as \texttt{ORDER BY} or \texttt{LIMIT}.
+\end{itemize}
+We developed a reformatter of the SPARQL code as described below.
+
+\subsection{SPANG APIs}
+SPANG library API and query API are developed in Ruby on Rails. The docker version of the SPANG includes the Ruby on Rails implementation of the SPANG APIs.
+
+\subsection{SPANG command line client}
+As an interface the the SPANG library, we constructed a command-line interface.
+
+Originally, SPANG was developed as a command line client using Perl language~\cite{spang}.
 It is re-implemented in JavaScript using Node.js.
@@
 
-\subsubsection{SPANG Web site}
+\subsection{SPANG Web site}
 SPARQL queries can be executed in Web site.
@@
 \section{Availability}
-\subsection{Command-line client}
-We developed a command-line client in JavaScript.
-The usages is as follows.
+
+\subsection{SPANG portal web site}
+SPANG portal web site is developed using Ruby on Rails. And it can be run on Docker. The SPANG query library is published on GitHub. Thus, users can run a portal site by their own.
+
+\subsection{Using in JavaScript applications}
+SPANG is now implemented in JavaScript, so the SPARQL queries can be executed in JavaScript code across the internet.
+To avid CORS retriction, it can access CDN services such as jsDelivr~\cite{jsdelivr} as shown in Figure~\ref{fig:jsdelivr}.
 
@@
 \begin{verbatim}
-Usage: spang2 [options] <SPARQL_TEMPLATE>
-
-Options:
-  -e, --endpoint <ENDPOINT>    target SPARQL endpoint (URL or its predifined name in SPANG_DIR/etc/endpoints,~/.spang/endpoints)
-  -p, --param <PARAMS>         parameters to be embedded (in the form of "--param par1=val1,par2=val2,...")
-  -o, --outfmt <FORMAT>        tsv, json, n-triples (nt), turtle (ttl), rdf/xml (rdfxml), n3, xml, html (default: "tsv")
-  -a, --abbr                   abbreviate results using predefined prefixes
-  -v, --vars                   variable names are included in output (in the case of tsv format)
-  -S, --subject <SUBJECT>      shortcut to specify subject
-  -P, --predicate <PREDICATE>  shortcut to specify predicate
-  -O, --object <OBJECT>        shortcut to specify object
-  -L, --limit <LIMIT>          LIMIT output (use alone or with -[SPOF])
-  -F, --from <FROM>            shortcut to search FROM specific graph (use alone or with -[SPOLN])
-  -N, --number                 shortcut to COUNT results (use alone or with -[SPO])
-  -G, --graph                  shortcut to search for graph names (use alone or with -[SPO])
-  -r, --prefix <PREFIX_FILES>  read prefix declarations (default: SPANG_DIR/etc/prefix,~/.spang/prefix)
-  -n, --ignore                 ignore user-specific file (~/.spang/prefix) for test purpose
-  -m, --method <METHOD>        GET or POST (default: "GET")
-  -q, --show_query             show query and quit
-  -f, --fmt                    format the query
-  -i, --indent <DEPTH>         indent depth; use with --fmt (default: 2)
-  -l, --list_nick_name         list up available nicknames of endpoints and quit
-  -d, --debug                  debug (output query embedded in URL, or output AST with --fmt)
-  -V, --version                output the version number
-  -h, --help                   output usage information
-
+spang.getTemplate('https://raw.githubusercontent.com/hchiba1/spang-library/master/li
+brary/uniprot/count_org.rq', (template) => {
+result = spang.query(template, 'https://sparql.uniprot.org', { abbr: true, format:
+'tsv'}, (error, res, body) => { console.log(body); } );
+})
 \end{verbatim}
 \end{scriptsize}
-\caption{Example of input RDF data}
-\label{fig:example-rdf}
+\caption{Call SARQL in a JavaScript application}
+\label{fig:jsdelivr}
 \end{figure}
 
-\subsection{SPANG portal web site}
-SPANG portal web site is developed using Ruby on Rails. And it can be run on Docker. The SPANG query library is published on GitHub. Thus, users can run a portal site by their own.
+% \subsection{SPANG command: simple querying with shortcuts}
 
-\subsection{Simple querying with SPARQL shortcuts}
+% Specific command-line options, including \texttt{-S~\textit{SUBJECT}}, \texttt{-P~\textit{PREDICATE}}, \texttt{-O~\textit{OBJECT}}, \texttt{-L~\textit{LIMIT}}, and other modifiers, 
+% are interpreted as shortcuts for generating typical SPARQL queries. 
+% A simple example is:
 
-Specific command-line options, including \texttt{-S~\textit{SUBJECT}}, \texttt{-P~\textit{PREDICATE}}, \texttt{-O~\textit{OBJECT}}, \texttt{-L~\textit{LIMIT}}, and other modifiers, 
-are interpreted as shortcuts for generating typical SPARQL queries. 
-A simple example is:
+% \texttt{spang uniprot -S tax:511145 -a}
 
-\texttt{spang uniprot -S tax:511145 -a}
+% \noindent where the first argument is the target SPARQL endpoint and the following arguments are SPARQL shortcuts (the SPARQL endpoint can be specified in a URL or nickname for simplicity). 
+% \texttt{uniprot} is a nickname for the UniProt SPARQL endpoint \citep{UniProt} and \texttt{tax:} is a prefix for URIs of NCBI taxonomy IDs. 
+% This example command line searches the target database for statements that have taxonomy ID 511145 ({\it Escherichia coli} strain K-12 MG1655) as a subject.
+Using the \texttt{-a} option transforms the URIs in the
+%  search result into abbreviated forms using predefined prefix declarations. For example,\\
+% \texttt{\textless http://www.w3.org/2000/01/rdf-schema\#subClassOf\textgreater} 
+% is transformed into \texttt{rdfs:subClassOf
+% }.
+% The result is output to the standard output in the form of tab-separated values by default, as it is suitable for processing by line-oriented Unix programs.
+% In addition, combination of subject, predicate, and object is possible according to the following.
 
-\noindent where the first argument is the target SPARQL endpoint and the following arguments are SPARQL shortcuts (the SPARQL endpoint can be specified in a URL or nickname for simplicity). 
-\texttt{uniprot} is a nickname for the UniProt SPARQL endpoint \citep{UniProt} and \texttt{tax:} is a prefix for URIs of NCBI taxonomy IDs. 
-This example command line searches the target database for statements that have taxonomy ID 511145 ({\it Escherichia coli} strain K-12 MG1655) as a subject.
-Using the \texttt{-a} option transforms the URIs in the
- search result into abbreviated forms using predefined prefix declarations. For example,\\
-\texttt{\textless http://www.w3.org/2000/01/rdf-schema\#subClassOf\textgreater} 
-is transformed into \texttt{rdfs:subClassOf
-}.
-The result is output to the standard output in the form of tab-separated values by default, as it is suitable for processing by line-oriented Unix programs.
-In addition, combination of subject, predicate, and object is possible according to the following.
+% \texttt{spang uniprot -S tax:511145 -P up:otherName}
 
-\texttt{spang uniprot -S tax:511145 -P up:otherName}
+% \noindent where predicate {\tt up:otherName} is specified to further confine the results to other names. 
+% For the full list of available command-line options, simply type the command {\tt spang}.
+% \vspace*{-5pt}
 
-\noindent where predicate {\tt up:otherName} is specified to further confine the results to other names. 
-For the full list of available command-line options, simply type the command {\tt spang}.
-\vspace*{-5pt}
-
-\subsection{Using SPARQL templates with parameters}
+\subsection{SPANG command: calling libraries}
 
@@
 
-\subsection{Combinatorial execution of multiple queries}
+\subsection{SPANG command: combinatorial execution}
 
@@
 Based on the templating mechanisms, SPARQL libraries have been implemented, such as Bioqueries.
-SPARQList is a framework to store SPRARQL templates to be used through API.
+SPARQList is a framework to store SPARQL templates to be used through API.
 
@@
 
+SPARQList~\cite{sparqlist} is a REST API server which executes a SPARQL query, transform the result into formatted data if defined.
+In SPARQList, configuration of the SPARQL queries such as parameters of the API, SPARQL endpoints is written in the Markdown format.
+SPARQList server can be considered as a repository of SPARQL queries.
+In terms of the FAIR principle, findability should be enhanced.
+That is, 1) queries are assigned with globally unique and persistent identifier; 2) queries are described with rich metadata; 3) metadata clearly and explicitly include the identifier of the data they describe; 4) queries are registered or indexed in a searchable resource.
+
+SPARQL inferencing notation (SPIN) specifications~\cite{spin} includes the RDF expression of SPARQL queries.
+This addressed the interoperability and reusability of SPARQL queries, but it did not explicitly addressed the findability and accessibility.
+Metadata for SPARQL queries is important for findability.
+And identifier is important for accessibility.
+
+In this study, we put rich metadata into queries, and registered in a searchable resource.
+
 Client for calling parameterized queries is still limited.
-ASQC~\cite{asqc} command enables the execution of parameterized queries or queries with given variable bindings. However, it is still not possible to execute the quries publised online across the Web.
+ASQC~\cite{asqc} command enables the execution of parameterized queries or queries with given variable bindings.
+However, it is still not possible to execute the queries published online across the Web.
 
-\section{Conclusion}
-SPANG enables easy generation of typical queries, thereby reducing the burden of writing SPARQL.
-SPANG also provides a framework for reusing and sharing arbitrary queries across the Web.
+To the best of our knowledge, this is the first study to consider the FAIRification process comprehensively and show the concrete process of the FAIRification of it.
+
+\section{Conclusion and future work}
+SPANG provides a framework for reusing and sharing arbitrary queries across the Web.
+Sharing not only data but also queries (i.e., means of interpreting data) on the Semantic Web platform will help the biological research community collaborate in knowledge integration and discovery.
+Toward the FAIRification of SPARQL, SPANG provides step toward the FAIRification of Semantic Web, not only in terms of 
+If an RDF database provider,
+who knows best the manner in which the database should be used,
+publishes SPARQL template libraries, database usage can be considerably enhanced.
+
 Moreover, it enables users to execute complex queries by combining existing query templates.
@@
 
-\subsubsection{Limitations and Futur Work}
 SPANG enables easy and effective access to RDF databases, thereby enhancing integrative exploitation of distributed biological databases.
@@
 Specifically, SPANG can call SPARQL templates by their URIs across the Web.
-Thus, if an RDF database provider,
-who knows best the manner in which the database should be used,
-publishes SPARQL template libraries, database usage can be considerably enhanced.
-Sharing not only data but also queries (i.e., means of interpreting data) on the Semantic Web platform will help the biological research community collaborate in knowledge integration and discovery.
 
-\subsubsection{Toward FAIR SPARQL libraries}
-FAIRification of SPARQL is the goal of this project.
+To the best of our knowledge, this is the first study to consider the FAIRification process comprehensively and show the concrete process of the FAIRification of it, and addressed the issues in the process.
+One of the remaining issue is the licensing issue of the SPARQL.
+The licensing issue requires the community consensus, thus it remains to be discussed.
+Nevertheless, we clarified the issues on the process, and contributed the increased reusability of the SPARQL queries to make the Semantic Web more useful community.
+
+The SPANG API returns the result in JSON format.
+The JSON format can be mapped to JSON-LD using JSON-LD mapper, which is compatible with RDF.
+The future work includes the use of the SPANG resources in the form of RDF.
 
 \section*{Acknowledgements}
-We thank Shota Matsumoto for helping implementing the updated version of SPANG.
+We thank Shota Matsumoto for helping in implementation of SPANG.
 
@@
 \bibitem{fair}
-Wilkinson, M.
-D., Dumontier, M., Aalbersberg, I.
-J., Appleton, G., Axton, M., Baak, A., ...
-& Bouwman, J.
+Wilkinson, M. D., Dumontier, M., Aalbersberg, I. J., Appleton, G., Axton, M., Baak, A., et al. (2016). The FAIR Guiding Principles for scientific data management and stewardship. Scientific data, 3.
+
+\bibitem{fairification}
+Jacobsen, A., Kaliyaperumal, R., da Silva Santos, L. O. B., Mons, B., Schultes, E., Roos, M., & Thompson, M. (2020). A generic workflow for the data FAIRification process. Data Intelligence, 56-65.
+
+\bibitem{disgenet}
+Queralt-Rosinach, N., Pinero, J., Bravo, À., Sanz, F., & Furlong, L.
+I.
 (2016).
-The FAIR Guiding Principles for scientific data management and stewardship.
-Scientific data, 3.
+DisGeNET-RDF: harnessing the innovative power of the Semantic Web to explore the genetic basis of diseases.
+Bioinformatics, 32(14), 2236-2238.
 
@@
 \url{https://github.com/ldodds/sparql-doc}
+
+\bibitem{virtuoso}
+Erling, O., & Mikhailov, I. (2009). RDF Support in the Virtuoso DBMS. In Networked Knowledge-Networked Media (pp. 7-24). Springer, Berlin, Heidelberg.
+
+\bibitem{nodejs}
+Node.js is a JavaScript runtime built on Chrome's V8 JavaScript engine. \url{https://nodejs.org/}
+
+\bibitem{jsdelivr}
+jsDelivr - A free, fast, and reliable CDN for open source.
+\url{https://www.jsdelivr.com/}
+
+\bibitem{peg}
+Ford, B.
+(2004, January).
+Parsing expression grammars: a recognition-based syntactic foundation.
+In Proceedings of the 31st ACM SIGPLAN-SIGACT symposium on Principles of programming languages (pp.
+111-122).
+
+\bibitem{pegjs}
+PEG.js – Parser Generator for JavaScript
+\url{https://pegjs.org/}
 
@@
 
+\bibitem{sparqlist}
+Katayama, T., & Kawashima, S. (2017). SPARQList: Markdown-Based Highly Configurable REST API Hosting Server for SPARQL. In SWAT4LS.
+
 % \bibitem{ref_article1}

### 2020-05-23 paper.tex
v1.1

@@
 %
-\title{SPANG library: making SPARQL FAIR in controlled query sets}
+\title{SPANG Library: Making SPARQL Queries FAIR}
 %
@@
 How can we maximize the value of accumulated SPARQL queries? 
+SPARQL is a key component of the Semantic Web, thus the reusability of SPARQL is important.
+An increasing number of datasets have been published in the Resource Description Framework (RDF) and the SPARQL standard allows interoperable framework for querying the RDF datasets; however, reuse of SPARQL queries remains limited due to the lack of findability, accessibility and reusability of SPARQL queries that were once written.
 SPARQL contributes to the standardized interface to the RDF, and maximizing the reusability of RDF; however, reusability of SPARQL itself remains to be addressed. 
-SPARQL is a key component of the Semantic Web, thus the reusability of SPARQL is important.
+In this study, we focus on FAIR (findable, accessible, interoperable,
+reusable) principle to improve usability of SPARQL queries.
+We present the FAIRification process of SPARQL and demonstrate the usefulness of the result.
 FAIRification of the SPARQL is a plausible way to make SPARQL interoperable and reusable.
-An increasing number of datasets have been published in the Resource Description Framework (RDF) and the SPARQL standard allows interoperable framework for querying the RDF datasets; however, reuse of SPARQL queries remains limited due to the lack of findability, accessibility and reusability of SPARQL queries that were once written.
-%Given that SPARQL is an important framework of the Semantic Web, it is important to consolidate the eco-system to reuse SPARQL queries written in various project.
-%Here, we present a extended specification for storing and distributing SPARQL queries named SPANG, and provide a pilot study of SPANG library.
 Here we propose a SPARQL extension to construct a reusable query library to enrich the Semantic Web platform.
-As a use case, we constructed a reusable SPARQL query library, named SPANG library.
 Our contribution is the improvement of findability and accessibility of SPARQL queries.
-% These features facilitate easy access to RDF datasets by users. 
-More specifically,
-1) We present a metadata set for annotating a SPARQL query.
-It enables to identify SPARQL query, and provides useful information fo the query.
-2) We also present a mechanism to parameterize the SPARQL query.
+1) We present a metadata set for annotating a SPARQL query, which
+enables to identify SPARQL query and provides useful information for the query.
+2) We present a mechanism to parameterize the SPARQL query.
 It makes each query reusable in different settings.
-Further, the mechanism enables federated queries by combining multiple queries through Unix pipe. 
-% Here, we developed spang command, as a client that helps users to generate queries.
-SPANG can create typical short queries according to the arguments specified by users like a \textit{one-liner} style in the Unix command line.
-It can also call SPARQL template libraries constructed in a local file system or published on the Web.
-This study make SPARQL queries more findable, accessible, interoperable, and reusable, i.e., pushing forward FAIR SPARQL.
-This specification leads to the construction of eco-system to reuse SPARQL queries to enrich the use of the Semantic Web platform.
-SPANG project resources are available at \url{https://spang.dbcls.jp}.
+This study make SPARQL queries FAIR, and this specification leads to the construction of eco-system to reuse SPARQL queries to enrich the use of the Semantic Web platform.
 
-In this study, we present the FAIRification process of SPARQL and demonstarate the usefulness of the result.
-
-\keywords{SPARQL query \and RDF store \and template library.}
+\keywords{SPARQL \and FAIR \and query library}
 
@@
 \section{Introduction}
-
-SPARQL contributes to the standardized interface to RDF, and miximizing the RDF reusability. Reusability is the key to miximize the value of accumulated open data and software.
 An increasing number of datasets have been published in the Resource Description Framework (RDF).
+SPARQL contributes to the standardized interface to RDF, and maximizing the RDF reusability. 
+Although the SPARQL language provides a basis for exploiting RDF databases, writing a raw SPARQL code often becomes a burden for users. 
 SPARQL is the standardized query langage, and many Semantic Web users write queries in SPARQL, with a great amount of efforts.
 Those queries are valuable resource.
+Reusability is the key to maximize the value of accumulated open data and software.
 However, due to the limitation of SPARQL specifications, the reuse of those queries are limited. 
+Reusing SPARQL queries are important for efficient development of the Semantic Web.
+
 So, how can we maximize the value of accumulated SPARQL queries?
-%Although the SPARQL language provides a basis for exploiting RDF databases, writing a raw SPARQL code often becomes a burden for users. 
-% Several approaches for support of SPARQL writing exist. One is to develop SPARQL editors that have useful functionalities 
-% such as URI autocompletion~\cite{Rietveld}.
-% Another aims at automatic generation of SPARQL queries~\cite{Yamaguchi}.
-% Despite the efforts of previous studies, Semantic Web users remain bound to the task of SPARQL coding.
-%Here, we developed SPANG, a novel SPARQL client
-%that addresses this issue of SPARQL coding by simple query generation and reusing existing query templates.
-%SPANG
-%, with its unique features, 
-%minimizes the burden of coding SPARQL,
-%thereby enhancing integrative analysis of distributed RDF databases.
-
-SPARQL is a fundamental technology for querying RDF data contributing an interoperable interface to the Semantic Web.
-However, is is not designed for reusability.
-In data management guideline, FAIR principle is well known~\cite{fair}.
-Findability, Accesibility, Reusablility should be addressed, to make the most of SPARQL queries as resources.
-
-One of the key principle in the Semantic Web is the FAIR principle: findable, accessible, interoperable and reusable.
-Interestingly, the FAIR principle can be applied not only to the RDF data, but also other resource, like software.
 As the SPARQL queries are important component of the Semantic Web community,
 they should be shared in a solid principle.
-The FAIR principle is suitable for this aim.
-
+One of the key principle in the Semantic Web is the FAIR principle: findable, accessible, interoperable and reusable.
 The Semantic Web is comprised of various specifications, including RDF~\cite{rdf}, OWL~\cite{owl}, and SPARQL~\cite{sparql}.
@@
 Accumulating and reusing the queries are important.
+Interestingly, the FAIR principle can be applied not only to the RDF data, but also other resource, like software.
+SPARQL is a fundamental technology for querying RDF data contributing an interoperable interface to the Semantic Web. However, is is not designed for reusability. 
+In data management guideline, FAIR principle is well known~\cite{fair}. Findability, Accesibility, Reusablility should be addressed, to make the most of SPARQL queries as resources. 
+The FAIR principle is suitable for this aim.
 
-Reusing SPARQL queries are important for efficient development of the Semantic Web.
-
+How can we make SPARQL queries fair?
 Are SPARQL queries accessible?
@@
 But they do not have stable URIs.
-
-How about findability? In many Semantic Web projects, SPARQL queries are written and accumulated. However, those SPARQL queries are not findable, due to the lack of export and import SPARQL queries.
+How about findability?
+In many Semantic Web projects, SPARQL queries are written and accumulated.
+However, those SPARQL queries are not findable, due to the lack of export and import SPARQL queries.
 
 Here, we decided to follow the FAIR principle and extend the SPARQL specifications for more efficient development of the Semantic Web.
-
 Semantic Web users often write SPARQL queris.
@@
 How can we improve the reusability of SPARQL?
-
 One of the key to improve the reusability of queries is parameterization.
@@
 Using the template query with parameters, the same query can be applied to many use cases.
-There can be several types of parameterization.
-The SPARQL variables can be considered as parameter.
-In that case, values to the parameters can replace them.
-On the other hands, part of the URI or literals can be parameterized.
-In that case also, values to the parameters can replace them.
-Another mechanism to use template is to give binding to the variables.
-
-% The SPANG package includes the main {\tt spang} command, which can be used in the Unix command-line environment.
-% In general, the {\tt spang} command help users query RDF databases by dynamically generating SPARQL queries according to the command-line options or arguments. 
-% More specifically, {\tt spang} has two execution modes: 
-% 1) simple mode; for a simple query, users must only specify some command-line options to generate the query without writing any SPARQL code, and
-% 2) template mode; for a more complex query, users can generate the query using a predefined SPARQL template and parameters.
-% Basically, each {\tt spang} process submits a query to a specific database,
-% and the {\tt spang} process can be combined with other Unix processes through a Unix pipe. 
-% Notably, multiple {\tt spang} commands each with distinct target database can be combined through a Unix pipe, thereby realizing federated queries to multiple databases (see Section 2.4).
-
-% To reduce the burden of coding SPARQL, the SPANG package provides predefined configurations about nicknames for SPARQL endpoints, prefix declarations for URIs, and SPARQL libraries (see Section 3).
+% There can be several types of parameterization.
+% The SPARQL variables can be considered as parameter.
+% In that case, values to the parameters can replace them.
+% On the other hands, part of the URI or literals can be parameterized.
+% In that case also, values to the parameters can replace them.
+% Another mechanism to use template is to give binding to the variables.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-\section{FAIR principle}
-
+\section{Making SPARQL queries FAIR}
 The FAIR guiding principle aims to enhance the Findability, Accessibility, Interoperability and Reusability of digital resources.
@@
 Here, we provide the FAIR principle in the context of SPARQL queries.
-
-\subsection{Findability}
-The first step is using data to find SPARQL queries.
-Metadata should be easy to find for both humans and computers.
-Machine-readable metadata are essential for automatic discovery of resources, so this is essential component.
-% \begin{itemize}
-%     \item Assign global identifier
-%     \item Rich metadata
-%     \item Include the identifier of the data they describe
-%     \item Registered and indexed
-% \end{itemize}
-
-\subsection{Accessibility}
-Once the user finds the required data, the user needs to know how can they be accessed, possibly including authentication and authorisation.
-% \begin{itemize}
-%     \item Retrievable by identifier
-%     \item Metadata are accessible
-% \end{itemize}
-
-\subsection{Interoperability}
-The data usually need to be integrated with other data. In addition, the data need to interoperate with application or workflows for analysis, storage, and processing.
-% \begin{itemize}
-%     \item Use a formal, accessible, shared, and broadly applicable language for knowledge representation.
-%     \item Use vocabularies that follow FAIR principles.
-%     \item Include qualified references to others
-% \end{itemize}
-
-\subsection{Reusability}
-The ultimate goal of FAIR is to optimise the reuse of data. To achieve this, metadata should be well-described so that they can be replicated and/or combined in different settings.
-% \begin{itemize}
-%     \item Richly described with a plurality of accurate and relevant attributes
-%     \begin{itemize}
-%         \item released with a clear and accessible data usage license
-%         \item associated with detailed provenance
-%         \item meet domain-relevant community standards
-%     \end{itemize}
-% \end{itemize}
-
-The process of making SPARQL FAIR ("FAIRification") can be described in multiple steps~\cite{fairification}.
-Most of the requirements for findability and accessibility can be achieved at the metadata level. Interoperability and reuse requires more efforts at the SPARQL code level.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\section{FAIRification of SPARQL}
 
@@
 
+The process of making SPARQL FAIR ("FAIRification") can be described in multiple steps~\cite{fairification}.
+Most of the requirements for findability and accessibility can be achieved at the metadata level. Interoperability and reuse requires more efforts at the SPARQL code level.
+
 \subsection{Findability of SPARQL queries}
+The first step is using data to find SPARQL queries.
+Metadata should be easy to find for both humans and computers.
+Machine-readable metadata are essential for automatic discovery of resources, so this is essential component.
+% \begin{itemize}
+%     \item Assign global identifier
+%     \item Rich metadata
+%     \item Include the identifier of the data they describe
+%     \item Registered and indexed
+% \end{itemize}
+
 Most of the SPARQL queries are not findable from general users of the Semantic Web.
@@
 \subsection{Accessibility to SPARQL queries}
+Once the user finds the required data, the user needs to know how can they be accessed, possibly including authentication and authorisation.
+% \begin{itemize}
+%     \item Retrievable by identifier
+%     \item Metadata are accessible
+% \end{itemize}
+
 Some of the SPARQL libraries are accessible from internet.
@@
 \subsection{Interoperability of SPARQL}
+The ultimate goal of FAIR is to optimise the reuse of data. To achieve this, metadata should be well-described so that they can be replicated and/or combined in different settings.
+% \begin{itemize}
+%     \item Richly described with a plurality of accurate and relevant attributes
+%     \begin{itemize}
+%         \item released with a clear and accessible data usage license
+%         \item associated with detailed provenance
+%         \item meet domain-relevant community standards
+%     \end{itemize}
+% \end{itemize}
+
+The data usually need to be integrated with other data. In addition, the data need to interoperate with application or workflows for analysis, storage, and processing.
+% \begin{itemize}
+%     \item Use a formal, accessible, shared, and broadly applicable language for knowledge representation.
+%     \item Use vocabularies that follow FAIR principles.
+%     \item Include qualified references to others
+% \end{itemize}
+
 SPARQL specification is proposed for interoperable use of queries to the Semantic Web.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\section{SPANG specifications}
+\section{SPANG library specifications}
+%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section{Implementation details}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Implementation}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
 SPANG is implemented in JavaScript using the Node.js technology~\cite{nodejs}. Thus, it can be called in JavaScript applications, and also in the command-line environment.
@@
 Here, we consider the parameterization in this frame. We consider the parameters of the query as metadata of SPARQL.
-As a synatax parameterization, we consider mustash notation.
+As a syntax parameterization, we consider mustash notation.
 
-\subsection{SPARQL template engine on the basis of AST}
+\subsection{SPARQL template engine}
 SPANG template engine is implemented, where each template can be transformed into abstract syntax tree, and then reconstructed into SPARQL. 
-We used PEG~\cite{peg} expression of SPARQL grammer originally expressed in EBNF in the SPARQL specification.
-The original implementation of PEG.js~\cite{pegjs} of SPARQL grammer is provided by rdfstore-js project (https://github.com/antoniogarrote/rdfstore-js).
+We used PEG~\cite{peg} expression of SPARQL grammar originally expressed in EBNF in the SPARQL specification.
+The original implementation of PEG.js~\cite{pegjs} of SPARQL grammar is provided by rdfstore-js project (https://github.com/antoniogarrote/rdfstore-js).
 The PEG.js code was modified to fit the use in the case of SPANG library.
-The PEG.js is a parser generator, thus, we could generate our own parser based on the PEG.js description. Thus, we obtained abstract syntax tree in the form of JSON objecct.
+The PEG.js is a parser generator, thus, we could generate our own parser based on the PEG.js description. Thus, we obtained abstract syntax tree in the form of JSON object.
 
@@
 \subsubsection{SPANG coding rules}
-We defined a coding rule for SPARQL and its extention in SPANG framework.
+We defined a coding rule for SPARQL and its extension in SPANG framework.
 Coding rule is important for productivity of shared coding tasks and effective maintenance.
@@
     \item Prefix: prefix declaration comes in sequential lines. Each of before and after the prefix declaration lines, a blank line exists.
-    \item Cases: the SPARQL keywords should be in upper case characters. variabl names comes with ? followed by lower case characters.
+    \item Cases: the SPARQL keywords should be in upper case characters. variable names comes with ? followed by lower case characters.
     \item Literal: the literals are surrounded by "".

### 2020-05-23 paper.tex
v1.2

@@
 How can we maximize the value of accumulated SPARQL queries? 
-SPARQL is a key component of the Semantic Web, thus the reusability of SPARQL is important.
-An increasing number of datasets have been published in the Resource Description Framework (RDF) and the SPARQL standard allows interoperable framework for querying the RDF datasets; however, reuse of SPARQL queries remains limited due to the lack of findability, accessibility and reusability of SPARQL queries that were once written.
-SPARQL contributes to the standardized interface to the RDF, and maximizing the reusability of RDF; however, reusability of SPARQL itself remains to be addressed. 
+%SPARQL is a key component of the Semantic Web, thus the reusability of SPARQL is important.
+An increasing number of datasets have been published in the Resource Description Framework (RDF) and the SPARQL standard allows interoperable framework for querying the RDF datasets; however, reuse of SPARQL queries remains limited partly due to the lack of accessibility and findability of SPARQL queries that were once written.
+%SPARQL contributes to the standardized interface to the RDF, and maximizing the reusability of RDF; however, reusability of SPARQL itself remains to be addressed. 
 In this study, we focus on FAIR (findable, accessible, interoperable,
 reusable) principle to improve usability of SPARQL queries.
-We present the FAIRification process of SPARQL and demonstrate the usefulness of the result.
+We present the process of making SPARQL queries FAIR and demonstrate the usefulness of the result.
 FAIRification of the SPARQL is a plausible way to make SPARQL interoperable and reusable.
-Here we propose a SPARQL extension to construct a reusable query library to enrich the Semantic Web platform.
+Here, we define a SPANG library as a controleld query set with specific
+extension of SPARQL so that the query set follows FAIR pinciple.
+%Here we propose a SPARQL extension to construct a reusable query library to enrich the Semantic Web platform.
 Our contribution is the improvement of findability and accessibility of SPARQL queries.
@@
 \section{Introduction}
+How can we maximize the value of accumulated SPARQL queries?
+Reuse of them of could be the key.
 An increasing number of datasets have been published in the Resource Description Framework (RDF).
-SPARQL contributes to the standardized interface to RDF, and maximizing the RDF reusability. 
+SPARQL is the standardized interface to RDF and contributing the reusability of the RDF data. 
 Although the SPARQL language provides a basis for exploiting RDF databases, writing a raw SPARQL code often becomes a burden for users. 
-SPARQL is the standardized query langage, and many Semantic Web users write queries in SPARQL, with a great amount of efforts.
+SPARQL is the standardized query language, and many Semantic Web users write queries in SPARQL, with a great amount of efforts.
 Those queries are valuable resource.
@@
 
-So, how can we maximize the value of accumulated SPARQL queries?
+The FAIR principle~\cite{fair} could be suitable for addressing this issue.
+One of the key principle in recent days of the Semantic Web community is the FAIR principle: findable, accessible, interoperable and reusable.
 As the SPARQL queries are important component of the Semantic Web community,
 they should be shared in a solid principle.
-One of the key principle in the Semantic Web is the FAIR principle: findable, accessible, interoperable and reusable.
 The Semantic Web is comprised of various specifications, including RDF~\cite{rdf}, OWL~\cite{owl}, and SPARQL~\cite{sparql}.
@@
 In data management guideline, FAIR principle is well known~\cite{fair}. Findability, Accesibility, Reusablility should be addressed, to make the most of SPARQL queries as resources.
-The FAIR principle is suitable for this aim.
 
-How can we make SPARQL queries fair?
+%How can we make SPARQL queries fair? 
 Are SPARQL queries accessible?
@@
 \section{Making SPARQL queries FAIR}
+%%%%%%%%%%%%%%%%%%%%%%%%
+
 The FAIR guiding principle aims to enhance the Findability, Accessibility, Interoperability and Reusability of digital resources.
@@
 
-\subsection{Interoperability of SPARQL}
+\subsection{Interoperability of SPARQL queries}
 The ultimate goal of FAIR is to optimise the reuse of data. To achieve this, metadata should be well-described so that they can be replicated and/or combined in different settings.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\section{SPANG library specifications}
+\section{SPANG Library}
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Implementation}
+\section{Specifications and Implementation Details}
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{SPARQL template library}
-We implemented SPARQL queries for 10 endpoints.
+%We implemented SPARQL queries for 10 endpoints.
 

### 2020-05-23 paper.tex
v1.3

@@
 \begin{document}
-%
-\title{SPANG Library: Making SPARQL Queries FAIR}
-%
-\titlerunning{SPANG library: making SPARQL FAIR}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-%\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
-%Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
-%Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
+
+\title{SPANG Template Library: Making SPARQL Queries FAIR}
+\titlerunning{SPANG: Making SPARQL Queries FAIR}
 \author{Hirokazu Chiba}
-%
 \authorrunning{H. Chiba}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-%\institute{Princeton University, Princeton NJ 08544, USA \and
-%Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
-%\email{lncs@springer.com}\\
-%\url{http://www.springer.com/gp/computer-science/lncs} \and
-%ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-%\email{\{abc,lncs\}@uni-heidelberg.de}}
 \institute{Database Center for Life Science, Chiba 277-0871, Japan\\
@@
 \end{abstract}
-%
-%
-%
+
+%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%
+
 How can we maximize the value of accumulated SPARQL queries?
-Reuse of them of could be the key.
+Reuse of them is the key.
 An increasing number of datasets have been published in the Resource Description Framework (RDF).
@@
 
-% The following section includes: overview of the SPANG project, specification of SPANG templates, implementation of the SPANG library, and use case of SPANSG library.
+%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Overview}
+%%%%%%%%%%%%%%%%%%%%%%%%
 
-% \begin{figure}
-% \center
-% \includegraphics[width=1.0\textwidth]{spang_top.png}
-% \caption{SPANG web site}
-% \label{fig:spang_top}
-% \end{figure}
+We overview the FAIR principles, then describe how to apply the principle to SPARQL.
+We demonstarate how to use the SPANG templete library.
+Then, we describe the details of SPANG template specifications.
+
+%The following section includes: overview of the SPANG project, specification of SPANG templates, implementation of the SPANG library, and use case of SPANSG library.
+
+Figure~\ref{fig:spang_top} is the top page of SPANG, which includes links to GitHub, Documentation, and SPANG library.
+
+\begin{figure}
+\center
+\includegraphics[width=1.0\textwidth]{spang_top.png}
+\caption{SPANG web site}
+\label{fig:spang_top}
+\end{figure}
 
@@
 
-% Figure~\ref{fig:spang_top} is the top page of SPANG, which includes links to GitHub, Documentation, and SPANG library.
-
 Figure~\ref{fig:spang_lib} is the list of the target SPARQL endpoints. It also lists the SPARQL templates available in general for various endpoints.
@@
 
-\subsection{SPANG template specification}
+\subsection{Template specifications}
 SPANG template syntax is an extension of sparql-doc.
@@
 
-\subsection{SPARQL template engine}
+\subsection{Template engine}
 SPANG template engine is implemented, where each template can be transformed into abstract syntax tree, and then reconstructed into SPARQL. 
@@
 
-\subsection{SPARQL template library}
-%We implemented SPARQL queries for 10 endpoints.
-
-\subsubsection{SPANG coding rules}
+\subsection{Coding rules}
 We defined a coding rule for SPARQL and its extension in SPANG framework.
@@
 
-\subsection{SPANG APIs}
-SPANG library API and query API are developed in Ruby on Rails. The docker version of the SPANG includes the Ruby on Rails implementation of the SPANG APIs.
-
-\subsection{SPANG command line client}
-As an interface the the SPANG library, we constructed a command-line interface.
-
-Originally, SPANG was developed as a command line client using Perl language~\cite{spang}.
-It is re-implemented in JavaScript using Node.js.
-SPARQL templates can be executed in command line.
-
-\subsection{SPANG Web site}
-SPARQL queries can be executed in Web site.
-
-%%%%%%%%%%%%%%%%%%%%
-
-% \subsection{Simple querying with SPARQL shortcuts}
-
-% Specific command-line options, including \texttt{-S~\textit{SUBJECT}}, \texttt{-P~\textit{PREDICATE}},\\ \texttt{-O~\textit{OBJECT}}, \texttt{-L~\textit{LIMIT}}, and other modifiers, 
-% are interpreted as shortcuts for generating typical SPARQL queries. 
-% A simple example is:
-
-% \texttt{spang uniprot -S tax:511145 -a}
-
-% \noindent where the first argument is the target SPARQL endpoint and the following arguments are SPARQL shortcuts (the SPARQL endpoint can be specified in a URL or nickname for simplicity). 
-% \texttt{uniprot} is a nickname for the UniProt SPARQL endpoint \cite{UniProt} and \texttt{tax:} is a prefix for URIs of NCBI taxonomy IDs. 
-% This example command line searches the target database for statements that have taxonomy ID 511145 ({\it Escherichia coli} strain K-12 MG1655) as a subject.
-Using the \texttt{-a} option transforms the URIs in the search result into abbreviated forms using predefined prefix declarations.
-For example,\\
-% \texttt{\textless http://www.w3.org/2000/01/rdf-schema\#subClassOf\textgreater}\\
-% is transformed into \texttt{rdfs:subClassOf}.
-% The result is output to the standard output in the form of tab-separated values by default, as it is suitable for processing by line-oriented Unix programs.
-% In addition, combination of subject, predicate, and object is possible according to the following.
-
-% \texttt{spang uniprot -S tax:511145 -P up:otherName}
-
-% \noindent where predicate {\tt up:otherName} is specified to further confine the results to other names. 
-% For the full list of available command-line options, simply type the command {\tt spang}.
-
-% \subsection{Combinatorial execution of multiple queries}
-
-% SPANG combines multiple queries through a Unix pipe. 
-% Combining a {\tt spang} command in shortcut mode and another one in template mode is also possible.
-% An example of such a combinatorial query is shown in Fig.~\ref{fig:01}.
-% The first {\tt spang} command is in template mode, which is the same as that presented in the Section 2.3. 
-% This command searches the MBGD database for orthologs of a protein {\tt K9Z723}. 
-% The obtained list of proteins are used in the second query, which searches the UniProt database for annotations of the given list of proteins. 
-% The option \texttt{-S 1} specifies the values from the first column of the standard input as subject.
-% This combinatorial query enables integrative use of two databases distributed across the Web. 
-% Here, the output of the first command can be further modified by altering the second command.
-% For example:
-% \begin{quoting}
-% \texttt{spang mbgd mbgdl:get\_ortholog K9Z723 | spang uniprot uniprot\_xref PDB}
-% \vspace{1pt}
-% \end{quoting}
-% where {\tt uniprot\_xref} is a SPARQL template (see supplementary data for the code), which retrieves cross-references from the UniProt IDs given in the standard input to the database specified as the parameter (in this example, {\tt PDB}).
-This example command line searches for entries in the Protein Data Bank (PDB) \citep{Berman} among orthologs of {\tt K9Z723}.
-
 %%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{SPANG portal web site}
-SPANG portal web site is developed using Ruby on Rails. And it can be run on Docker. The SPANG query library is published on GitHub. Thus, users can run a portal site by their own.
+\subsection{SPANG server}
+SPARQL queries can be executed in Web site.
+SPANG server is developed using Ruby on Rails. And it can be run on Docker. The SPANG query library is published on GitHub. Thus, users can run a portal site by their own.
+
+\subsection{SPANG APIs}
+SPANG library API and query API are developed in Ruby on Rails. The docker version of the SPANG includes the Ruby on Rails implementation of the SPANG APIs.
 
@@
 
-% \subsection{SPANG command: simple querying with shortcuts}
+\subsection{SPANG command line client}
+As an interface the the SPANG library, we constructed a command-line interface.
 
-% Specific command-line options, including \texttt{-S~\textit{SUBJECT}}, \texttt{-P~\textit{PREDICATE}}, \texttt{-O~\textit{OBJECT}}, \texttt{-L~\textit{LIMIT}}, and other modifiers, 
-% are interpreted as shortcuts for generating typical SPARQL queries. 
-% A simple example is:
-
-% \texttt{spang uniprot -S tax:511145 -a}
-
-% \noindent where the first argument is the target SPARQL endpoint and the following arguments are SPARQL shortcuts (the SPARQL endpoint can be specified in a URL or nickname for simplicity). 
-% \texttt{uniprot} is a nickname for the UniProt SPARQL endpoint \citep{UniProt} and \texttt{tax:} is a prefix for URIs of NCBI taxonomy IDs. 
-% This example command line searches the target database for statements that have taxonomy ID 511145 ({\it Escherichia coli} strain K-12 MG1655) as a subject.
-Using the \texttt{-a} option transforms the URIs in the
-%  search result into abbreviated forms using predefined prefix declarations. For example,\\
-% \texttt{\textless http://www.w3.org/2000/01/rdf-schema\#subClassOf\textgreater} 
-% is transformed into \texttt{rdfs:subClassOf
-% }.
-% The result is output to the standard output in the form of tab-separated values by default, as it is suitable for processing by line-oriented Unix programs.
-% In addition, combination of subject, predicate, and object is possible according to the following.
-
-% \texttt{spang uniprot -S tax:511145 -P up:otherName}
-
-% \noindent where predicate {\tt up:otherName} is specified to further confine the results to other names. 
-% For the full list of available command-line options, simply type the command {\tt spang}.
-% \vspace*{-5pt}
+Originally, SPANG was developed as a command line client using Perl language~\cite{spang}.
+It is re-implemented in JavaScript using Node.js.
+SPARQL templates can be executed in command line.
 
@@
 
-% \subsection{A Subsection Sample}
-% Please note that the first paragraph of a section or subsection is
-% not indented. The first paragraph that follows a table, figure,
-% equation etc. does not need an indent, either.
-
-% Subsequent paragraphs, however, are indented.
-
-% \subsubsection{Sample Heading (Third Level)} Only two levels of
-% headings should be numbered. Lower level headings remain unnumbered;
-% they are formatted as run-in headings.
-
-% \paragraph{Sample Heading (Fourth Level)}
-% The contribution should contain no more than four levels of
-% headings. Table~\ref{tab1} gives a summary of all heading levels.
-
-% \begin{table}
-% \caption{Table captions should be placed above the
-% tables.}\label{tab1}
-% \begin{tabular}{|l|l|l|}
-% \hline
-% Heading level &  Example & Font size and style\\
-% \hline
-% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-% \hline
-% \end{tabular}
-% \end{table}
-
-% \noindent Displayed equations are centered and set on a separate
-% line.
-% \begin{equation}
-% x + y = z
-% \end{equation}
-% Please try to avoid rasterized images for line-art diagrams and
-% schemas. Whenever possible, use vector graphics instead (see
-% Fig.~\ref{fig1}).
-
-% \begin{figure}
-% \includegraphics[width=\textwidth]{fig1.eps}
-% \caption{A figure caption is always placed below the illustration.
-% Please note that short captions are centered, while long ones are
-% justified by the macro package automatically.} \label{fig1}
-% \end{figure}
-
-% \begin{theorem}
-% This is a sample theorem. The run-in heading is set in bold, while
-% the following text appears in italics. Definitions, lemmas,
-% propositions, and corollaries are styled the same way.
-% \end{theorem}
-%
-% the environments 'definition', 'lemma', 'proposition', 'corollary',
-% 'remark', and 'example' are defined in the LLNCS documentclass as well.
-%
-% \begin{proof}
-% Proofs, examples, and remarks have the initial word in italics,
-% while the following text appears in normal font.
-% \end{proof}
-% For citations of references, we prefer the use of square brackets
-% and consecutive numbers. Citations using labels or the author/year
-% convention are also acceptable. The following bibliography provides
-% a sample reference list with entries for journal
-% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-% and a homepage~\cite{ref_url1}. Multiple citations are grouped
-% \cite{ref_article1,ref_lncs1,ref_book1},
-% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-% \bibliographystyle{splncs04}
-% \bibliography{mybibliography}
-%
 \begin{thebibliography}{8}
-
-% \bibitem{Rietveld}
-% Rietveld,L. and Hoekstra,R.: YASGUI: not just another SPARQL client,
-% In: The Semantic Web: ESWC 2013 Satellite Events, 78-86. Springer (2013)
-
-% \bibitem{Yamaguchi}
-% Yamaguchi,A. \textit{et~al}.:
-% An intelligent SPARQL query builder for exploration of various life-science databases.
-% In: The 3rd International Workshop on Intelligent Exploration of Semantic Data (IESD 2014) (2014)
 
@@
 
-% \bibitem{ref_article1}
-% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
-
-% \bibitem{ref_lncs1}
-% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-% Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-
-% \bibitem{ref_book1}
-% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-% Location (1999)
-
-% \bibitem{ref_proc1}
-% Author, A.-B.: Contribution title. In: 9th International Proceedings
-% on Proceedings, pp. 1--2. Publisher, Location (2010)
-
-% \bibitem{ref_url1}
-% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-% Oct 2017
 \end{thebibliography}

### 2020-05-23 paper.tex
v1.4

@@
 
-Contributions of this work:
-we provide a SPARQL meta data required for constucting SPARQL queries.
-we constructed template engines for SPARQL queries.
-we constructed controlled SPARQL queries for available SPARQL endpoints.
+Contributions of this work is 
+1) we provide a SPARQL meta data required for constucting SPARQL queries;
+2) we constructed template engines for SPARQL queries; and
+3) we constructed controlled SPARQL queries for available SPARQL endpoints.
 
@@
 \includegraphics[width=1.0\textwidth]{spang_top.png}
-\caption{SPANG web site}
+\caption{SPANG server top page}
 \label{fig:spang_top}
@@
 
-\subsection{Findability of SPARQL queries}
+\subsection{Findability}
 The first step is using data to find SPARQL queries.
@@
 
-\subsection{Accessibility to SPARQL queries}
+\subsection{Accessibility}
 Once the user finds the required data, the user needs to know how can they be accessed, possibly including authentication and authorisation.
@@
 
-\subsection{Interoperability of SPARQL queries}
+\subsection{Interoperability}
 The ultimate goal of FAIR is to optimise the reuse of data. To achieve this, metadata should be well-described so that they can be replicated and/or combined in different settings.
@@
 
-\subsection{Reusability of SPARQL queries}
+\subsection{Reusability}
 Reusability of SPARQL is not a new topic.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\section{SPANG Library}
+\section{SPANG Library and Use Cases}
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Specifications and Implementation Details}
+\section{Specifications}
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{Using in JavaScript applications}
+\subsection{JavaScript}
 SPANG is now implemented in JavaScript, so the SPARQL queries can be executed in JavaScript code across the internet.
@@
 
-\subsection{SPANG command line client}
+\subsection{Command-line client}
 As an interface the the SPANG library, we constructed a command-line interface.
@@
 
-\subsection{SPANG command: calling libraries}
+\subsubsection{Calling libraries}
 
@@
 
-\subsection{SPANG command: combinatorial execution}
+\subsubsection{Combinatorial execution}
 

### 2020-05-23 paper.tex
v1.5

@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-\section{Making SPARQL queries FAIR}
+\section{Making SPARQL Queries FAIR}
 %%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Availability}
+%%%%%%%%%%%%%%%%%%%%%%
 
-\subsection{SPANG server}
-SPARQL queries can be executed in Web site.
-SPANG server is developed using Ruby on Rails. And it can be run on Docker. The SPANG query library is published on GitHub. Thus, users can run a portal site by their own.
-
-\subsection{SPANG APIs}
-SPANG library API and query API are developed in Ruby on Rails. The docker version of the SPANG includes the Ruby on Rails implementation of the SPANG APIs.
-
-\subsection{JavaScript}
+\subsection{JavaScript Application}
 SPANG is now implemented in JavaScript, so the SPARQL queries can be executed in JavaScript code across the internet.
@@
 
-\subsection{Command-line client}
+\subsection{Command-line Client}
 As an interface the the SPANG library, we constructed a command-line interface.
+Originally, SPANG was developed as a command line client using Perl language~\cite{spang}.
+It is re-implemented in JavaScript using Node.js as SPANG2.
+SPARQL templates can be executed in command line.
+The following example command line gives a parameter to the query template, and execute to the DisGeNet endpoint
 
-Originally, SPANG was developed as a command line client using Perl language~\cite{spang}.
-It is re-implemented in JavaScript using Node.js.
-SPARQL templates can be executed in command line.
+\texttt{spang2 gene\_disease.rq --param disease=C0751955}
 
-\subsubsection{Calling libraries}
+The template can be URL that returns a SPARQL query. The full usages of the command is as shown in Figure~\ref{fig:spang-command}.
 
-Although SPARQL shortcuts are useful for simple querying with typical query patterns, they do not cover various
-queries with complicated patterns. 
-Thus, SPANG provides a mechanism to accept SPARQL templates to generate arbitrary query patterns. 
-An example query is:
+\begin{figure}[!t]
+\begin{scriptsize}
+\begin{verbatim}
+Usage: spang2 [options] <SPARQL_TEMPLATE>
 
-\texttt{spang uniprot taxtree\_ancestor 511145 -ac}
+Options:
+  -e, --endpoint <ENDPOINT>    target SPARQL endpoint
+  -p, --param <PARAMS>         parameters to be embedded (in the form of "--param par1=val1,par2=val2,...")
+  -o, --outfmt <FORMAT>        tsv, json, n-triples (nt), turtle (ttl), rdf/xml (rdfxml), n3, xml, html
+  -a, --abbr                   abbreviate results using predefined prefixes
+  -v, --vars                   variable names are included in output (in the case of tsv format)
+  -S, --subject <SUBJECT>      shortcut to specify subject
+  -P, --predicate <PREDICATE>  shortcut to specify predicate
+  -O, --object <OBJECT>        shortcut to specify object
+  -L, --limit <LIMIT>          LIMIT output (use alone or with -[SPOF])
+  -F, --from <FROM>            shortcut to search FROM specific graph (use alone or with -[SPOLN])
+  -N, --number                 shortcut to COUNT results (use alone or with -[SPO])
+  -G, --graph                  shortcut to search for graph names (use alone or with -[SPO])
+  -r, --prefix <PREFIX_FILES>  read prefix declarations (default: SPANG_DIR/etc/prefix,~/.spang/prefix)
+  -n, --ignore                 ignore user-specific file (~/.spang/prefix) for test purpose
+  -m, --method <METHOD>        GET or POST (default: "GET")
+  -q, --show_query             show query and quit
+  -f, --fmt                    format the query
+  -i, --indent <DEPTH>         indent depth; use with --fmt (default: 2)
+  -l, --list_nick_name         list up available nicknames of endpoints and quit
+  -d, --debug                  debug (output query embedded in URL, or output AST with --fmt)
+  -V, --version                output the version number
+  -h, --help                   output usage information
 
-\noindent where the first argument is the target SPARQL endpoint and the following arguments are SPARQL templates and parameters.
+\end{verbatim}
+\end{scriptsize}
+\caption{SPANG command usage}
+\label{fig:spang-command}
+\end{figure}
+
+\subsection{SPANG Server}
+SPARQL queries can be executed in Web site.
+SPANG server is developed using Ruby on Rails.
+And it can be run on Docker.
+The SPANG query library is published on GitHub.
+Thus, users can run a portal site by their own.
+The SPANG APIs are available on the SPANG server.
+
+% \subsubsection{Calling libraries}
+
+% Although SPARQL shortcuts are useful for simple querying with typical query patterns, they do not cover various
+% queries with complicated patterns. 
+% Thus, SPANG provides a mechanism to accept SPARQL templates to generate arbitrary query patterns. 
+% An example query is:
+
+% \texttt{spang uniprot taxtree\_ancestor 511145 -ac}
+
+% \noindent where the first argument is the target SPARQL endpoint and the following arguments are SPARQL templates and parameters.
 {\tt taxtree\_ancestor} is the name of a SPARQL template included in the predefined SPARQL library (see supplementary data for the code), {\tt 511145} is the parameter, {\tt -a} is the option for abbreviating results, and {\tt -c} is for aligning output columns for easier reading.
-The specified parameter replaces the placeholder included in the template before execution. 
-This example query traverses the NCBI taxonomy tree from the given ID (511145) to the root node and outputs scientific names in each taxonomic rank.
+% The specified parameter replaces the placeholder included in the template before execution. 
+% This example query traverses the NCBI taxonomy tree from the given ID (511145) to the root node and outputs scientific names in each taxonomic rank.
 
-Available SPARQL templates are not limited to the local library.
-If SPARQL libraries are published on the Web, the users can call the templates by means of URIs across the Web.
-An example usage of the Microbial Genome Database (MBGD) SPARQL library published at http://mbgd.genome.ad.jp/sparql/library/ is as follows.
+% Available SPARQL templates are not limited to the local library.
+% If SPARQL libraries are published on the Web, the users can call the templates by means of URIs across the Web.
+% An example usage of the Microbial Genome Database (MBGD) SPARQL library published at http://mbgd.genome.ad.jp/sparql/library/ is as follows.
 
-\texttt{spang mbgd mbgdl:get\_ortholog K9Z723}
+% \texttt{spang mbgd mbgdl:get\_ortholog K9Z723}
 
-where {\tt mbgd} is the MBGD SPARQL endpoint \citep{Chiba} and \texttt{mbgdl:} is a prefix for abbreviating the URI of the template {\tt get\_ortholog} in the MBGD SPARQL library (see supplementary data for the code).
-The template can be specified in the full URI or in abbreviated form using the predefined prefix declarations.
-This example query searches the MBGD database \citep{Uchiyama} for the orthologs of a protein \texttt{K9Z723} (Photosystem II lipoprotein Psb27).
+% where {\tt mbgd} is the MBGD SPARQL endpoint \citep{Chiba} and \texttt{mbgdl:} is a prefix for abbreviating the URI of the template {\tt get\_ortholog} in the MBGD SPARQL library (see supplementary data for the code).
+% The template can be specified in the full URI or in abbreviated form using the predefined prefix declarations.
+% This example query searches the MBGD database \citep{Uchiyama} for the orthologs of a protein \texttt{K9Z723} (Photosystem II lipoprotein Psb27).
 
-The following example command line gives a parameter to the query template, and execute to the DisGeNet endpoint.
-\texttt{spang gene\_disease.rq --param disease=C0751955}
+% \subsubsection{Combinatorial execution}
 
-\subsubsection{Combinatorial execution}
-
-SPANG combines multiple queries through a Unix pipe. 
-Combining a {\tt spang} command in shortcut mode and another one in template mode is also possible.
-An example of such a combinatorial query is shown in Fig.~\ref{fig:01}.
-The first {\tt spang} command is in template mode, which is the same as that presented in the Section 2.3. 
-This command searches the MBGD database for orthologs of a protein {\tt K9Z723}. 
-The obtained list of proteins are used in the second query, which searches the UniProt database for annotations of the given list of proteins. 
-The option \texttt{-S 1} specifies the values from the first column of the standard input as subject.
-This combinatorial query enables integrative use of two databases distributed across the Web. 
-Here, the output of the first command can be further modified by altering the second command.
-For example:
-\begin{quoting}
-\texttt{spang mbgd mbgdl:get\_ortholog K9Z723 | spang uniprot uniprot\_xref PDB}
-\vspace{1pt}
-\end{quoting}
-where {\tt uniprot\_xref} is a SPARQL template (see supplementary data for the code), which retrieves cross-references from the UniProt IDs given in the standard input to the database specified as the parameter (in this example, {\tt PDB}).
+% SPANG combines multiple queries through a Unix pipe. 
+% Combining a {\tt spang} command in shortcut mode and another one in template mode is also possible.
+% An example of such a combinatorial query is shown in Fig.~\ref{fig:01}.
+% The first {\tt spang} command is in template mode, which is the same as that presented in the Section 2.3. 
+% This command searches the MBGD database for orthologs of a protein {\tt K9Z723}. 
+% The obtained list of proteins are used in the second query, which searches the UniProt database for annotations of the given list of proteins. 
+% The option \texttt{-S 1} specifies the values from the first column of the standard input as subject.
+% This combinatorial query enables integrative use of two databases distributed across the Web. 
+% Here, the output of the first command can be further modified by altering the second command.
+% For example:
+% \begin{quoting}
+% \texttt{spang mbgd mbgdl:get\_ortholog K9Z723 | spang uniprot uniprot\_xref PDB}
+% \vspace{1pt}
+% \end{quoting}
+% where {\tt uniprot\_xref} is a SPARQL template (see supplementary data for the code), which retrieves cross-references from the UniProt IDs given in the standard input to the database specified as the parameter (in this example, {\tt PDB}).
 This example command line searches for entries in the Protein Data Bank (PDB) \citep{Berman} among orthologs of {\tt K9Z723}.
 
+%%%%%%%%%%%%%%%%%%%%%%
 \section{Related Work}
+%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section{Conclusion and future work}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion and Future Work}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 SPANG provides a framework for reusing and sharing arbitrary queries across the Web.

### 2020-05-23 paper.tex
v1.6

@@
 
-\subsection{SPARQL metadata}
+\subsection{SPARQL Metadata}
 
@@
 
-\subsection{SPARQL parameterization}
+\subsection{SPARQL Parameterization}
 
@@
 
-\subsection{SPANG library API}
+\subsection{SPANG Library API}
 According to the metadata and parameterization mechanism, we can construct a controlled set of SPARQL library which is reusable in various settings.
@@
 
-\subsection{SPANG query API}
+\subsection{SPANG Query API}
 
@@
 
-\subsection{SPANG portal}
+\subsection{SPANG Server}
 SPANG is originally developed for "SARQLing" the RDF dataset from command line. Here, we re-implemented the SPANG using Node.js and now the functionality is available through Web browser.
@@
 
-\subsection{Template specifications}
+\subsection{Template Specifications}
 SPANG template syntax is an extension of sparql-doc.
@@
 
-\subsection{Template engine}
+\subsection{Template Engine}
 SPANG template engine is implemented, where each template can be transformed into abstract syntax tree, and then reconstructed into SPARQL. 
@@
 
-\subsection{Coding rules}
+\subsection{Coding Rules}
 We defined a coding rule for SPARQL and its extension in SPANG framework.
@@
 SPANG is now implemented in JavaScript, so the SPARQL queries can be executed in JavaScript code across the internet.
-To avid CORS retriction, it can access CDN services such as jsDelivr~\cite{jsdelivr} as shown in Figure~\ref{fig:jsdelivr}.
+To avid CORS retriction, it can access through content delivery network services, such as jsDelivr~\cite{jsdelivr}, as shown in Figure~\ref{fig:jsdelivr}.
 
@@
 \begin{verbatim}
-spang.getTemplate('https://raw.githubusercontent.com/hchiba1/spang-library/master/li
-brary/uniprot/count_org.rq', (template) => {
-result = spang.query(template, 'https://sparql.uniprot.org', { abbr: true, format:
-'tsv'}, (error, res, body) => { console.log(body); } );
-})
+spang.getTemplate('https://cdn.jsdelivr.net/gh/hchiba1/spang-library@latest/library/uniprot/count_org.rq', 
+(template) => {
+  result = spang.query(template, 'https://sparql.uniprot.org', { abbr: true, format:'tsv'}, 
+  (error, res, body) => { console.log(body); });
+});
 \end{verbatim}
 \end{scriptsize}
-\caption{Call SARQL in a JavaScript application}
+\caption{Use of SPARQL library in a JavaScript application}
 \label{fig:jsdelivr}
@@
 As an interface the the SPANG library, we constructed a command-line interface.
-Originally, SPANG was developed as a command line client using Perl language~\cite{spang}.
-It is re-implemented in JavaScript using Node.js as SPANG2.
+Originally, SPANG was developed as a command line client in Perl~\cite{spang}.
+It is re-implemented in JavaScript using Node.js as \texttt{SPANG2}.
 SPARQL templates can be executed in command line.
@@
 
-\texttt{spang2 gene\_disease.rq --param disease=C0751955}
+\texttt{spang2 disease\_gene.rq --param disease=C0751955}
 
-The template can be URL that returns a SPARQL query. The full usages of the command is as shown in Figure~\ref{fig:spang-command}.
+The template can be URL that returns a SPARQL query, such as \url{https://cdn.jsdelivr.net/gh/hchiba1/spang-library@latest/library/disgenet/disease_gene.rq}.
+The full usages of the command is as shown in Figure~\ref{fig:spang-command}.
 
@@
 \end{scriptsize}
-\caption{SPANG command usage}
+\caption{Usage of the \texttt{SPANG2} command}
 \label{fig:spang-command}

### 2020-05-23 paper.tex
v1.7

@@
 %SPARQL is a key component of the Semantic Web, thus the reusability of SPARQL is important.
-An increasing number of datasets have been published in the Resource Description Framework (RDF) and the SPARQL standard allows interoperable framework for querying the RDF datasets; however, reuse of SPARQL queries remains limited partly due to the lack of accessibility and findability of SPARQL queries that were once written.
+An increasing number of datasets have been published in the Resource Description Framework (RDF) and the SPARQL standard allows interoperable framework for querying the RDF datasets; however, reuse of SPARQL queries remains limited due to the lack of accessibility and findability of SPARQL queries written in various projects.
 %SPARQL contributes to the standardized interface to the RDF, and maximizing the reusability of RDF; however, reusability of SPARQL itself remains to be addressed. 
 In this study, we focus on FAIR (findable, accessible, interoperable,
-reusable) principle to improve usability of SPARQL queries.
-We present the process of making SPARQL queries FAIR and demonstrate the usefulness of the result.
-FAIRification of the SPARQL is a plausible way to make SPARQL interoperable and reusable.
+reusable) principle to improve reusability of SPARQL queries.
+We present the process of making SPARQL queries FAIR and demonstrate the usefulness of the resulting query library.
+%FAIRification of the SPARQL is a plausible way to make SPARQL interoperable and reusable.
 Here, we define a SPANG library as a controleld query set with specific
@@
 %Here we propose a SPARQL extension to construct a reusable query library to enrich the Semantic Web platform.
-Our contribution is the improvement of findability and accessibility of SPARQL queries.
-1) We present a metadata set for annotating a SPARQL query, which
-enables to identify SPARQL query and provides useful information for the query.
-2) We present a mechanism to parameterize the SPARQL query.
-It makes each query reusable in different settings.
-This study make SPARQL queries FAIR, and this specification leads to the construction of eco-system to reuse SPARQL queries to enrich the use of the Semantic Web platform.
+Our contribution is showing steps for making SPARQL queries FAIR;
+1) assigning a metadata set for annotating a SPARQL query, which
+enables to identify SPARQL query and provides useful information for the query;
+2) parameterize SPARQL queries, which makes each query reusable in different settings;
+3) assigning globally unique and stable identifier for each query;
+4) construct a server to provide the index of SPARQL queries.
+This study make SPARQL queries FAIR, and leads to the construction of eco-system where SPARQL queries are reused to maximize the potential of the Semantic Web.
 
@@
 
-How can we maximize the value of accumulated SPARQL queries?
-Reuse of them is the key.
-An increasing number of datasets have been published in the Resource Description Framework (RDF).
-SPARQL is the standardized interface to RDF and contributing the reusability of the RDF data. 
-Although the SPARQL language provides a basis for exploiting RDF databases, writing a raw SPARQL code often becomes a burden for users. 
-SPARQL is the standardized query language, and many Semantic Web users write queries in SPARQL, with a great amount of efforts.
-Those queries are valuable resource.
-Reusability is the key to maximize the value of accumulated open data and software.
-However, due to the limitation of SPARQL specifications, the reuse of those queries are limited. 
-Reusing SPARQL queries are important for efficient development of the Semantic Web.
+How can we maximize the value of accumulated SPARQL~\cite{sparql} queries?
+An increasing number of datasets have been published in the Resource Description Framework (RDF)~\cite{rdf}.
+SPARQL is the standardized interface to RDF and contributing effective reuse of distributed RDF data. 
+Although eco-systems for developing SPARQL have been developed, writing SPARQL codes often becomes a burden for the Semantic Web users. 
+SPARQL queries have been written in many Semantic Web projects, which requires efforts of developers. 
+For effective enrichment of the Semantic Web, reuse of such queries are valuable.
+% Reusability is the key to maximize the value of accumulated open data and software.
+However, due to the limitation of SPARQL specifications, such as the lack of parameterization mechanism, the reuse of those queries are limited. 
+% Reusing SPARQL queries are important for efficient development of the Semantic Web.
+Thus, reuse of the queries is the key of this problem.
 
-The FAIR principle~\cite{fair} could be suitable for addressing this issue.
-One of the key principle in recent days of the Semantic Web community is the FAIR principle: findable, accessible, interoperable and reusable.
-As the SPARQL queries are important component of the Semantic Web community,
-they should be shared in a solid principle.
+%The FAIR principle~\cite{fair} could be suitable for addressing this issue.
+One of the key principle in recent days of the Semantic Web community is the FAIR (findable, accessible, interoperable and reusable) principle~\cite{fair}.
 The Semantic Web is comprised of various specifications, including RDF~\cite{rdf}, OWL~\cite{owl}, and SPARQL~\cite{sparql}.
@@
 Not only the ontologies and datasets, but also the queries are important for the Semantic Web.
+% As the SPARQL queries are important component of the Semantic Web community,
+% they should be shared in a solid principle.
 Accumulating and reusing the queries are important.
 Interestingly, the FAIR principle can be applied not only to the RDF data, but also other resource, like software.
-SPARQL is a fundamental technology for querying RDF data contributing an interoperable interface to the Semantic Web. However, is is not designed for reusability. 
-In data management guideline, FAIR principle is well known~\cite{fair}. Findability, Accesibility, Reusablility should be addressed, to make the most of SPARQL queries as resources.
+% SPARQL is a fundamental technology for querying RDF data contributing an interoperable interface to the Semantic Web. However, is is not designed for reusability. 
+% In data management guideline, FAIR principle is well known~\cite{fair}. Findability, Accesibility, Reusablility should be addressed, to make the most of SPARQL queries as resources. 
+Applying FAIR principle to SPARQL query should increase the reusability of the queries.
 
 %How can we make SPARQL queries fair?
-Are SPARQL queries accessible?
-In most cases, those queries are not accessible.
-According to the FAIR principle, resources should be accessible by through URI.
-In some cases, SPARQL queries are stored in repositories.
-But they do not have stable URIs.
-How about findability?
-In many Semantic Web projects, SPARQL queries are written and accumulated.
-However, those SPARQL queries are not findable, due to the lack of export and import SPARQL queries.
 
-Here, we decided to follow the FAIR principle and extend the SPARQL specifications for more efficient development of the Semantic Web.
-Semantic Web users often write SPARQL queris.
-However, the SPARQL lacks the parameterization mechanism, thus, users write queries for their specific use cases.
-But good SPARQL queries can be reused.
-Actually, writing good query requires much efforts, thus, they should be reused to improve the productivity.
-Thus, considering the reusability of SPARQL queries are crucial to enrich the Semantic Web community.
+Here, we apply the FAIR principle and extend the SPARQL specifications for more efficient development of the Semantic Web.
+%Semantic Web users often write SPARQL queris.
+%However, the SPARQL lacks the parameterization mechanism, thus, users write queries for their specific use cases.
+%But good SPARQL queries can be reused.
+%Actually, writing good query requires much efforts, thus, they should be reused to improve the productivity.
+%Thus, considering the reusability of SPARQL queries are crucial to enrich the Semantic Web community.
 How can we improve the reusability of SPARQL?
@@
 % Another mechanism to use template is to give binding to the variables.
+Are SPARQL queries accessible?
+In most cases, those queries are not accessible.
+According to the FAIR principle, resources should be accessible by through URI.
+In some cases, SPARQL queries are stored in repositories.
+But they do not have stable URIs.
+How about findability?
+In many Semantic Web projects, 
+%SPARQL queries are written and accumulated. However, those SPARQL queries 
+%are not findable, due to the lack of export and import SPARQL queries.
+SPARQL queries are not exposed to the web in a reusable form, nor indexed by metadata in a findable form.
 
-Contributions of this work is 
-1) we provide a SPARQL meta data required for constucting SPARQL queries;
-2) we constructed template engines for SPARQL queries; and
-3) we constructed controlled SPARQL queries for available SPARQL endpoints.
+In this study, we show the step to make SPARQL queries FAIR to maximize the value of written SPARQL queries.
+Contributions of this work is demonstrating how to
+1) assign meta data to SPARQL queries;
+2) parameterize the SPARQL queries;
+3) assign global identifiers;
+4) construct a server for providing queries.
 
@@
 
-We overview the FAIR principles, then describe how to apply the principle to SPARQL.
-We demonstarate how to use the SPANG templete library.
+Figure~\ref{fig:spang_top} is the top page of SPANG server, which provides access to a SPANG library, links to GitHub repositories of the SPANG project, and documentations.
+
+First, we review FAIR principles and describe how to apply the principle to SPARQL.
+Further, we demonstrate how to use the SPANG templete library.
 Then, we describe the details of SPANG template specifications.
@@
 %The following section includes: overview of the SPANG project, specification of SPANG templates, implementation of the SPANG library, and use case of SPANSG library.
-
-Figure~\ref{fig:spang_top} is the top page of SPANG, which includes links to GitHub, Documentation, and SPANG library.
 
@@
 
+Here we review the preliminaries for the FAIR principle
+and provide the FAIR principle in the context of SPARQL queries.
 The FAIR guiding principle aims to enhance the Findability, Accessibility, Interoperability and Reusability of digital resources.
-
+It shoulbe noted that the FIAR principle can be applied not only to the dataset resources but also to other type of resources including software tools.
 Not only the RDF dataset, but also the SPARQL queries are important resource to be shared on the Semantic Web platform.
@@
 
-Here we overview the preliminaries for the FAIR principle.
-It shoulbe noted that the FIAR principle can be applied not only to the dataset resources but also to other type of resources including software tools.
+%The core technology constituting the Semantic Web is RDF, OWL, and SPARQL. 
+%RDF and OWL follows the FAIR principle. However, SPARQL is not FAIR.
 
-Here, we provide the FAIR principle in the context of SPARQL queries.
+%So, what is the problem of the FAIRification status of SPARQL?
+%SPARQL is important component of the Semantic Web. The use of SPARQL query is essential for the Semantic Web community.
 
-In the previous section, we showed the core idea of the FAIR principle.
+%The key is the metadata.
 
-So, what is the relationship between FAIR principle and the Semantic Web?
-The core technology constituting the Semantic Web is RDF, OWL, and SPARQL. RDF and OWL follows the FAIR principle. However, SPARQL is not FAIR.
-
-So, what is the problem of the FAIRification status of SPARQL?
-SPARQL is important component of the Semantic Web. The use of SPARQL query is essential for the Semantic Web community.
-
-The key is the metadata.
-
-Here, we constructed SPANG library: a SPARQL library which is findable, accessible, interoperable and reusable.
-
-The process of making SPARQL FAIR ("FAIRification") can be described in multiple steps~\cite{fairification}.
-Most of the requirements for findability and accessibility can be achieved at the metadata level. Interoperability and reuse requires more efforts at the SPARQL code level.
+%Here, we constructed SPANG library: a SPARQL library which is findable, accessible, interoperable and reusable.
 
 \subsection{Findability}
-The first step is using data to find SPARQL queries.
-Metadata should be easy to find for both humans and computers.
-Machine-readable metadata are essential for automatic discovery of resources, so this is essential component.
+
+In the FAIR principle, making resources findable includes indexing resources by adding metadata to each resources. 
+Most of the SPARQL queries are not findable from general users of the Semantic Web. 
+The first and most important step toward increased value of the written SPARQL queries is to consider how to make SPARQL queries findable.
+The first step is using metadata to find SPARQL queries. 
+Metadata should be easy to find for both humans and computers. Machine-readable metadata are essential for automatic discovery of resources, so this is essential component.
 % \begin{itemize}
@@
 % \end{itemize}
-
-Most of the SPARQL queries are not findable from general users of the Semantic Web.
-The first and most important step toward increased value of the written SPARQL queries is to consider how to make SPARQL queries findable.
-In the FAIR principle, making resources findable includes indexing resources by adding metadata to each resources. 
 To make SPARQL queries findable, we propose to add metadata to SPARQL.
 The SPARQL metadata includes: title, description, target endpoint, and parameters with its name, default value, and classes.
-
 Indexing of SPARQL queries are conducted and thus users can obtain specific queries of interest through a search API.
@@
 % \end{itemize}
-
-Some of the SPARQL libraries are accessible from internet.
-Howver, we could consider more general scheme for accesibility.
-In the FAIR principle, accessibility includes minting URI for each resource.
+%Some of the SPARQL libraries are accessible from internet. 
+%However, we could consider more general scheme for accessibility. 
+%In the FAIR principle, accessibility includes minting URI for each resource.
 Here we propose to use stable URI for each SPARQL query.
-In the case of SPANG library, we assign two URI for each query.
+In the case of SPANG library, we assign two URIs for each query. 
 One is for retrieving SPARQL query string, thereby users can retrieve the concrete content of the query. 
-Another is URI to get results.
-This URI can include the parameter settings for the specified query.
+Another is URI to get results. This URI can include the parameter settings for the specified query.
 
 \subsection{Interoperability}
-The ultimate goal of FAIR is to optimise the reuse of data. To achieve this, metadata should be well-described so that they can be replicated and/or combined in different settings.
+%The ultimate goal of FAIR is to optimise the reuse of data. 
+%To achieve this, metadata should be well-described so that they can be replicated and/or combined in different settings.
+
 % \begin{itemize}
@@
 
-The data usually need to be integrated with other data. In addition, the data need to interoperate with application or workflows for analysis, storage, and processing.
+The data usually need to be integrated with other data. 
+In addition, the data need to interoperate with application or workflows for analysis, storage, and processing.
 % \begin{itemize}
@@
 It is valuable to use several triplestore implementation through the same programming interface. 
-However, no rule is proposed for coding rules; capitalization, indentation and newline, etc.
+However, standard SPARQL specifications do not include coding rules; capitalization, indentation and newline, etc. 
 Lack of those rules result in variation of SPARQL queries, which hampers the reuse of SPARQL queries. 
-In other languages, some coding ruels exist.
-In the case of SPARQL, specification document or text books do not follow a specific coding rules.
-Here, we specify the coding rule used in SPANG template library, and implemented spfmt command to reformat of the code.
+In other languages, coding rules exist in most cases. 
+In the case of SPARQL, even specification document or text books do not follow a specific coding rules. 
+In this study, we specify the coding rule used in SPANG template library, and implemented a formatter command to evaluate and reformat the input SPARQL code.
 
 \subsection{Reusability}
-Reusability of SPARQL is not a new topic.
-Various activity is conducted to construct libraries of SPARQL.
-It is considered as acitivities to increase the reusability of SPARQL queries.
-However, no standard to increase the reusability is proposed.
-In the specifiation of SPARQL, reusability is not a centroal topic.
-However, it is an central resource in a Semantic Web.
-If it is a component of Semantic Web comprised of RDF/OWL/SPARQL, it is reasonable to represent it in RDF framework.
-We propose a way to represent SPARQL in the RDF framework.
-
-Templating is also a key issue for reusability.
+%Reusability of SPARQL is not a new topic. 
+In the specification of SPARQL, reusability is not a central topic. 
+However, it is an central resource in a Semantic Web, it is valuable to share and reuse SPARQL queires.
+Templating is a key for reusability. 
 SPARQL specifications do not includes templating mechanism, but without templating, each SPARQL queries are not applicable to other use cases. 
 We implemented templating mechanism using a general freamework, mustash.
+Various activity is conducted to construct libraries of SPARQL. 
+It is considered as activities to increase the reusability of SPARQL queries. However, no standard to increase the reusability is proposed. 
+%If it is a component of Semantic Web comprised of RDF/OWL/SPARQL, it is reasonable to represent it in RDF framework. 
+%We propose a way to represent SPARQL in the RDF framework.
+
+\subsection{FAIRification of SPARQL}
+The process of making SPARQL FAIR ("FAIRification") can be described in multiple steps~\cite{fairification}.
+Most of the requirements for findability and accessibility can be achieved at the metadata level. 
+Interoperability and reusability requires more efforts at the SPARQL code level.
 
@@
 \caption{Example query in SPANG library}
-\label{fig:example-rdf}
+\label{fig:example-sparql}
 \end{figure}
@@
 
-An example query in the SPANG library is shown below.
+An example query in the SPANG library is shown in Figure~\ref{fig:example-sparql}.
 The DisGeNet endpoint~\cite{disgenet} is specified.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Specifications}
+\section{SPANG Template Specifications}
 %%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-05-23 paper.tex
v1.8

@@
 
-\title{SPANG Template Library: Making SPARQL Queries FAIR}
-\titlerunning{SPANG: Making SPARQL Queries FAIR}
+\title{SPANG: Template Library for Making SPARQL Queries FAIR}
+\titlerunning{SPANG: Template Library for Making SPARQL Queries FAIR}
 \author{Hirokazu Chiba}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-\section{Overview}
+\section{SPANG Overview}
 %%%%%%%%%%%%%%%%%%%%%%%%
 
-Figure~\ref{fig:spang_top} is the top page of SPANG server, which provides access to a SPANG library, links to GitHub repositories of the SPANG project, and documentations.
-
-First, we review FAIR principles and describe how to apply the principle to SPARQL.
+In this study, we review FAIR principles and describe how to apply the principle to SPARQL.
 Further, we demonstrate how to use the SPANG templete library.
 Then, we describe the details of SPANG template specifications.
+
+Figure~\ref{fig:spang_top} is the top page of SPANG server, which provides access to a SPANG library, links to GitHub repositories of the SPANG project, and documentations.
 

### 2020-05-24 paper.tex
v1.9

@@
 %SPARQL is a key component of the Semantic Web, thus the reusability of SPARQL is important.
-An increasing number of datasets have been published in the Resource Description Framework (RDF) and the SPARQL standard allows interoperable framework for querying the RDF datasets; however, reuse of SPARQL queries remains limited due to the lack of accessibility and findability of SPARQL queries written in various projects.
+Whereas an increasing number of datasets have been published in the Resource Description Framework (RDF) and the SPARQL standard allows interoperable framework for querying the RDF datasets, reuse of SPARQL queries remains limited due to the lack of accessibility and findability of SPARQL queries written in various projects.
 %SPARQL contributes to the standardized interface to the RDF, and maximizing the reusability of RDF; however, reusability of SPARQL itself remains to be addressed. 
-In this study, we focus on FAIR (findable, accessible, interoperable,
+Here, we focus on FAIR (findable, accessible, interoperable,
 reusable) principle to improve reusability of SPARQL queries.
@@
 %FAIRification of the SPARQL is a plausible way to make SPARQL interoperable and reusable.
-Here, we define a SPANG library as a controleld query set with specific
-extension of SPARQL so that the query set follows FAIR pinciple.
+We define a SPANG library as a controlled query set with specific
+extension of SPARQL so that the query set follows FAIR principle.
 %Here we propose a SPARQL extension to construct a reusable query library to enrich the Semantic Web platform.
-Our contribution is showing steps for making SPARQL queries FAIR;
-1) assigning a metadata set for annotating a SPARQL query, which
+We show steps for making SPARQL queries FAIR;
+1) assigning a set of metadata for annotating a SPARQL query, which
 enables to identify SPARQL query and provides useful information for the query;
-2) parameterize SPARQL queries, which makes each query reusable in different settings;
+2) parameterizing SPARQL queries, which makes each query reusable in different settings;
 3) assigning globally unique and stable identifier for each query;
-4) construct a server to provide the index of SPARQL queries.
-This study make SPARQL queries FAIR, and leads to the construction of eco-system where SPARQL queries are reused to maximize the potential of the Semantic Web.
+4) constructing a server to provide indices of SPARQL queries.
+This study make SPARQL queries FAIR, and leads to the construction of eco-system of the Semantic Web where SPARQL queries are reused to maximize the productivity of the Semantic Web developers and users.
 
@@
 
-How can we maximize the value of accumulated SPARQL~\cite{sparql} queries?
 An increasing number of datasets have been published in the Resource Description Framework (RDF)~\cite{rdf}.
 SPARQL is the standardized interface to RDF and contributing effective reuse of distributed RDF data. 
+How can we maximize the value of accumulated SPARQL~\cite{sparql} queries?
+Reuse of the queries is the key of this problem.
 Although eco-systems for developing SPARQL have been developed, writing SPARQL codes often becomes a burden for the Semantic Web users. 
@@
 % Reusing SPARQL queries are important for efficient development of the Semantic Web.
-Thus, reuse of the queries is the key of this problem.
 
@@
 Accumulating and reusing the queries are important.
-Interestingly, the FAIR principle can be applied not only to the RDF data, but also other resource, like software.
+Notably, the FAIR principle can be applied not only to the RDF data, but also other resource, like software.
 % SPARQL is a fundamental technology for querying RDF data contributing an interoperable interface to the Semantic Web. However, is is not designed for reusability. 
@@
 %Thus, considering the reusability of SPARQL queries are crucial to enrich the Semantic Web community.
-How can we improve the reusability of SPARQL?
+%How can we improve the reusability of SPARQL?
+Following the FAIR principle, we could identify the process to make SPARQL query reusable.
 One of the key to improve the reusability of queries is parameterization.
@@
 % Another mechanism to use template is to give binding to the variables.
-Are SPARQL queries accessible?
-In most cases, those queries are not accessible.
+%Are SPARQL queries accessible? 
+Accessibility to SPARQL queries should also be reconsidered.
+afIn most cases, those queries are not accessible.
 According to the FAIR principle, resources should be accessible by through URI.
@@
 In this study, we review FAIR principles and describe how to apply the principle to SPARQL.
-Further, we demonstrate how to use the SPANG templete library.
+Further, we demonstrate how to use the SPANG template library.
 Then, we describe the details of SPANG template specifications.
@@
 Figure~\ref{fig:spang_top} is the top page of SPANG server, which provides access to a SPANG library, links to GitHub repositories of the SPANG project, and documentations.
+The SPANG project consists of SPANG server, SPANG library, SPANG API, and SPANG command.
+The central topic of this paper is how to construct the SPANG library in an interoperable and reusable way.
+It also provides the foundation of findability and accessibility through SPANG API and command.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-
 Here we review the preliminaries for the FAIR principle
@@
 The FAIR guiding principle aims to enhance the Findability, Accessibility, Interoperability and Reusability of digital resources.
-It shoulbe noted that the FIAR principle can be applied not only to the dataset resources but also to other type of resources including software tools.
+It shoul be noted that the FAIR principle can be applied not only to the dataset resources but also to other type of resources including software tools.
 Not only the RDF dataset, but also the SPARQL queries are important resource to be shared on the Semantic Web platform.
-Thus, we applied the FAIR principle which have been applied to the RDF datasets, into SPARQL queries.
+Thus, we tried to apply the FAIR principle which have been applied to the RDF datasets, into SPARQL queries.
 
@@
 \subsection{Findability}
-
+The ultimate goal of FAIR is to optimise the reuse of resources. 
+To achieve this, metadata should be well-described so that they can be replicated and/or combined in different settings.
 In the FAIR principle, making resources findable includes indexing resources by adding metadata to each resources. 
@@
 Indexing of SPARQL queries are conducted and thus users can obtain specific queries of interest through a search API.
+We review each item in the following subsections.
+In the following subsections, the target of FAIR principle is extended from data to resource.
+We consider a SPARQL query as a resource.
 
 \subsection{Accessibility}
-Once the user finds the required data, the user needs to know how can they be accessed, possibly including authentication and authorisation.
+To be accessible, resource should be retrievable by identifier, and metadata should be also available even if the resource are no longer available.
+%Once the user finds the required data, the user needs to know how can they be accessed, possibly including authentication and authorisation.
 % \begin{itemize}
@@
 \subsection{Interoperability}
-%The ultimate goal of FAIR is to optimise the reuse of data. 
-%To achieve this, metadata should be well-described so that they can be replicated and/or combined in different settings.
-
-% \begin{itemize}
-%     \item Richly described with a plurality of accurate and relevant attributes
-%     \begin{itemize}
-%         \item released with a clear and accessible data usage license
-%         \item associated with detailed provenance
-%         \item meet domain-relevant community standards
-%     \end{itemize}
-% \end{itemize}
-
-The data usually need to be integrated with other data. 
-In addition, the data need to interoperate with application or workflows for analysis, storage, and processing.
+For interoperability, a formal, accessible, shared, and broadly applicable language is necessary.
+The resource usually need to be integrated with other resources. 
+In addition, the resource need to interoperate with application or workflows for analysis, storage, and processing.
 % \begin{itemize}
@@
 \subsection{Reusability}
+
+% \begin{itemize}
+%     \item Richly described with a plurality of accurate and relevant attributes
+%     \begin{itemize}
+%         \item released with a clear and accessible data usage license
+%         \item associated with detailed provenance
+%         \item meet domain-relevant community standards
+%     \end{itemize}
+% \end{itemize}
+
 %Reusability of SPARQL is not a new topic. 
@@
 SPARQL specifications do not includes templating mechanism, but without templating, each SPARQL queries are not applicable to other use cases. 
-We implemented templating mechanism using a general freamework, mustash.
+We implemented templating mechanism using a general freamework, mustache.
 Various activity is conducted to construct libraries of SPARQL. 
@@
 Here, we consider the parameterization in this frame. We consider the parameters of the query as metadata of SPARQL.
-As a syntax parameterization, we consider mustash notation.
+As a syntax parameterization, we consider mustache~\cite{mustache} notation.
 
@@
 
+\bibitem{mustache}
+Logic-less templates.
+https://mustache.github.io/
+
 \bibitem{peg}

### 2020-05-24 paper.tex
v2.0

@@
 Reuse of the queries is the key of this problem.
-Although eco-systems for developing SPARQL have been developed, writing SPARQL codes often becomes a burden for the Semantic Web users. 
-SPARQL queries have been written in many Semantic Web projects, which requires efforts of developers. 
-For effective enrichment of the Semantic Web, reuse of such queries are valuable.
+Although eco-systems for developing SPARQL have been developed, writing SPARQL codes often becomes a burden for the Semantic Web developers and users. 
+SPARQL queries have been written in many Semantic Web projects, which requires efforts. 
+For effective construction of the Semantic Web applications, reuse of such queries are valuable.
 % Reusability is the key to maximize the value of accumulated open data and software.
@@
 One of the key principle in recent days of the Semantic Web community is the FAIR (findable, accessible, interoperable and reusable) principle~\cite{fair}.
+The ultimate goal of FAIR is to optimise the reuse of resources. 
 The Semantic Web is comprised of various specifications, including RDF~\cite{rdf}, OWL~\cite{owl}, and SPARQL~\cite{sparql}.
@@
 Accessibility to SPARQL queries should also be reconsidered.
-afIn most cases, those queries are not accessible.
+In most cases, those queries are not accessible.
 According to the FAIR principle, resources should be accessible by through URI.
@@
 
-In this study, we show the step to make SPARQL queries FAIR to maximize the value of written SPARQL queries.
-Contributions of this work is demonstrating how to
+In this study, we show the steps to make SPARQL queries FAIR to maximize the value of written SPARQL queries:
 1) assign meta data to SPARQL queries;
@@
 4) construct a server for providing queries.
+And we demonstrate the steps to construct the SPANG template library, which is reusable on the Semantic Web platform.
 
 %%%%%%%%%%%%%%%%%%%%%%%%
-\section{SPANG Overview}
+\section{SPANG Project Overview}
 %%%%%%%%%%%%%%%%%%%%%%%%
-
-In this study, we review FAIR principles and describe how to apply the principle to SPARQL.
-Further, we demonstrate how to use the SPANG template library.
-Then, we describe the details of SPANG template specifications.
 
@@
 It also provides the foundation of findability and accessibility through SPANG API and command.
+
+In the following sections, we review FAIR principles and describe how to apply the principle to SPARQL.
+Further, we demonstrate how to use the SPANG template library.
+Then, we describe the details of SPANG template specifications.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-Here we review the preliminaries for the FAIR principle
-and provide the FAIR principle in the context of SPARQL queries.
+
 The FAIR guiding principle aims to enhance the Findability, Accessibility, Interoperability and Reusability of digital resources.
@@
 Thus, we tried to apply the FAIR principle which have been applied to the RDF datasets, into SPARQL queries.
+In the following subsections, we review the preliminaries for the FAIR principle
+and provide the FAIR principle in the context of SPARQL queries.
+We review each item in the following subsections.
+In the following subsections, the target of FAIR principle is extended from data to resource.
+We consider a SPARQL query as a resource.
 
@@
 The SPARQL metadata includes: title, description, target endpoint, and parameters with its name, default value, and classes.
-Indexing of SPARQL queries are conducted and thus users can obtain specific queries of interest through a search API.
-We review each item in the following subsections.
-In the following subsections, the target of FAIR principle is extended from data to resource.
-We consider a SPARQL query as a resource.
+Indexing of SPARQL queries are conducted and thus users can obtain specific queries of interest through application programming interfaces (APIs).
 
 \subsection{Accessibility}
-To be accessible, resource should be retrievable by identifier, and metadata should be also available even if the resource are no longer available.
+To be accessible, resource should be retrievable by identifier.
 %Once the user finds the required data, the user needs to know how can they be accessed, possibly including authentication and authorisation.
@@
 Another is URI to get results. This URI can include the parameter settings for the specified query.
+Also, according to the FAIR principle, metadata of each resource should be also available even if the resource are no longer available. 
+We assume that API can provide the metadata for each SPARQL query even if the query is no longer available.
 
@@
 However, standard SPARQL specifications do not include coding rules; capitalization, indentation and newline, etc. 
-Lack of those rules result in variation of SPARQL queries, which hampers the reuse of SPARQL queries. 
+Lack of those rules result in variation of SPARQL queries, which hampers the efficiency in collaborative development of SPARQL queries. 
 In other languages, coding rules exist in most cases. 
 In the case of SPARQL, even specification document or text books do not follow a specific coding rules. 
-In this study, we specify the coding rule used in SPANG template library, and implemented a formatter command to evaluate and reformat the input SPARQL code.
+Thus, we specify the coding rule used in SPANG template library, and implemented a formatter command to evaluate and reformat the input SPARQL code.
 
@@
 %Reusability of SPARQL is not a new topic. 
-In the specification of SPARQL, reusability is not a central topic. 
-However, it is an central resource in a Semantic Web, it is valuable to share and reuse SPARQL queires.
+The ultimate goal of FAIR is to optimise the reuse of resources. 
+However, in the specification of SPARQL, reusability is not a central topic. 
+Since it is an central resource in a Semantic Web, it is valuable to share and reuse SPARQL queries.
 Templating is a key for reusability. 
@@
 \subsection{FAIRification of SPARQL}
-The process of making SPARQL FAIR ("FAIRification") can be described in multiple steps~\cite{fairification}.
+The process of making resource FAIR ("FAIRification") can be described in multiple steps~\cite{fairification}.
 Most of the requirements for findability and accessibility can be achieved at the metadata level. 
-Interoperability and reusability requires more efforts at the SPARQL code level.
+Interoperability and reusability requires more efforts at the resource level.
+The same strategy can be applied to the SPARQL queries.
+The following section describes how we constructed the SPANG library which follows the FAIR principle.
 
@@
 \end{scriptsize}
-\caption{Example query in SPANG library}
+\caption{Example query in the SPANG library}
 \label{fig:example-sparql}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-
-The core of the SPANG specification is the SPARQL metadata and templating mechanism for increasing the reusability of the SPARQL queries.
-
-An example query in the SPANG library is shown in Figure~\ref{fig:example-sparql}.
-The DisGeNet endpoint~\cite{disgenet} is specified.
+In the previous section we review the FAIR principle in the context of SPARQL queries.
+In this section, we describe how we constructed the SPANG library with some use cases.
+The use case shown in this section includes the query to the DisGeNet endpoint~\cite{disgenet}, which is shown in Figure~\ref{fig:example-sparql}.
+This query retrieve protein IDs involved in a specific disease.
+The core of the SPANG library specification is the SPARQL metadata and templating mechanism for increasing the reusability of the SPARQL queries.
+The query example includes metadata at the beginning of the query as comment lines.
+The query also includes a parameter for a disease identifier.
+According to the metadata and parameterization mechanism, we can construct a controlled set of SPARQL library which is reusable in various settings.
 
@@
 
-As a use case, we developed a SPANG API to search for the set of SPARQL queries.
-
-\subsection{SPARQL Parameterization}
-
-We propose the parapeterization mechanism of SPARQL query. It is crucial to reuse the SPARQL query for us to improve the productivity of the programming experiance on the Semantic Web platform.
-
-Using SPANG API, users can execute SPARQL query over the Web, with the given parameters.
-
-\subsection{SPANG Library API}
-According to the metadata and parameterization mechanism, we can construct a controlled set of SPARQL library which is reusable in various settings.
-
-SPANG library is accesible through SPANG Web API.
-
+We developed a SPANG library API to search for the set of SPARQL queries.
+SPANG library is accessible through SPANG Web API.
 The following command returns the list of libraries.
@@
 The results is shown in Figure~\ref{fig:libs-api-out} as JSON format.
-
 The following command returns the list of query in a library.
@@
 The results is shown in Figure~\ref{fig:lib-api-out} as JSON format.
+The following command searches for queries with keywords.
 
-\subsection{SPANG Query API}
+\texttt{curl https://spang-portal.dbcls.jp/api/search?keyword=gene}
 
-The following command returns the result of the query, with the given paramter.
+\subsection{SPARQL Parameterization}
+
+We propose the parameterization mechanism of SPARQL query. It is crucial to reuse the SPARQL query for us to improve the productivity of the programming experience on the Semantic Web platform.
+
+Using SPANG API, users can execute SPARQL query over the Web, with the given parameters.
+The following command returns the result of the query, with the given parameter.
 
@@
 
-Figure~\ref{fig:spang_disease_gene_query} shows a query for DiesGeNet SPARQL endpoint to get disase gene relationship. 
+Figure~\ref{fig:spang_disease_gene_query} shows a query for DisGeNET SPARQL endpoint to get disease gene relationship. 
 Figure~\ref{fig:spang_disease_gene_result} shows the result of the query. Thus, users can get the results only by clicking on the web pages, browsing the SPARQL template on the SPANG web site.
 
-The following command searches for queries with keywords.
-
 \subsection{SPANG Server}
-SPANG is originally developed for "SARQLing" the RDF dataset from command line. Here, we re-implemented the SPANG using Node.js and now the functionality is available through Web browser.
+SPANG is originally developed as a SPARQL client to query the RDF dataset from command line.
+Here, we re-implemented the SPANG using Node.js and now the functionality is available through Web browsers.
 
@@
 
-Figure~\ref{fig:spang_lib} is the list of SPARQL templates for DisGeNet SPARQL endpoint.
-A short name for the SPARQL template, descriptin of the query, and example parameters are shown.
+Figure~\ref{fig:spang_lib} is the list of SPARQL templates for DisGeNET SPARQL endpoint.
+A short name for the SPARQL template, description of the query, and example parameters are shown.
 
@@
 \end{figure}
-
-\texttt{curl https://spang-portal.dbcls.jp/api/search?keyword=gene}
 

### 2020-05-24 paper.tex
v2.1

@@
 An increasing number of datasets have been published in the Resource Description Framework (RDF)~\cite{rdf}.
-SPARQL is the standardized interface to RDF and contributing effective reuse of distributed RDF data. 
-How can we maximize the value of accumulated SPARQL~\cite{sparql} queries?
+SPARQL~\cite{sparql} is the standardized interface to RDF and contributing effective reuse of distributed RDF data. 
+Although eco-systems for developing SPARQL have been developed, writing SPARQL codes often becomes a burden for the Semantic Web developers and users. 
+SPARQL queries have been written in many Semantic Web projects, which are the result of developers' efforts. 
+How can we maximize the value of accumulated SPARQL queries?
 Reuse of the queries is the key of this problem.
-Although eco-systems for developing SPARQL have been developed, writing SPARQL codes often becomes a burden for the Semantic Web developers and users. 
-SPARQL queries have been written in many Semantic Web projects, which requires efforts. 
 For effective construction of the Semantic Web applications, reuse of such queries are valuable.
@@
 The Semantic Web is comprised of various specifications, including RDF~\cite{rdf}, OWL~\cite{owl}, and SPARQL~\cite{sparql}. 
+RDF datasets are also accumulated and hosted in portal web sites~\cite{rdf-portal}.
 The ontologies written in OWL are accumulated and shared on repositories~\cite{bioportal}.
-RDF datasets are also accumulated and hosted in portal web sites~\cite{rdf-portal}.
-Not only the ontologies and datasets, but also the queries are important for the Semantic Web.
+Not only the datasets and ontologies, but also the queries are important for the Semantic Web.
 % As the SPARQL queries are important component of the Semantic Web community,
@@
 % In data management guideline, FAIR principle is well known~\cite{fair}. Findability, Accesibility, Reusablility should be addressed, to make the most of SPARQL queries as resources. 
-Applying FAIR principle to SPARQL query should increase the reusability of the queries.
+Thsu, applying FAIR principle to SPARQL query should increase the reusability of the queries.
 
@@
 
-Here, we apply the FAIR principle and extend the SPARQL specifications for more efficient development of the Semantic Web.
+Here, we apply the FAIR principle and extend the SPARQL specifications for more efficient development of the Semantic Web applications.
 %Semantic Web users often write SPARQL queris.
@@
 %How can we improve the reusability of SPARQL?
-Following the FAIR principle, we could identify the process to make SPARQL query reusable.
+According to the FAIR principle, we identified the process to make SPARQL query reusable.
 One of the key to improve the reusability of queries is parameterization.
@@
 4) construct a server for providing queries.
-And we demonstrate the steps to construct the SPANG template library, which is reusable on the Semantic Web platform.
+Further, we demonstrate the steps to construct the SPANG template library, which is reusable on the Semantic Web platform.
 
@@
 
+The SPANG~\cite{spang} project stared aiming at maximizing the usability of SPARQL queries, and the project now includes development of SPANG server, SPANG library, SPANG API, and SPANG command. 
 Figure~\ref{fig:spang_top} is the top page of SPANG server, which provides access to a SPANG library, links to GitHub repositories of the SPANG project, and documentations. 
-The SPANG project consists of SPANG server, SPANG library, SPANG API, and SPANG command.
 The central topic of this paper is how to construct the SPANG library in an interoperable and reusable way. 
-It also provides the foundation of findability and accessibility through SPANG API and command.
+The SPANG library specifications also provide the foundation of findability and accessibility through SPANG API and command.
 
-In the following sections, we review FAIR principles and describe how to apply the principle to SPARQL.
+In the following sections, we review FAIR principles in the context of SPARQL and describe how to apply the principle to SPARQL.
 Further, we demonstrate how to use the SPANG template library.
@@
 \includegraphics[width=1.0\textwidth]{spang_top.png}
-\caption{SPANG server top page}
+\caption{SPANG project top page}
 \label{fig:spang_top}
@@
 
-The FAIR guiding principle aims to enhance the Findability, Accessibility, Interoperability and Reusability of digital resources.
-It shoul be noted that the FAIR principle can be applied not only to the dataset resources but also to other type of resources including software tools.
+The FAIR guiding principle~\cite{fair} aims to enhance the Findability, Accessibility, Interoperability and Reusability of digital resources.
+It should be noted that the FAIR principle can be applied not only to datasets but also to other type of resources including software.
 Not only the RDF dataset, but also the SPARQL queries are important resource to be shared on the Semantic Web platform.
@@
 and provide the FAIR principle in the context of SPARQL queries.
-We review each item in the following subsections.
-In the following subsections, the target of FAIR principle is extended from data to resource.
-We consider a SPARQL query as a resource.
+We consider a SPARQL query as a resource,
+and here, the target of FAIR principle is extended from data to resources which include SPARQL queries.
 
@@
 \subsection{Findability}
-The ultimate goal of FAIR is to optimise the reuse of resources. 
-To achieve this, metadata should be well-described so that they can be replicated and/or combined in different settings.
+%The ultimate goal of FAIR is to optimise the reuse of resources. 
+%To achieve this, metadata should be well-described so that they can be replicated and/or combined in different settings.
 In the FAIR principle, making resources findable includes indexing resources by adding metadata to each resources. 
@@
 \subsection{Interoperability}
-For interoperability, a formal, accessible, shared, and broadly applicable language is necessary.
+%For interoperability, a formal, accessible, shared, and broadly applicable language is necessary.
+For interoperability, a shared language is necessary.
 The resource usually need to be integrated with other resources. 
@@
 SPARQL specification is proposed for interoperable use of queries to the Semantic Web. 
-It is valuable to use several triplestore implementation through the same programming interface. 
-However, standard SPARQL specifications do not include coding rules; capitalization, indentation and newline, etc. 
-Lack of those rules result in variation of SPARQL queries, which hampers the efficiency in collaborative development of SPARQL queries. 
-In other languages, coding rules exist in most cases. 
-In the case of SPARQL, even specification document or text books do not follow a specific coding rules. 
-Thus, we specify the coding rule used in SPANG template library, and implemented a formatter command to evaluate and reformat the input SPARQL code.
+Indeed, it is valuable to use several triplestore implementation through the same programming interface. 
+Nevertheless, standard SPARQL specifications do not include coding rules; capitalization, indentation and newline, etc. 
+Lack of such rules result in variation of SPARQL queries, which hampers the efficiency in collaborative development of SPARQL queries. 
+In the programming languages in general, coding rules exist in most cases. 
+In the case of SPARQL, however, even specification document or text books do not follow a specific coding rules. 
+Thus, we specify the coding rule used in SPANG template library, and implemented a formatter command to evaluate and reformat the input SPARQL.
 
@@
 The ultimate goal of FAIR is to optimise the reuse of resources. 
-However, in the specification of SPARQL, reusability is not a central topic. 
-Since it is an central resource in a Semantic Web, it is valuable to share and reuse SPARQL queries.
-Templating is a key for reusability. 
+However, in the specification of SPARQL, reusability is not considered as a central topic. 
+Since SPARQL queries is essential resources comprising the Semantic Web, it is valuable to share and reuse SPARQL queries.
+Templating is a key for improving reusability. 
 SPARQL specifications do not includes templating mechanism, but without templating, each SPARQL queries are not applicable to other use cases. 
-We implemented templating mechanism using a general freamework, mustache.
-Various activity is conducted to construct libraries of SPARQL. 
+We implemented templating mechanism using a general freamework, mustache~\cite{mustache}.
+Various activities are conducted to construct libraries of SPARQL~\cite{bioqueries}. 
 It is considered as activities to increase the reusability of SPARQL queries. However, no standard to increase the reusability is proposed. 
@@
 WHERE {
-    ?gda sio:SIO_000628 umls:{{arg1}} ,
-                        ?gene ;
+    ?gda sio:SIO_000628 umls:{{arg1}} , ?gene ;
         a ?type ;
@@
 \end{scriptsize}
-\caption{Example query in the SPANG library}
+\caption{Example query in the SPANG template library}
 \label{fig:example-sparql}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\section{SPANG Library and Use Cases}
+\section{SPANG Template Library with Use Cases}
 %%%%%%%%%%%%%%%%%%%%%%%%%
+
 In the previous section we review the FAIR principle in the context of SPARQL queries.
 In this section, we describe how we constructed the SPANG library with some use cases.
-The use case shown in this section includes the query to the DisGeNet endpoint~\cite{disgenet}, which is shown in Figure~\ref{fig:example-sparql}.
-This query retrieve protein IDs involved in a specific disease.
 The core of the SPANG library specification is the SPARQL metadata and templating mechanism for increasing the reusability of the SPARQL queries.
+According to the metadata and parameterization mechanism, we can construct a controlled set of SPARQL library which is reusable in various settings.
+The use case shown in this section includes the query to the DisGeNET endpoint~\cite{disgenet} shown in Figure~\ref{fig:example-sparql}.
+This query retrieves protein IDs involved in a specific disease.
 The query example includes metadata at the beginning of the query as comment lines.
 The query also includes a parameter for a disease identifier.
-According to the metadata and parameterization mechanism, we can construct a controlled set of SPARQL library which is reusable in various settings.
 
-\subsection{SPARQL Metadata}
+\subsection{SPANG Server}
+SPANG is originally developed as a SPARQL client to query the RDF dataset from command line.
+Here, we re-implemented the SPANG using Node.js and now the functionality is available through Web browsers.
 
-We propose a set of SPARQL metadata to annotate each SPARQL query, to make them more reusable.
+Figure~\ref{fig:spang_lib} is the list of the target SPARQL endpoints. It also lists the SPARQL templates available in general for various endpoints.
+
+Figure~\ref{fig:spang_disgenet} is the list of SPARQL templates for DisGeNET SPARQL endpoint.
+A short name for the SPARQL template, description of the query, and example parameters are shown.
+
+\begin{figure}
+\center
+\includegraphics[width=1.0\textwidth]{spang_lib.png}
+\caption{SPANG library}
+\label{fig:spang_lib}
+\end{figure}
+
+\begin{figure}
+\center
+\includegraphics[width=1.0\textwidth]{spang_disgenet.png}
+\caption{SPANG templates for DisGeNET SPARQL endpoint}
+\label{fig:spang_disgenet}
+\end{figure}
+
+\subsection{Assigning Metadata}
+
+We propose a set of SPARQL metadata to annotate each SPARQL query, to make them more findable.
 Those metadata are added as comment at the head of the SPARQL query, thus that does not violate the SPARQL specification. 
@@
 
-\subsection{SPANG Server}
-SPANG is originally developed as a SPARQL client to query the RDF dataset from command line.
-Here, we re-implemented the SPANG using Node.js and now the functionality is available through Web browsers.
-
-Figure~\ref{fig:spang_lib} is the list of the target SPARQL endpoints. It also lists the SPARQL templates available in general for various endpoints.
-
-Figure~\ref{fig:spang_lib} is the list of SPARQL templates for DisGeNET SPARQL endpoint.
-A short name for the SPARQL template, description of the query, and example parameters are shown.
-
-\begin{figure}
-\center
-\includegraphics[width=1.0\textwidth]{spang_lib.png}
-\caption{SPANG library}
-\label{fig:spang_lib}
-\end{figure}
-
 \begin{figure}[!t]
@@
 \label{fig:libs-api-out}
-\end{figure}
-
-\begin{figure}
-\center
-\includegraphics[width=1.0\textwidth]{spang_disgenet.png}
-\caption{SPANG templates for DisGeNet SPARQL endpoint}
-\label{fig:spang_disgenet}
 \end{figure}
@@
 
-SPANG is implemented in JavaScript using the Node.js technology~\cite{nodejs}. Thus, it can be called in JavaScript applications, and also in the command-line environment.
+SPANG is implemented in JavaScript using the Node.js~\cite{nodejs}. Thus, it can be called in JavaScript applications, and also in the command-line environment.
 
 \subsection{Template Specifications}
-SPANG template syntax is an extension of sparql-doc.
+SPANG template syntax is an extension of sparql-doc~\cite{sparql-doc}.
 Although the sparql-doc aims at documentation of SPARQL originally, this notation is suitable for annotating each SPARQL query with metadata in the frame of SPARQL query.
@@
 SPANG template engine is implemented, where each template can be transformed into abstract syntax tree, and then reconstructed into SPARQL. 
-We used PEG~\cite{peg} expression of SPARQL grammar originally expressed in EBNF in the SPARQL specification.
+We used Parsing Expression Grammar (PEG)~\cite{peg} expression of SPARQL grammar originally expressed in EBNF in the SPARQL specifications~\cite{sparql}.
 The original implementation of PEG.js~\cite{pegjs} of SPARQL grammar is provided by rdfstore-js project (https://github.com/antoniogarrote/rdfstore-js).
@@
 The template can be URL that returns a SPARQL query, such as \url{https://cdn.jsdelivr.net/gh/hchiba1/spang-library@latest/library/disgenet/disease_gene.rq}.
-The full usages of the command is as shown in Figure~\ref{fig:spang-command}.
+The full usages of the SPANG command is as shown in Figure~\ref{fig:spang-command}.
 
@@
 \end{scriptsize}
-\caption{Usage of the \texttt{SPANG2} command}
+\caption{Usage of the SPANG command}
 \label{fig:spang-command}
@@
 
+\bibitem{rdf}
+RDF 1.1 Concepts and Abstract Syntax, W3C Recommendation 25 February 2014. \url{http://www.w3.org/TR/rdf11-concepts/}
+
 \bibitem{sparql}
@@
 
-\bibitem{rdf}
-RDF 1.1 Concepts and Abstract Syntax, W3C Recommendation 25 February 2014. \url{http://www.w3.org/TR/rdf11-concepts/}
+\bibitem{fair}
+Wilkinson, M. D., Dumontier, M., Aalbersberg, I. J., Appleton, G., Axton, M., Baak, A., et al. (2016). The FAIR Guiding Principles for scientific data management and stewardship. Scientific data, 3.
 
@@
 \url{https://www.w3.org/TR/owl2-overview/}
+
+\bibitem{rdf-portal}
+Kawashima, S., Katayama, T., Hatanaka, H., Kushida, T., & Takagi, T. (2018). NBDC RDF portal: a comprehensive repository for semantic data in life sciences. Database, 2018.
+
+\bibitem{bioportal}
+Salvadores, M., Alexander, P. R., Musen, M. A., & Noy, N. F. (2013). BioPortal as a dataset of linked biomedical ontologies and terminologies in RDF. Semantic web, 4(3), 277-284.
 
@@
 Yamamoto, Y., Yamaguchi, A., & Splendiani, A. (2018). YummyData: providing high-quality open life science data. Database, 2018.
-
-\bibitem{fair}
-Wilkinson, M. D., Dumontier, M., Aalbersberg, I. J., Appleton, G., Axton, M., Baak, A., et al. (2016). The FAIR Guiding Principles for scientific data management and stewardship. Scientific data, 3.
 
@@
 
-\bibitem{rdf-portal}
-Kawashima, S., Katayama, T., Hatanaka, H., Kushida, T., & Takagi, T. (2018). NBDC RDF portal: a comprehensive repository for semantic data in life sciences. Database, 2018.
-
-\bibitem{bioportal}
-Salvadores, M., Alexander, P. R., Musen, M. A., & Noy, N. F. (2013). BioPortal as a dataset of linked biomedical ontologies and terminologies in RDF. Semantic web, 4(3), 277-284.
-
 \bibitem{asqc}

### 2020-05-24 paper.tex
v2.2

@@
 
-\subsection{Assigning Metadata}
+\subsection{Metadata Assignment and Usage}
 
@@
 
-\subsection{SPARQL Parameterization}
+\subsection{Parameterizing SPARQL}
 
@@
 \includegraphics[width=1.0\textwidth]{spang_disease_gene_query.png}
-\caption{SPANG templates for DisGeNet SPARQL endpoint}
+\caption{SPANG templates for searching DisGeNET}
 \label{fig:spang_disease_gene_query}
@@
 \includegraphics[width=1.0\textwidth]{spang_disease_gene_result.png}
-\caption{SPANG templates for DisGeNet SPARQL endpoint}
+\caption{DisGeNET search result}
 \label{fig:spang_disease_gene_result}
@@
 
+\subsection{SPANG Server}
+SPARQL queries can be executed in Web site (\url{https://spang.dbcls.jp/}).
+SPANG server is developed using Ruby on Rails.
+And it can be run on Docker.
+The SPANG query library is published on GitHub.
+Thus, users can run a portal site by their own.
+The SPANG APIs are available on the SPANG server.
+
 \subsection{JavaScript Application}
 SPANG is now implemented in JavaScript, so the SPARQL queries can be executed in JavaScript code across the internet.
-To avid CORS retriction, it can access through content delivery network services, such as jsDelivr~\cite{jsdelivr}, as shown in Figure~\ref{fig:jsdelivr}.
+To allow Cross-Origin Resource Sharing (CORS), it can access through content delivery network services, such as jsDelivr~\cite{jsdelivr}, as shown in Figure~\ref{fig:jsdelivr}.
 
@@
 \subsection{Command-line Client}
-As an interface the the SPANG library, we constructed a command-line interface.
+As an interface the the SPANG library, a Unix command-line interface is also available.
 Originally, SPANG was developed as a command line client in Perl~\cite{spang}.
-It is re-implemented in JavaScript using Node.js as \texttt{SPANG2}.
+It is now re-implemented in JavaScript using Node.js as \texttt{SPANG2}.
 SPARQL templates can be executed in command line.
-The following example command line gives a parameter to the query template, and execute to the DisGeNet endpoint
+The following example command line gives a parameter to the query template, and execute to the DisGeNET endpoint.
 
@@
 \end{figure}
-
-\subsection{SPANG Server}
-SPARQL queries can be executed in Web site.
-SPANG server is developed using Ruby on Rails.
-And it can be run on Docker.
-The SPANG query library is published on GitHub.
-Thus, users can run a portal site by their own.
-The SPANG APIs are available on the SPANG server.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%
+In this study, we put rich metadata into queries, and registered in a searchable resource.
+To the best of our knowledge, this is the first study to consider the FAIRification process comprehensively and show the concrete process of the FAIRification of it.
 
 SPARQL tempalting mechanisms have been implemented in various projects.
-Based on the templating mechanisms, SPARQL libraries have been implemented, such as Bioqueries.
-SPARQList is a framework to store SPARQL templates to be used through API.
-
-As a SPARQL formatter, some software are available.
-rdfstore-js\cite{rdfstore-js} has SPARQL parser, but does not have formatter.
-SPARQL.js~\cite{sparql-js} implements parser and formatter. However, there are no formatting rule explicitly defined.
-Jena package~\cite{jena} includes parser and formatter. However, it does not define formatting rule.
-
-Bioqueries~\cite{bioqueries} have tried to collect SPARQL queries as community effort. It increase the findability and reusability.
+Based on the templating mechanisms, SPARQL libraries have been implemented, such as Bioqueries~\cite{bioqueries}.
+Bioqueries~\cite{bioqueries} have tried to collect SPARQL queries as community effort.
+It increase the findability and reusability.
 However, the query can only be executed on the web site.
@@
 
+SPARQList is a framework to store SPARQL templates to be used through API.
 SPARQList~\cite{sparqlist} is a REST API server which executes a SPARQL query, transform the result into formatted data if defined.
@@
 
-In this study, we put rich metadata into queries, and registered in a searchable resource.
-
 Client for calling parameterized queries is still limited.
@@
 
-To the best of our knowledge, this is the first study to consider the FAIRification process comprehensively and show the concrete process of the FAIRification of it.
+As a SPARQL formatter, some software are available.
+rdfstore-js\cite{rdfstore-js} has SPARQL parser, but does not have formatter.
+SPARQL.js~\cite{sparql-js} implements parser and formatter. However, there are no formatting rule explicitly defined.
+Jena package~\cite{jena} includes parser and formatter. However, it does not define formatting rule.
 
@@
 Sharing not only data but also queries (i.e., means of interpreting data) on the Semantic Web platform will help the biological research community collaborate in knowledge integration and discovery.
-Toward the FAIRification of SPARQL, SPANG provides step toward the FAIRification of Semantic Web, not only in terms of 
+Toward the FAIRification of SPARQL, SPANG provides step toward the FAIRification of Semantic Web. 
 If an RDF database provider,
@@
 
-Moreover, it enables users to execute complex queries by combining existing query templates.
+%Moreover, it enables users to execute complex queries by combining existing query templates.
 SPANG, with these unique features, facilitates integrative exploitation of published RDF datasets and supports knowledge discovery.
@@
 
-The SPANG API returns the result in JSON format.
+Another issue is publishing the content of SPARQL as data, which enables analysis of query content.
+Currently, the SPANG API returns the result in JSON format.
 The JSON format can be mapped to JSON-LD using JSON-LD mapper, which is compatible with RDF.

### 2020-05-25 paper.tex
v2.3

@@
 % In data management guideline, FAIR principle is well known~\cite{fair}. Findability, Accesibility, Reusablility should be addressed, to make the most of SPARQL queries as resources. 
-Thsu, applying FAIR principle to SPARQL query should increase the reusability of the queries.
+Thus, applying FAIR principle to SPARQL query should increase the reusability of the queries.
 
@@
 %How can we improve the reusability of SPARQL?
-According to the FAIR principle, we identified the process to make SPARQL query reusable.
+According to the FAIR principle, we identify the process to make SPARQL query reusable.
 One of the key to improve the reusability of queries is parameterization.
@@
 The SPANG~\cite{spang} project stared aiming at maximizing the usability of SPARQL queries, and the project now includes development of SPANG server, SPANG library, SPANG API, and SPANG command. 
-Figure~\ref{fig:spang_top} is the top page of SPANG server, which provides access to a SPANG library, links to GitHub repositories of the SPANG project, and documentations. 
+Figure~\ref{fig:spang_top} is the top page of SPANG project, which provides access to a SPANG library, links to GitHub repositories of the SPANG project, and documentations. 
 The central topic of this paper is how to construct the SPANG library in an interoperable and reusable way. 
@@
 The SPARQL metadata includes: title, description, target endpoint, and parameters with its name, default value, and classes.
+Examples are shown in Section \ref{subsec:example-sparql}.
 Indexing of SPARQL queries are conducted and thus users can obtain specific queries of interest through application programming interfaces (APIs).
@@
 %For interoperability, a formal, accessible, shared, and broadly applicable language is necessary.
-For interoperability, a shared language is necessary.
+For interoperability, a formal and shared language is necessary.
 The resource usually need to be integrated with other resources. 
@@
 % \end{itemize}
-
-SPARQL specification is proposed for interoperable use of queries to the Semantic Web. 
-Indeed, it is valuable to use several triplestore implementation through the same programming interface. 
+Indeed, SPARQL specification is proposed for interoperable use of queries to the Semantic Web. 
+It is valuable to use several triplestore implementation through the same programming interface. 
 Nevertheless, standard SPARQL specifications do not include coding rules; capitalization, indentation and newline, etc. 
@@
 The ultimate goal of FAIR is to optimise the reuse of resources. 
-However, in the specification of SPARQL, reusability is not considered as a central topic. 
+However, in the specification of SPARQL, reusability has not been considered as a central topic. 
 Since SPARQL queries is essential resources comprising the Semantic Web, it is valuable to share and reuse SPARQL queries.
@@
 
-\begin{figure}[!t]
-\begin{scriptsize}
-\begin{verbatim}
-# @title Get UniProt IDs for a specific disease, e.g. C0751955 ("Brain Infarction")
-# @endpoint http://rdf.disgenet.org/sparql/
-# @prefix https://raw.githubusercontent.com/hchiba1/spang-library/master/prefix/bio
-# @param arg1=C0751955
-
-PREFIX disgenet_source: <http://rdf.disgenet.org/v4.0.0/void/>
-PREFIX umls: <http://linkedlifedata.com/resource/umls/id/>
-
-SELECT DISTINCT ?gene ?score ?gene_label ?source ?gda ?pmid ?description
-WHERE {
-    ?gda sio:SIO_000628 umls:{{arg1}} , ?gene ;
-        a ?type ;
-        sio:SIO_000253 ?source ;
-        sio:SIO_000216/sio:SIO_000300 ?score .
-    ?gene a ncit:C16612 ;
-        rdfs:label ?gene_label .
-    OPTIONAL {
-        ?gda sio:SIO_000772 ?pmid ;
-            dct:description ?description .
-    }
-}
-ORDER BY DESC(?score) ?source ?pmid
-
-\end{verbatim}
-\end{scriptsize}
-\caption{Example query in the SPANG template library}
-\label{fig:example-sparql}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 According to the metadata and parameterization mechanism, we can construct a controlled set of SPARQL library which is reusable in various settings.
-The use case shown in this section includes the query to the DisGeNET endpoint~\cite{disgenet} shown in Figure~\ref{fig:example-sparql}.
-This query retrieves protein IDs involved in a specific disease.
-The query example includes metadata at the beginning of the query as comment lines.
-The query also includes a parameter for a disease identifier.
 
@@
 
+\subsection{Example Query}
+\label{subsec:example-sparql}
+
+An example query to the DisGeNET endpoint~\cite{disgenet} is shown in Figure~\ref{fig:example-sparql}.
+This query retrieves protein IDs involved in a specific disease.
+The query example includes metadata at the beginning of the query as comment lines.
+The query also includes a parameter for a disease identifier \texttt{C0751955} (``Brain Infarction'').
+
+\begin{figure}[!t]
+\begin{scriptsize}
+\begin{verbatim}
+# @title Get UniProt IDs for a specific disease, e.g. C0751955 ("Brain Infarction")
+# @endpoint http://rdf.disgenet.org/sparql/
+# @prefix https://raw.githubusercontent.com/hchiba1/spang-library/master/prefix/bio
+# @param arg1=C0751955
+
+PREFIX disgenet_source: <http://rdf.disgenet.org/v4.0.0/void/>
+PREFIX umls: <http://linkedlifedata.com/resource/umls/id/>
+
+SELECT DISTINCT ?gene ?score ?gene_label ?source ?gda ?pmid ?description
+WHERE {
+    ?gda sio:SIO_000628 umls:{{arg1}} , ?gene ;
+        a ?type ;
+        sio:SIO_000253 ?source ;
+        sio:SIO_000216/sio:SIO_000300 ?score .
+    ?gene a ncit:C16612 ;
+        rdfs:label ?gene_label .
+    OPTIONAL {
+        ?gda sio:SIO_000772 ?pmid ;
+            dct:description ?description .
+    }
+}
+ORDER BY DESC(?score) ?source ?pmid
+
+\end{verbatim}
+\end{scriptsize}
+\caption{Example query in the SPANG template library}
+\label{fig:example-sparql}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-SPANG is implemented in JavaScript using the Node.js~\cite{nodejs}. Thus, it can be called in JavaScript applications, and also in the command-line environment.
+In the previous section, we describe the SPANG library we developed, with some use cases.
+However, constructing some other implementations following the same specifications.
+In this section, we describe the details of the SPANG template specifications.
+It is possible to implement another interoperable specifications.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%
+
+SPANG is implemented in JavaScript using the Node.js~\cite{nodejs}. Thus, it can be called in JavaScript applications, and also in the command-line environment.
 
